---
title: "Seeing Myself in My Group: A Formal Architecture of Self-Anchoring via Similarity-Based Generalization"
shorttitle: "Self-Anchoring Formal Architecture"
author:
  - name: Jacob J. Elder
    affiliations:
      - name: University of California, Riverside
        department: Psychology
    corresponding: true
    email: jelder@ucr.edu
abstract: |
  People tend to see themselves as similar to their ingroup, often by projecting self-beliefs onto their perceptions of others. However, the within-person cognitive mechanisms facilitating this process remain under-specified. This research moves social identity theory from a verbal model to a formal architecture, establishing the similarity-based (e.g., if I am outgoing, my group should be characteristic of semantically related traits like sociable) and contrastive (i.e., how the ingroup compares to a specific outgroup) mechanisms through which self-evaluations generalize to the ingroup. Across three studies using minimal groups (N = 61), university groups (N = 283), and racial groups (N = 265), we find that individuals use semantic similarity among traits—consistent with principles of similarity-based generalization—to infer group characteristics based on their own attributes. We further demonstrate that self-anchoring is a structured inferential generalization primarily driven by a motivation to achieve similarity with the ingroup. However, in the racial context, racial minority participants contrasting against the racial majority were driven moreso to achieve dissimilarity from the majority outgroup. Using a computational model to measure the rate at which self-beliefs are converted into ingroup beliefs, we find this projection rate weakens when participants contrast their ingroup against a positively regarded outgroup (e.g., a higher-status university in Study 2 or a fellow minority group in Study 3). This suggests self-anchoring is a cognitive process systematically amplified by intergroup context, with projection rates correlating with self-reported intergroup bias in studies 2 and 3 and social identification in all three studies. Findings reflect that social identity emerges through similarity-based classification processes analogous to the structured semantic representations found in modern word embedding architectures.
keywords: [self-anchoring, social identity, category learning, semantic similarity, computational modeling]
format:
  apaquarto-docx: default
---

```{r}
#| label: setup
#| include: false
library(here)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.width = "100%")
# Figures are generated by Figures/make_figures.R.
# Run that script first if figures are missing.
fig_path <- function(...) here("Figures", ...)
```

## INTRODUCTION
People carry distinct sets of stable self-beliefs across various situations (Markus & Wurf, 1987), yet they also manage to achieve a sense of belonging (Baumeister & Leary, 1995) by assimilating into their various social groups (Brewer, 1991; Ellemers et al., 2001). In achieving this sense of similarity, individuals promote social identification—a sense of positive attachment to the group that is foundational to social life (Tajfel, 1978; Turner et al., 1987). Historically, social psychology has conceptualized group membership as a process of "depersonalization," where the self is categorized as an interchangeable exemplar of a group prototype (Turner et al., 1987). While this dominant account—often termed "self-stereotyping"—emphasizes the assimilation of group attributes into the self-concept, it does not sufficiently explain how people identify with novel groups or how they maintain self-beliefs that remain stable beyond specific group memberships (van Veelen et al., 2016).

Rather than merely limitlessly assimilating group attributes, people also project their own attributes onto how they represent and perceive their ingroups (M. Cadinu & Rothbart, 1996) as well as others in interpersonal contexts (Ames, 2004). This process, known as self-anchoring, serves as an informational base (Gramzow et al., 2001) from which people draw inferences about their social environment. Specifically, individuals engage in inductive reasoning, inferring unknown information about their group on the basis of their own self-knowledge (DiDonato et al., 2011; Krueger, 2007). Self-anchoring is most pronounced in situations where group knowledge is ambiguous or diagnostic information is absent (van Veelen et al., 2013a), making it a critical mechanism for the emergence of social identity.

The present approach differs fundamentally from the social projection literature (Krueger, 1998; Ames, 2004; Van Boven & Loewenstein, 2003), which treats self-to-group inference as a Bayesian base-rate problem: one's own trait level adjusts a prior belief about the group mean, with each trait evaluated independently. We model self-anchoring instead as similarity-based generalization across a structured semantic network. This distinction is consequential: it allows us to test whether self-knowledge propagates *through relational structure* to traits the person never directly evaluated—a form of inference that base-rate accounts cannot generate and that directly constitutes generalization in the category learning sense.

### Inferences About the Ingroup Based on the Self
Despite the apparent strength of evidence for self-anchoring, the majority of research in this domain has relied on correlated ratings of identical traits across the self and group (M. Cadinu & Rothbart, 1996; Otten & Wentura, 2001). While these tests provide evidence of rating stability, they do not necessarily demonstrate *generalization* per se. Furthermore, traditional measures are vulnerable to repetition effects; the mere repetition of information can cause it to be perceived as more characteristic (Unkelbach et al., 2019). A rigorous test of the generalization-based theory of self-anchoring requires establishing that self-evaluations generalize across semantically related but novel traits (Heit & Rubinstein, 1994). For example, if an individual perceives themselves as "outgoing," do they infer that their group is characteristic of semantically similar traits like "sociable" and "fun," even if they have not explicitly evaluated themselves on those specific attributes?

In the current research, we move social identity theory from a verbal, descriptive model to a formal architecture by integrating principles of category learning. We frame the self as a semantic prototype in a high-dimensional space, where group beliefs emerge through similarity-based generalization analogous to foundational principles of cognition (Shepard, 1987). To formalize this process, we utilize a semantic dependency network of 147 positive traits, constructed using data from 178 Amazon Mechanical Turk participants with a 25% consensus threshold. From this network, we derive relational similarity measures (network-based Dice similarity; Equation 1) that allow us to quantify how self-representations propagate across an interconnected semantic web.

This network approach enables the first formal implementation of the "metacontrast principle," which posits that group categorization is defined by the ratio of an individual’s similarity to the ingroup relative to the individual’s similarity to the outgroup (Turner et al., 1987). While the metacontrast principle has been central to social identity research for decades, it has remained a verbal description (Davis & Goldwater, 2021). Structurally, Turner's metacontrast ratio is formally isomorphic to Nosofsky's (1986) Generalized Context Model—both define category membership via a ratio of summed similarities; we provide the formal backbone Turner's verbal architecture required. By applying a category learning framework to social identity, we provide a formal test of whether intergroup contrast accentuates self-anchoring and how individuals balance the motivation for ingroup similarity against outgroup differentiation.

### Relational Similarity as the Basis for Self-Concept Generalization
Effective navigation of social environments requires generalizing from known experiences to new stimuli based on similarity (Shepard, 1987). In recent work, we developed a semantic network of trait dependencies (J. Elder et al., 2023) to extract relational similarity based on shared semantic neighbors. This network model allows us to identify how people represent themselves and their groups, moving beyond simple trait-for-trait matching. Inferred similarity is not only critical for classifying elements within a category but also facilitates the contrasting of distinctive features between categories (Tversky, 1977).

Social identity research has borrowed heavily from cognitive science research on concept learning, yet it has rarely implemented the formalism leveraged by that field. The ability to make representational claims about the role of similarity-based inference in social categorization has previously been limited by the absence of model formalism (Guest & Martin, 2021). Here, we bridge this gap by implementing formal category learning models—such as the Generalized Context Model (Nosofsky, 1986)—to test the principles of social categorization in a self-anchoring context.

### The Current Design
We utilize a "training-to-generalization" paradigm common in concept learning research (Bowman et al., 2020). Participants first self-evaluate on a subset of traits (training phase), which serve as exemplars of the self-concept prototype. This is followed by a "generalization phase" where participants classify traits—including novel traits not seen during training—as more characteristic of either the ingroup or outgroup. Using the traits’ semantic similarities to the self-concept, we predict the likelihood of ingroup classification.

Across three studies, we examine how various intergroup contexts amplify or attenuate these generalization weights. Study 1 utilizes minimal groups to provide a proof-of-concept for similarity-based generalization. Study 2 examines the role of relative social status using university groups, testing whether self-anchoring is driven by differentiation from low-status outgroups or assimilation toward high-status ones. Study 3 applies this framework to racial identities, examining how majority or minority outgroup contrasts exert differential effects on the tendency to self-anchor. This approach provides a formal backbone for the "sense of sameness" (James, 1890) that defines the integration of the individual into the social collective.

## STUDY 1: SELF-ANCHORING BASED ON MINIMAL CONDITIONS
Study 1 provided a first proof-of-concept for similarity-based generalization in a minimal group context where group knowledge is absent.

### Methods
**Participants**
From an initial pool of 80 participants, 19 were excluded (final *N* = 61). Exclusions were applied for: failure to consent to data use after debriefing (*n* = 9), self-reported low task seriousness (< 4 on a 7-point item; *n* = 1), self-reported unusable data (*n* = 2), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 10). Participants were native English-speaking university students (40.98% Cisgender Female, 59.02% Cisgender Male; *M*<sub>Age</sub> = 19.95, *SD*<sub>Age</sub> = 1.51, Range<sub>Age</sub> = [18, 25]), with an ethnic composition of 9.84% White/Caucasian, 11.48% Mixed/Other, 32.79% Asian, 40.98% Hispanic/Latino, and 4.92% Native-American. A power analysis using *simr* (Green & MacLeod, 2016) on a prior relational similarity dataset indicated that *N* = 5 was sufficient to detect within-subjects effects at 95% power. This seemingly low threshold reflects the statistical structure of multilevel models: within-subjects fixed effects are powered by Level-1 observations — here, 148 binary classification trials per participant — rather than by the number of Level-2 clusters. With 148 observations per person, detecting fixed effects on within-person variation achieves high power at small N; the final sample of *N* = 61 provides substantial additional power and enables detection of between-person individual differences. Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 61 can detect correlations of *r* ≥ .34 at 80% power (α = .05, two-tailed).

**Network Procedure**
We utilized a semantic dependency network of 147 traits constructed using data from 178 Amazon Mechanical Turk participants (25% consensus threshold). This network captures psychological implication structure (e.g., "If I am brave, I am adventurous") rather than linguistic co-occurrence. Static word embeddings (e.g., GloVe) are ill-suited for this purpose on two grounds: antonyms acquire high cosine similarity because they appear in identical sentence contexts, and cosine similarity is symmetric, discarding the directional dependencies (e.g., *Thoughtful* → *Humble* but not vice versa) that the dependency network preserves. From this network, we derived network-based Dice similarity (@eq-dice), representing the proportion of shared neighbors between traits.

$$S_{ij} = \frac{2|N(i) \cap N(j)|}{|N(i)| + |N(j)|}$$ {#eq-dice}

where $N(i)$ and $N(j)$ denote the neighbor sets of traits $i$ and $j$ in the semantic dependency network.

```{r}
#| label: fig-01-trait-network
#| fig-cap: "Trait network. Top figure depicts full semantic dependency network of traits. Bottom figure is subset of network containing the trait ‘Friendly’ and its immediate neighbors."
#| eval: false
knitr::include_graphics(fig_path("fig01_trait_network.tiff"))
```

**Design**
*Training phase.* Participants self-evaluated approximately 60% of the network (90 traits) on a Likert scale from 1 (*Not at all*) to 7 (*Extremely*). Following a dot-estimation minimal group assignment task (NEST), participants were randomly assigned to be "overestimators" or "underestimators." In the *generalization phase*, participants classified all 148 traits in the network as characteristic of either the ingroup or outgroup (148 trials). This included 90 repeated traits and 58 novel traits.

```{r}
#| label: fig-02-task-schematic
#| fig-cap: "Schematic of task design. Depicting training phase on top and generalization phase on bottom. Participants self-evaluate on 90 out of 148 traits on a Likert scale from 1 to 7. During generalization phase, 90 traits are thus repeated while 58 traits are novel and never received a self-evaluation. Participants then proceed through all traits in the semantic trait network, and classify whether each trait is characteristic of the ingroup or the outgroup."
#| eval: !expr file.exists(fig_path("fig02_task_schematic.tiff"))
knitr::include_graphics(fig_path("fig02_task_schematic.tiff"))
```

**Indices**
We computed *Similarity-to-Self* ($SS_g$; @eq-ss) as a similarity-weighted average of self-evaluations across training traits, capturing the degree to which the self-concept predicts the semantic neighborhood of each test trait. We also computed a *local self-concept clarity* index ($H_g$; @eq-entropy): a similarity-weighted Shannon entropy over the self-evaluation distribution in the semantic neighborhood of each test trait. Low $H_g$ means training traits near $g$ share a concentrated, coherent self-rating (e.g., all high or all low) — a clear discriminating signal. High $H_g$ means they carry mixed, conflicting self-evaluations — a noisy signal for group inference. This operationalizes Campbell et al.'s (1996) self-concept clarity at the local semantic level: when a trait's neighborhood is clearly self-descriptive in one direction, $SS_g$ can reliably guide classification; when self-ratings are diffuse, inference is degraded. We estimated the association of $H_g$ with ingroup classification in a dedicated mixed-effects logistic regression for each study (desirability controlled).

$$SS_g = \frac{\sum_{t=1}^{T} E_t \cdot S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$ {#eq-ss}

where $E_t$ is the self-evaluation on training trait $t$, $S_{tg}$ is the Dice similarity between training trait $t$ and test trait $g$, and $T$ is the number of training traits.

$$H_g = -\sum_{e=1}^{7} p_e \log_2 p_e, \quad p_e = \frac{\sum_{t:\, E_t = e} S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$ {#eq-entropy}

where $p_e$ is the similarity-weighted proportion of training traits rated at level $e$ on the 7-point scale, yielding a distribution over self-evaluation ratings for each test trait $g$.

Each computational model produces a *model-derived Metacontrast Ratio* (MCR) as a generated quantity (see *Computational Modeling* below), computed using parameter-calibrated similarity weights and individual projection gradients: $\text{MCR}_t = \text{simW}_{\text{in},t} / \text{simW}_{\text{out},t}$, where $\text{simW}_{\text{in}}$ and $\text{simW}_{\text{out}}$ are the generalization-weighted sums of projection onto ingroup- and outgroup-predictive self-knowledge, respectively. The subject-level MCR ($\overline{\text{MCR}}_s$) averages this ratio across trials, yielding a person-specific index of how strongly the semantic self-concept discriminates ingroup from outgroup classification.

**Computational Modeling**
We compared four cognitive architectures based on category learning principles (Nosofsky, 2011) to test the representational structure of self-anchoring.

**Level 1: Bias Model (Motivational Baseline).** This model represents a general tendency to choose the ingroup regardless of trait content, serving as a baseline for ingroup favoritism:
$$P(\text{Ingroup} | g) = \text{logit}^{-1}(\text{logit}(\gamma))$$
where $\gamma$ is the bias parameter.

**Level 2: Symmetric Model (Traditional Self-Anchoring).** This model utilizes a single projection rate ($\alpha$) assuming that the rate of ingroup assimilation is mathematically identical to the rate of outgroup repulsion:
$$P(\text{Ingroup} | g) = \frac{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta}{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta + (1-\gamma) \cdot (\sum_{t=1}^T S_{tg} \cdot (1-G_t))^\beta}$$
where $G_t = \frac{1}{1 + e^{-\alpha(E_t-4)}}$ represents the latent belief transformed from self-evaluations ($E_t$).

**Level 3: Symmetric + $\lambda$ Model (The Generalization Gradient).** This model introduces Shepard’s Law by adding a generalization sensitivity parameter ($\lambda$), representing the decay of inference across semantic similarity ($S_{tg} \rightarrow S_{tg}^\lambda$). This architecture treats $\lambda$ as a foundational cognitive principle that defines the self-concept’s structural reach, independent of social target or bias. 

```{r}
#| label: fig-05-lambda-identifiability
#| fig-cap: "How Shepard's Law (λ) Unlocks Parameter Identifiability. As λ increases, the generalization gradient becomes steeper, restricting the influence of self-evaluations to only local semantic neighbors. This 'flattening' of influence for more distant novel traits provides the mathematical leverage necessary to distinguish the structural reach of the self-concept (λ) from the extremity of social projection (α)."
#| eval: !expr file.exists(fig_path("fig05_lambda_identifiability.tiff"))
knitr::include_graphics(fig_path("fig05_lambda_identifiability.tiff"))
```

**Level 4: Asymmetric + $\lambda$ Model (The Full Architecture).** This model decouples the assimilation and repulsion processes into distinct parameters, $\alpha_{in}$ and $\alpha_{out}$, to test if social identity is driven by "ingroup love" or "outgroup hate":
$$G_{in,t} = \frac{1}{1 + e^{-\alpha_{in}(E_t-4)}} ; \quad G_{out,t} = \frac{1}{1 + e^{\alpha_{out}(E_t-4)}}$$
By utilizing novel traits to establish the baseline "semantic radius" via $\lambda$, the model possesses the mathematical leverage to decouple these otherwise collinear slopes, unlocking the asymmetric forces central to social identity theory. 

To ensure identifiability of these parameters within a 2AFC task, we leveraged three computational strategies. First, we exploited the unique information provided by novel versus repeated traits; while repeated traits primarily inform projection extremity ($\alpha$), novel traits isolate the signal for generalization sensitivity ($\lambda$) by forcing the model to rely entirely on the semantic similarity matrix ($S$). Second, we implemented the dual latent belief structure described above, allowing the model to distinguish choices driven by ingroup similarity from those driven by outgroup dissimilarity. Finally, we utilized hierarchical Bayesian regularization to stabilize individual estimates: by sharing statistical strength across participants, individual parameter estimates are shrunk toward the group mean, preventing extreme estimates from subjects with noisy or sparse data from distorting inference. To account for potential non-systematic noise in participant responses (e.g., accidental button presses or lapses in attention), we incorporated a lapse parameter ($w$) into all four architectures. This parameter estimates the probability that a given choice was a result of random guessing (fixed at $P = 0.5$) rather than the underlying cognitive model, such that the final probability of an ingroup choice is defined as:
$$P(\text{Ingroup}) = w \cdot 0.5 + (1 - w) \cdot P_{\text{model}}$$
This addition ensures that occasional outlying responses do not unduly bias the estimation of the structural parameters ($\lambda$, $\alpha$). In addition to log-likelihood (used for LOO-CV model comparison), each model outputs, as generated quantities, trial-level predicted choice probabilities ($\hat{P}_t = w \cdot 0.5 + (1-w) \cdot P_{\text{model},t}$) and a model-derived Metacontrast Ratio ($\widehat{\text{MCR}}_t = \text{simW}_{in,t} / \text{simW}_{out,t}$), where $\text{simW}_{in,t}$ and $\text{simW}_{out,t}$ are the parameter-calibrated ingroup and outgroup similarity totals at trial $t$. This model-derived quantity is calibrated by each participant's posterior parameter estimates, incorporating both generalization breadth ($\lambda$) and projection slopes ($\alpha_{in}$, $\alpha_{out}$), making it person-specific: two participants with identical behavioral responses but different estimated parameters will yield different model MCRs, as the metric reflects each person's underlying representation of how strongly a given trait's semantic neighborhood predicts ingroup versus outgroup membership. This hierarchical structure was extended to a pooled analysis across all three studies, treating each study as an exchangeable sample of a broader human social-cognitive architecture (Global $\rightarrow$ Study $\rightarrow$ Subject). To ensure robust estimation across these distinct contexts, hierarchical variances were sampled from Cauchy distributions, providing the necessary regularization to accommodate the small hierarchical sample size. This architecture allowed for the formal estimation of "Global Mean" parameters ($\lambda$, $\alpha$, $w$) that capture cross-context structural properties of social generalization across the three intergroup contexts studied here. Models were fitted using Stan (four MCMC chains; 2,000 samples post-warmup). Convergence was confirmed via $\hat{R} < 1.01$ (Vehtari et al., 2021).

**Table 1. Summary of Computational Model Architectures.**

| Model | *k* | Parameters | Description |
|:------|:---:|:-----------|:------------|
| Bias | 2 | $\gamma$, $w$ | Ingroup favoritism baseline. Choices driven entirely by response bias; no role for trait similarity or self-knowledge. |
| Symmetric | 3 | $\alpha$, $\gamma$, $w$ | Single projection rate; ingroup assimilation and outgroup repulsion are mathematically yoked ($\alpha_{in} = \alpha_{out}$). |
| Symmetric+$\lambda$ | 4 | $\alpha$, $\gamma$, $\lambda$, $w$ | Adds Shepard's generalization gradient; the reach of the self-concept across semantic space is governed by a sensitivity parameter $\lambda$, but projection remains symmetric. |
| Asymmetric+$\lambda$ | 5 | $\alpha_{in}$, $\alpha_{out}$, $\gamma$, $\lambda$, $w$ | Full architecture. Decouples ingroup assimilation ($\alpha_{in}$) from outgroup repulsion ($\alpha_{out}$), allowing independent estimation of "ingroup love" and "outgroup hate." |

*Note.* $k$ = number of free parameters. $\alpha$ / $\alpha_{in}$ / $\alpha_{out}$ = projection rate(s) (0–10); $\gamma$ = response bias (0–1); $\lambda$ = generalization sensitivity (0–5); $w$ = lapse rate (0–1). All models estimated via hierarchical Bayesian inference; subject-level parameters are drawn from a group-level distribution with non-centered parameterization.


```{r}
#| label: fig-03-parameter-space
#| fig-cap: "Parameter space of the Self-Projection Model. Rows vary generalization sensitivity (λ: Low = 0.5, High = 4.0); columns vary projection rate (α: Low = 0.5, High = 3.5). Each panel shows how P(ingroup) changes as a function of a test trait's semantic similarity to the self-concept (x-axis) for a hypothetical participant. Low-λ curves are shallow (self-knowledge generalizes broadly across dissimilar traits); high-λ curves are steep (self-knowledge generalizes narrowly to close semantic neighbors only). Low-α curves cluster near chance (0.5; weak projection); high-α curves diverge strongly from chance (strong projection). The Venn diagrams at right illustrate the qualitative distinction: Low-λ/High-α produces a broad projection footprint spanning the full trait network (large circle overlap), whereas High-λ/Low-α produces a narrow footprint concentrated on the most similar traits (small overlap). Dashed line = chance (0.50)."
#| eval: !expr file.exists(fig_path("fig03_parameter_space_visualization.tiff"))
knitr::include_graphics(fig_path("fig03_parameter_space_visualization.tiff"))
```

```{r}
#| label: fig-04-parameter-illustration
#| fig-cap: "From self-ratings to ingroup classifications: the role of projection rate and generalization sensitivity. (A) Self-rating profile for eight hypothetical training traits forming two semantic clusters (social: Sociable, Warm, Outgoing, Friendly; quiet/neutral: Organized, Accurate, Quiet, Reserved). Dashed line = neutral midpoint (4). (B) Dice similarity heatmap showing the two-cluster semantic structure. (C) Predicted P(ingroup) for a *low-projection* participant (α = 0.5, λ = 1.0): predictions are broadly distributed and modestly above chance, with little contrast between social and quiet traits. (D) Predicted P(ingroup) for a *high-projection* participant (α = 3.0, λ = 3.5): predictions are sharply amplified—highly-rated social traits (trained and novel) approach 85–90% ingroup, while low-rated quiet traits drop to ~35–40%. Both profiles show that the model generalizes to semantically novel traits (light bars) by propagating beliefs through the similarity structure, not just repeating training-phase labels."
#| eval: !expr file.exists(fig_path("fig04_parameter_illustration.tiff"))
knitr::include_graphics(fig_path("fig04_parameter_illustration.tiff"))
```

### Results
Predictors of ingroup classification were estimated using mixed-effects logistic regression with crossed random effects for subjects and traits; random slopes were estimated for focal predictors. We report average marginal effects (AMEs) with 95% confidence intervals and two-tailed *p*-values. Desirability reliability was good, ICC(C, 16) = .682 [.601, .753].

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in models for self-evaluations and similarity-to-self) quantified predictors of ingroup classification. A 1-SD increase in *Similarity-to-Self* increased P(ingroup) by 7.0 percentage points (AME = .070, 95% CI [.028, .111], *p* = .001), substantially larger than the 6.3 pp effect of direct self-evaluations (AME = .063, 95% CI [.040, .086], *p* < .001), replicating traditional self-anchoring. Desirability was non-significant (AME = .016, 95% CI [−.002, .034], *p* = .075). Across the Similarity-to-Self gradient, predicted P(ingroup) ranged from 48% at −1 SD to 56% at the mean to 64% at +1 SD. The effect did not differ between trained and held-out traits (Trained AME = .069, Held-Out AME = .073; difference = .004 pp, 95% CI [−.013, .020]), confirming practical equivalence and ruling out repetition as an explanation. Self-concept entropy (*H_g*) was in the expected negative direction but non-significant in Study 1 (AME = −.058, 95% CI [−.152, .036], *p* = .225), consistent with low statistical power and the high lapse rate under minimal-group conditions.

```{r}
#| label: fig-06-equivalence
#| fig-cap: “Depiction of probability of significance and equivalence test in Study 1. Vertical line denotes the threshold for significance (β > ±.18). Red = proportion within the Region of Practical Equivalence (ROPE); blue = proportion that is significant.”
#| eval: false
knitr::include_graphics(fig_path(“fig06_equivalence_test.tiff”))
```

```{r}
#| label: fig-07-marginal-effects
#| fig-cap: "Predictors of ingroup classification: Desirability, self-evaluations, and similarity-to-self. Plotted using average marginal predictions (marginaleffects package) ± 95% CI. Top row is Study 1 (Minimal Groups). Middle row is Study 2 (University Status). Bottom row is Study 3 (Racial Groups). Left column: desirability; center: self-evaluations; right: similarity-to-self. X-axis = Z-scored predictor (−1 SD, Mean, +1 SD); Y-axis = predicted P(ingroup classification). Colors denote outgroup conditions within each study. Dashed line = chance (0.50). Generated from Results/marginal_effects_s*_predictions.csv."
#| fig-width: 10
#| fig-height: 10
#| eval: !expr file.exists(fig_path("fig07_marginal_effects.tiff"))
knitr::include_graphics(fig_path("fig07_marginal_effects.tiff"))
```


**Trait Segregation**

```{r}
#| label: fig-trait-segregation
#| fig-cap: "Conceptual illustration of trait segregation (network homophily) in a semantic trait network. Each node represents a personality trait; edges connect semantically similar traits. Node color indicates group classification (blue = Ingroup, pink = Outgroup). *Left:* High trait segregation — semantically similar traits receive the same group label, producing two spatially coherent ingroup and outgroup neighborhoods. *Right:* Low trait segregation — ingroup and outgroup labels are scattered across the semantic structure regardless of semantic proximity."
#| fig-width: 10
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_trait_segregation.tiff"))
knitr::include_graphics(fig_path("fig_trait_segregation.tiff"))
```

```{r}
#| label: fig-trait-segregation-placeholder
#| results: 'asis'
#| echo: false
#| eval: !expr !file.exists(fig_path("fig_trait_segregation.tiff"))
cat("*[Figure pending: run `Figures/make_trait_segregation_fig.R` to generate.]*")
```

*Trait segregation* (network nominal homophily) quantifies how much a participant's ingroup versus outgroup classifications cluster along the semantic similarity network—whether semantically connected traits tend to receive the same group label (*M* = .09, *SD* = .08; range [−.04, .26]). Higher values indicate that participants carved sharper, spatially coherent ingroup and outgroup regions out of the trait network; lower values indicate that ingroup and outgroup labels were intermixed across the semantic structure. Exploratory correlations with individual differences (95% CIs reported in lieu of *p*-values given multiple comparisons) indicated that higher need to belong (*r* = .29, 95% CI [.04, .50]) and greater interdependence (*r* = .18, CI [−.07, .41]) were associated with greater trait segregation, while higher self-esteem (*r* = −.27, CI [−.49, −.02]) and greater independence (*r* = −.21, CI [−.44, .04]) were associated with less. This pattern suggests that individuals more motivated by group membership impose sharper categorical boundaries on the trait network, whereas those with more autonomous, positively evaluated self-concepts draw less rigid group lines. Correlations with computational parameters and the model-derived MCR (FDR-corrected within the same family as the personality correlates) revealed a non-significant negative association between MCR and trait segregation (*r* = −.23, *p*_raw = .081, *p*_FDR = .316): participants whose self-concept more strongly discriminates ingroup from outgroup semantic neighborhoods (higher MCR) tended to draw *less* rigid categorical boundaries, suggesting that semantic self-anchoring and categorical segregation may reflect complementary rather than redundant routes to ingroup differentiation. Generalization sensitivity (*λ*) showed a non-significant positive association (*r* = .18, *p*_raw = .160). No associations survived FDR correction (all *p*_FDR > .23).

**Model Performance and Parameters**
We compared four cognitive architectures of social inference: Bias, Symmetric, Symmetric+$\lambda$, and Asymmetric+$\lambda$ (see Table 1 for architecture summary). Model selection used leave-one-out cross-validation (LOO-CV; Vehtari et al., 2017), with models ranked by expected log predictive density (ELPD); $\Delta$ELPD is reported relative to the best-fitting model. Log-likelihood was stored at the trial level rather than the subject level, enabling observation-level LOO and reliable Pareto $k$ diagnostics; greater than 95% of trials had $k < 0.7$ across models, confirming the validity of the PSIS approximation (Vehtari et al., 2017). To complement the group-level comparison, we computed each participant's *per-subject LOO ELPD difference* (per-subject $\Delta$ELPD = $\text{ELPD}_{\text{asymmetric}} - \text{ELPD}_{\text{symmetric}}$), summing pointwise ELPD values across that participant's valid trials. A positive per-subject $\Delta$ELPD indicates the asymmetric architecture better predicts that individual's choices; a negative value indicates the symmetric architecture is favored. This person-specific index was examined against individual-difference measures to test whether particular psychological characteristics predict which model best accounts for a given participant's behavior.

**Table 2. LOO Model Comparison — Study 1 (Minimal Groups, *N* = 61).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Symmetric+$\lambda$ | −5647.5 | 29.2 | 0.0 | — |
| Asymmetric+$\lambda$* | −5647.7 | 29.1 | −0.21 | 0.55 |
| Symmetric | −5760.4 | 25.6 | −112.9 | 13.0 |
| Bias | −5839.0 | 24.7 | −191.4 | 16.2 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy. *One divergent transition; $\hat{R}_{\max} = 1.006$.

The Symmetric+$\lambda$ model provided the best predictive fit (ELPD = $-5647.5$, SE = $29.2$), meaningfully outperforming the Symmetric model ($\Delta$ELPD = $-112.9$, SE = $13.0$; $|\Delta\text{ELPD}|/\Delta\text{SE} = 8.7$) and the Bias model ($\Delta$ELPD = $-191.4$, SE = $16.2$). Crucially, the Asymmetric+$\lambda$ model was statistically indistinguishable from the winner ($\Delta$ELPD = $-0.21$, SE = $0.55$; $|\Delta\text{ELPD}|/\Delta\text{SE} = 0.38$), while producing one divergent transition ($\hat{R}_{\max} = 1.006$). Together these results indicate that in minimal groups, decoupling ingroup projection ($\alpha_{in}$) from outgroup discrimination ($\alpha_{out}$) affords no reliable improvement in predictive accuracy: a symmetric projection rate captures the data as well as an asymmetric one. Group-level parameter medians for the Symmetric+$\lambda$ model were: projection rate $m = 2.80$ (95% CI $[1.50, 6.67]$), generalization sensitivity $\lambda = 3.56$ (95% CI $[2.79, 4.22]$), ingroup classification baseline $\gamma = 0.36$ (95% CI $[0.28, 0.45]$), and lapse rate $w = 0.56$ (95% CI $[0.39, 0.70]$). The elevated lapse rate under minimal group conditions is interpretable rather than artifactual: when groups carry no prior content, a substantial portion of trial-by-trial variability is structurally underdetermined — participants must classify 148 traits for a group defined by nothing beyond an arbitrary assignment label, producing genuine choice indeterminacy the similarity structure cannot fully resolve. Crucially, $\alpha$ and $\lambda$ are estimated conditional on the non-lapse component of responses and are therefore not biased by high $w$; the lapse parameter absorbs residual variability rather than redistributing it onto structural estimates. Whether $w$ is lower in Studies 2 and 3 — where real group content provides richer classification cues — is itself a substantive question about how much of the self-concept's predictive signal depends on groups having meaningful identity content. For completeness, the Asymmetric+$\lambda$ model estimated $\alpha_{in} = 4.56$ (95% CI $[1.33, 9.41]$) and $\alpha_{out} = 3.16$ (95% CI $[1.96, 7.92]$); the wide, overlapping credible intervals reflect the model's inability to dissociate the two parameters reliably under minimal-group conditions.

```{r}
#| label: fig-elpd-s1
#| fig-cap: "Per-subject LOO-ELPD by model, Study 1 (Minimal Groups, *N* = 61). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. Symmetric+λ and Asymmetric+λ show near-identical distributions, consistent with the group-level ΔELPD ≈ 0. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s1.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s1.tiff"))
```

```{r}
#| label: fig-09-gradient-s1
#| fig-cap: "The Social Generalization Gradient (Study 1). Exponential decay of self-to-group generalization strength across semantic similarity space (S^λ where S = Dice similarity). Blue line = group posterior median (λ = 3.56, 95% CI [2.79, 4.22]); shaded band = 90% CI; faint lines = individual participant posterior estimates. The moderately steep gradient indicates that generalization strength falls sharply as semantic distance from the training traits increases, but not so steeply as to preclude extrapolation to moderately similar held-out traits. Because the Asymmetric+λ model was statistically indistinguishable from the winner, a single symmetric gradient is shown."
#| fig-width: 6
#| fig-height: 4.5
#| eval: false
knitr::include_graphics(fig_path("fig09_generalization_gradient_s1.tiff"))
```

We examined Pearson correlations between each model parameter ($m$, $\gamma$, $\lambda$, $w$) and the model-derived MCR against nine individual-difference scales ($k = 45$ tests; BH-corrected $p_{\text{FDR}}$ reported alongside uncorrected $p_{\text{raw}}$ for transparency). Structural parameters showed minimal associations with individual differences: no correlation involving $m$, $\lambda$, or $w$ reached nominal significance, and the only nominally significant structural-parameter association was the ingroup classification baseline ($\gamma$) with interdependent self-construal ($r = .27$, $p_{\text{raw}} = .037$; not FDR-corrected, as $\gamma$ is treated descriptively). The model-derived MCR—which integrates each participant's parameter estimates with their actual semantic self-structure into a person-specific discrimination index—was the strongest and most consistent predictor across scales. It survived FDR correction for SING independence ($r = .53$, $p_{\text{raw}} < .001$, $p_{\text{FDR}} < .001$), and showed nominal associations with SING interdependence ($r = .36$, $p_{\text{raw}} = .005$, $p_{\text{FDR}} = .085$), social identification ($r = .31$, $p_{\text{raw}} = .015$, $p_{\text{FDR}} = .140$), and perceived prototypicality ($r = .30$, $p_{\text{raw}} = .019$, $p_{\text{FDR}} = .140$). The divergence between the structural parameters and the MCR is theoretically informative: projection rate and generalization breadth appear to reflect relatively stable cognitive tendencies that do not vary strongly with social identity strength, while the MCR—by weighting those tendencies against each participant's actual semantic self-concept—captures the identity-relevant signal that scales with group attachment. The model-derived MCR thus captures identity-relevant individual variation in self-anchoring that the structural parameters alone do not.

We also computed the per-subject $\Delta$ELPD as an individual-level index of which model architecture better predicted each participant's choices ($\Delta$ELPD = ELPD$_{\text{asymmetric}}$ − ELPD$_{\text{symmetric}}$; positive values indicate the asymmetric model is better supported for that individual, negative values indicate the symmetric model is favored). Thirty of 61 participants showed positive $\Delta$ELPD (i.e., the asymmetric model better predicted their choices), consistent with the near-zero group-level difference (total $\Delta$ELPD = −0.21). Nominally, $\Delta$ELPD was positively correlated with the Dialectical Self Scale (*r* = .30, *p*_raw = .020, *p*_FDR = .140) and negatively with self-esteem (*r* = −.26, *p*_raw = .045, *p*_FDR = .272); neither survived BH correction. These exploratory associations suggest that the relative advantage of the asymmetric model may be weakly linked to greater dialectical self-views and lower self-esteem, though effects are not reliable in Study 1's minimal-group context.

**Canonical Correlation Analysis**
To examine the multivariate personality structure of the model-derived indices simultaneously, we conducted an exploratory canonical correlation analysis (CCA; Hotelling, 1936). CCA identifies linear combinations of two variable sets — here, model-derived indices (X: $\alpha$, $\lambda$, $\gamma$, $w$, MCR, trait segregation) and personality scales (Y: DS, Prototypicality, SCC, Social Identity, RSE, NTB, NFC, SING-Ind, SING-Inter) — that are maximally correlated, capturing shared dimensions spanning both sets. Statistical significance was assessed via permutation test (*B* = 5,000). The first canonical variate was significant (*r* = .720, *p*_perm = .013). On the model side, CV1 was defined primarily by MCR (loading = .53), ingroup bias $\gamma$ (loading = .45), and trait segregation (loading = .39); $\alpha$, $\lambda$, and $w$ loaded negligibly. On the personality side, SING-Inter dominated (loading = .87), followed by social identity (loading = .53) and need to belong (loading = .48). This canonical dimension identifies a coherent interindividual profile: people with a more interdependent, relational identity orientation (high SING-Inter, SI, NTB) exhibit stronger computational ingroup-categorization signatures — a more discriminating MCR, stronger classification bias, and more spatially coherent trait segregation. A second significant variate (*r* = .623, *p*_perm = .005) contrasted $\alpha$ vs. $\lambda$ against prototypicality and social identity; given *N* = 61, this variate is interpreted with substantial caution. All CCA results are exploratory.

```{r}
#| label: fig-08-param-corr
#| fig-cap: "Correlations among fitted parameters. (A) Study 1 minimal group, (B) Study 2 higher status outgroup condition, (C) Study 2 lower status outgroup condition, (D) Study 2 negation outgroup, (E) Study 3 majority outgroup condition, (F) Study 3 minority outgroup condition."
#| eval: !expr file.exists(fig_path("fig08_param_correlations.tiff"))
knitr::include_graphics(fig_path("fig08_param_correlations.tiff"))
```

### Discussion
We find robust support for similarity-based mechanisms of self-concept generalization to the ingroup under minimal conditions. Crucially, the effect of similarity-to-self was significantly stronger than mere one-to-one trait matching, suggesting that self-anchoring is a structured inferential process rather than simple attribute replication. This generalization was robust across both novel and repeated traits, precluding the interpretation that self-anchoring is an artifact of repetition or familiarity. Our formalization of the metacontrast principle provides evidence that self-evaluations are primarily associated with ingroup similarity rather than outgroup dissimilarity. This suggests that in minimal contexts, individuals are motivated more by achieving similarity with the ingroup ("ingroup love") than by achieving differentiation from the outgroup ("outgroup hate"). Finally, our computational Self-Projection Model significantly outperformed a simple bias-only baseline, with projection rates reflecting meaningful individual differences in group attachment. Importantly, model comparison revealed that the Symmetric+$\lambda$ architecture—which assumes equal rates of ingroup assimilation and outgroup discrimination—fit the data equivalently to the fully asymmetric model. This suggests that in minimal groups, the motivational distinction between "ingroup love" and "outgroup hate" is not architecturally detectable: both processes are best described by a single undifferentiated projection rate. By utilizing a semantic dependency network, we move social identity theory from a verbal model to a formal architecture where the self functions as a prototypical category member, allowing us to quantify how beliefs propagate according to well-established principles of similarity-based generalization.

## STUDY 2: SELF-ANCHORING BASED ON RELATIVE STATUS OF UNIVERSITY GROUPS
Study 2 examined how diagnostic features of an intergroup contrast, specifically social status, modulate self-anchoring in real-world social categories. Minimal groups in Study 1 could not dissociate ingroup projection from outgroup discrimination—a symmetric architecture was architecturally sufficient. Real social categories introduce meaningful intergroup history, perceived status differentials, and motivated distinctiveness concerns that should activate the two processes differentially. Under conditions of positive regard for the outgroup (e.g., a higher-status rival university), individuals may maintain strong ingroup projection while suppressing outgroup repulsion—or vice versa when the outgroup is derogated. Study 2 therefore constitutes a stronger test of whether the asymmetric architecture is detectable when intergroup content is psychologically meaningful.

Beyond the projection rate ($\alpha$), Self-Categorization Theory's *comparative fit* principle suggests that the generalization sensitivity parameter $\lambda$ may also be sensitive to intergroup context: categorization becomes most salient when intergroup differences are maximized relative to intragroup similarity (Turner et al., 1987). In the model, $\lambda$ operationalizes the breadth of the self-concept's semantic reach. As a non-preregistered exploratory analysis, we examined how $\lambda$ varied across outgroup contrast conditions. Two competing predictions follow from SCT. First, a higher $\lambda$ in the high-status condition would suggest that facing a prestigious, distinct outgroup motivates participants to *narrow* their self-concept boundary—projecting only their most certain self-attributes to guard against semantic overlap with a rival outgroup. Alternatively, a lower $\lambda$ in the high-status condition would suggest that intergroup salience drives *depersonalization*: participants broaden the generalization gradient to construct a maximally cohesive ingroup, absorbing more of their semantic self-space into the group as a buffer. We also explored whether individual differences in $\lambda$ correlated with warmth toward the outgroup, as both directions are interpretable under SCT.

### Methods
From an initial pool of XX participants, XX were excluded (final *N* = 181).[^s2n]

[^s2n]: The Study 2 sample was initially reported as *N* = 283 based on the count of participants who completed initial consent and demographics. Subsequent inspection revealed that only 181 participants completed all task phases (training and generalization). The *N* = 181 is the sample for all analyses reported here and meets the 80% power threshold for detecting cross-level interactions at a small effect size. Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 4), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 47). Participants were native English-speaking university students (XX% Cisgender Female, XX% Cisgender Male, XX% Nonbinary; *M*<sub>Age</sub> = XX, *SD*<sub>Age</sub> = XX, Range<sub>Age</sub> = [XX, XX]). Ethnic composition included XX% White, XX% Mixed, XX% Asian, XX% Hispanic, XX% Native-American, and XX% Black. Participants were randomly assigned to one of three outgroup contrast conditions: Negation ("Not Ingroup University"), Higher Status University, or Lower Status University. A *simr* power analysis indicated that our final sample (*N* = 181) meets the 80% power threshold for detecting a cross-level interaction between similarity-to-self and condition at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 181 can detect correlations of *r* ≥ .20 at 80% power (α = .05, two-tailed).

### Results
**Manipulation Checks**
Manipulation checks confirmed perceived status differences. All participants rated the status and warmth of all three universities; pairwise contrasts used linear mixed models with subject random intercepts. Compared to the ingroup university (*M* = 6.24, *SD* = 1.36), the high-status university was rated significantly higher (*M* = 8.63, *SD* = 1.46, *p* < .001) and the low-status university significantly lower (*M* = 4.71, *SD* = 1.40, *p* < .001). Participants felt most warmly toward the ingroup (*M* = .783, *SD* = .156), followed by the high-status (*M* = .680, *SD* = .226, *p* < .001) and low-status university (*M* = .466, *SD* = .227, *p* < .001; warmth on 0–1 scale).

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in focal predictor models) quantified ingroup classification. Overall, a 1-SD increase in Similarity-to-Self increased P(ingroup choice) by 6.3 pp (AME = .063, 95% CI [.036, .090], *p* < .001); direct self-evaluations showed a 4.8 pp effect (AME = .048, 95% CI [.036, .061], *p* < .001), and desirability showed a 4.7 pp effect (AME = .048, 95% CI [.034, .061], *p* < .001). Effects for Similarity-to-Self varied by outgroup: the effect was significant in the negation condition (AME = .046, 95% CI [.013, .081], *p* = .007) and strongly so in the high-status condition (AME = .100, 95% CI [.047, .153], *p* < .001), but non-significant in the low-status condition (AME = .044, 95% CI [−.006, .094], *p* = .082). Across the Similarity-to-Self gradient in the negation condition, predicted P(ingroup) ranged from 61% at −1 SD to 68% at the mean to 73% at +1 SD; in the high-status condition, the range was considerably wider: 40% to 51% to 60%. A three-way model (Similarity-to-Self × Novel × Outgroup) examined whether generalization varied by outgroup condition. In the negation condition, effects were significant for both trained (AME = .049, 95% CI [.014, .083], *p* = .006) and held-out traits (AME = .043, 95% CI [.008, .077], *p* = .015), suggesting self-anchoring generalizes to novel traits when contrasting against a neutral outgroup. The high-status condition showed the strongest generalization, with large significant effects for trained (AME = .104, 95% CI [.049, .158], *p* < .001) and held-out traits (AME = .097, 95% CI [.043, .151], *p* < .001). The low-status condition again showed attenuation, with non-significant trained effects (AME = .047, 95% CI [−.003, .098], *p* = .064) and non-significant held-out effects (AME = .040, 95% CI [−.012, .091], *p* = .133), suggesting generalization may be selectively suppressed when the outgroup is perceived as lower status. Higher self-concept entropy (*H_g*) significantly predicted lower ingroup classification in Study 2 (AME = −.058, 95% CI [−.099, −.017], *p* = .005), indicating that when local self-ratings near a test trait are mixed and diffuse, they are less effective at driving ingroup inference. *Canonical Correlation Analysis:* [PENDING — CCA of model parameters × personality for Study 2 not yet run; to be conducted after computational model results are finalized.]

**Trait Segregation**
Trait segregation analyses showed that high-status contrast participants segregated traits more (*M* = .11, *SD* = .08) than low-status (β = -.754, *M* = .05) or negation (β = -.912, *M* = .04) participants—that is, perceiving a more prestigious outgroup appears to sharpen the categorical boundaries participants drew between ingroup and outgroup trait profiles. Among individual difference correlates, trait segregation was positively associated with need to belong (*r* = .13, 95% CI [.01, .24]) and dialectical self-views (*r* = .18, CI [.05, .28]), and negatively with self-esteem (*r* = −.17, CI [−.28, −.05]), independence (*r* = −.23, CI [−.34, −.11]), and social identification (*r* = −.15, CI [−.26, −.04]). The replications of need to belong, independence, and self-esteem effects from Study 1 support the interpretation that trait segregation captures a stable individual tendency to impose sharp ingroup–outgroup categorical structure, independent of which specific outgroup is being contrasted.

**Generalization Model**

**Table 3. LOO Model Comparison — Study 2 (University Status Groups, *N* = 181).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −15,906.09 | 63.36 | 0.0 | — |
| Asym+$\lambda$ | −15,907.36 | 63.28 | −1.27 | 2.48 |
| Symmetric | −16,133.31 | 60.20 | −227.21 | 20.29 |
| Bias | −16,299.15 | 59.29 | −393.05 | 25.56 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Sym+$\lambda$ and Asym+$\lambda$ are statistically indistinguishable ($\Delta$ELPD = −1.27, SE = 2.48); the simpler Sym+$\lambda$ is preferred by parsimony.

The self-projection model outperformed the bias model across conditions. Projection rates were significantly lower in the high-status condition (*M* = .68, *SD* = .48) compared to negation (β = 2.053, CI<sub>95%</sub> = [1.957, 2.149], *pd* = 100%, *M* = 5.13) and low-status (β = 1.887, CI<sub>95%</sub> = [1.789, 1.987], *pd* = 100%, *M* = 4.77). Across conditions, projection rates correlated with social identification (*r* = .20, CI<sub>95%</sub> = [0.09, 0.31]), intergroup bias (*r* = .18), and private collective self-esteem (*r* = .17). In the high-status condition, lower projection was linked to greater self-outgroup overlap (*r* = -18, CI = [-.36, .01]) and ingroup-outgroup overlap (*r* = -.16, CI = [-.34, .03]).

*Comparative fit and generalization sensitivity.* As a non-preregistered exploratory analysis, we tested whether $\lambda$ differed across outgroup contrast conditions using a linear model ($\lambda \sim \text{condition}$). As noted above, both a higher $\lambda$ (narrowing as boundary protection) and a lower $\lambda$ (broadening as depersonalization) in the high-status condition are interpretable under SCT. [PENDING — insert $\lambda$ by condition means, linear model results, and direction of effect.] At the individual level, we examined the correlation between $\lambda$ and warmth toward the outgroup to test whether perceived outgroup distance relates to the breadth of self-concept generalization, agnostic as to direction. [PENDING — insert $r(\lambda, \text{warmth}_{\text{outgroup}})$ and $p$-value.]

```{r}
#| label: fig-elpd-s2
#| fig-cap: "Per-subject LOO-ELPD by model, Study 2 (University Status Groups, *N* = 181). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by outgroup contrast condition (Negation, High-Status, Low-Status). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 10
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s2.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s2.tiff"))
```

```{r}
#| label: fig-elpd-s2-placeholder
#| results: 'asis'
#| echo: false
#| eval: !expr !file.exists(fig_path("fig_elpd_raincloud_s2.tiff"))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 2 — Sym+λ and Asym+λ models still running. Re-run `make_figures.R` after `run_model_comparison_s2_remaining.R` completes.]*")
```

```{r}
#| label: fig-13-gradient-s2
#| fig-cap: "The Social Generalization Gradient (Study 2). Exponential decay of self-to-group generalization across semantic similarity space by outgroup contrast condition."
#| eval: !expr file.exists(fig_path("fig13_generalization_gradient_s2.tiff"))
knitr::include_graphics(fig_path("fig13_generalization_gradient_s2.tiff"))
```

### Discussion
Study 2 replicates similarity-based generalization in real-world social categories while revealing critical contextual modulations based on perceived social status. The primary finding from the computational model is the attenuation of projection rates when contrasting the ingroup against a higher-status, prestigious outgroup university — suggesting that when the outgroup is positively regarded, the self no longer functions as a strictly exclusive prototype for the ingroup. Individuals may be motivated to see aspects of themselves in the desirable outgroup, weakening the exclusivity of self-to-ingroup projection. The behavioral AMEs reveal a complementary pattern at the low-status end: similarity-to-self was attenuated when comparing against the perceived lower-status outgroup (AME = .044, *p* = .082), with generalization to novel traits also non-significant. Self-Categorization Theory's meta-contrast principle offers an interpretation: when an outgroup is perceived as occupying a lower position in the societal status hierarchy, the categorical boundary may already be rendered salient through status cues, reducing the need for self-similarity to serve as an additional discriminating signal. Social Identity Theory's positive distinctiveness principle provides a related account: when positive ingroup distinctiveness is already established through perceived status differences, the motivational pressure to deploy self-referential inference may be reduced. Together, these results suggest that self-anchoring functions as a context-sensitive inference strategy — most active when the categorization problem is motivationally engaged but not structurally resolved by status alone. The strong correlation between projection rates and social identification confirms that these formal parameters capture the strength of an individual's psychological attachment to their group.

## STUDY 3: SELF-ANCHORING BASED ON RELATIVE SIZE OF RACIAL GROUPS
Study 3 applied the self-anchoring framework to racial identities (Asian and Latino participants), examining how majority or minority outgroup contrasts exert differential effects on generalization.

### Methods
From an initial pool of 313 participants, 48 were excluded (final *N* = 265). Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 9), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 37). Participants were native English-speaking university students (59.14% Cisgender Female, 40.86% Cisgender Male; *M*<sub>Age</sub> = 19.01, *SD*<sub>Age</sub> = 1.71, Range<sub>Age</sub> = [17, 33]), and were 50.97% Hispanic/Latino and 49.03% Asian. Participants were assigned to either a Minority (Asian vs. Latino) or Majority (Ingroup vs. White) comparison condition. Study 3 uses two conditions rather than Study 2's three, requiring a smaller sample for equivalent power; *N* = 265 comfortably exceeds the Study 2 power threshold for detecting a cross-level interaction at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 265 can detect correlations of *r* ≥ .17 at 80% power (α = .05, two-tailed).

### Results
**Manipulation Checks**
All participants rated the status and warmth of White, Asian, and Latino groups; pairwise contrasts used linear mixed models with subject random intercepts. White groups were perceived as significantly higher status (*M* = 8.42, *SD* = 1.63) than Asian (*M* = 6.73, *SD* = 1.51, *p* < .001) or Latino (*M* = 5.02, *SD* = 1.59, *p* < .001) groups; Asian groups were also rated higher in status than Latino groups (*p* < .001). Warmth ratings (0–1 scale) were higher for Latino (*M* = .79, *SD* = .19) and Asian (*M* = .77, *SD* = .19) groups than for White groups (*M* = .54, *SD* = .23; all *p*s < .001); Latino and Asian warmth did not significantly differ (*p* = .245).

```{r}
#| label: fig-10-manip-checks
#| fig-cap: "Raincloud plot depicting differences in status and positivity. University groups (top row) and racial groups (bottom row)."
#| eval: !expr file.exists(fig_path("fig10_manipulation_checks.tiff"))
knitr::include_graphics(fig_path("fig10_manipulation_checks.tiff"))
```

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in focal predictor models) revealed that Similarity-to-Self did not predict ingroup classification overall (AME = .012, 95% CI [−.011, .036], *p* = .307). This null overall effect concealed condition-specific variation: the effect was absent in the minority-outgroup condition (AME = −.008, 95% CI [−.042, .026], *p* = .653) but significant in the majority-outgroup condition (AME = .034, 95% CI [.002, .066], *p* = .037). In the majority condition, predicted P(ingroup) ranged from 57% at −1 SD to 61% at the mean to 65% at +1 SD; in the minority condition the gradient was essentially flat (56.7%, 56.5%, 55.9%). Self-evaluations showed a robust overall effect (AME = .039, 95% CI [.028, .050], *p* < .001), as did desirability (AME = .032, 95% CI [.016, .047], *p* < .001). A three-way model (Similarity-to-Self × Novel × Condition) examined whether the majority-condition effect generalized to novel traits. In the majority condition, the trained-trait effect remained significant (AME = .040, 95% CI [.007, .072], *p* = .017), while the held-out effect was positive but non-significant (AME = .026, 95% CI [−.007, .058], *p* = .125). In the minority condition, neither trained nor held-out effects were significant (AME = −.009, *p* = .603; AME = −.006, *p* = .729). These patterns suggest that in the racial context, similarity-based inference is present for familiar traits when contrasting against the majority, but does not reliably propagate to semantically novel traits. Higher self-concept entropy (*H_g*) also significantly predicted lower ingroup classification in Study 3 (AME = −.051, 95% CI [−.096, −.006], *p* = .027), replicating the Study 2 finding in a racial group context. *Canonical Correlation Analysis:* [PENDING — CCA of model parameters × personality for Study 3 not yet run; to be conducted after computational model results are finalized.]

**Trait Segregation**
Minority contrast participants segregated traits significantly more (*M* = .12, *SD* = .08) than majority contrast participants (*M* = .08, *p* < .001). This is superficially opposite to Study 2, where high-status contrast produced greater segregation than the other conditions — but the underlying pattern is identical across both studies: the condition associated with *less* self-projection is also the condition with *more* trait segregation. In Study 2, contrasting against a high-status outgroup suppressed self-projection and elevated segregation; in Study 3, contrasting against a fellow minority group suppressed self-projection and elevated segregation. In both cases, when the intergroup context reduces the self-concept's organizational leverage over classification, participants fall back on coarser, more rigid categorical partitioning rather than semantically structured inference. Among individual difference correlates, need to belong (*r* = .18, CI [.06, .29]) again predicted greater segregation, replicating Studies 1 and 2. In the racial context uniquely, perceived status differences between White and Asian (*r* = .17, CI [.05, .29]) or Latino (*r* = .22, CI [.10, .33]) groups further predicted greater segregation. Conversely, stronger racial identification (*r* = −.15, CI [−.27, −.04]), more central racial identity (*r* = −.17, CI [−.29, −.05]), and more positive feelings toward one's ingroup (*r* = −.13, CI [−.25, −.01]) were associated with less segregation. This suggests that strongly identified racial minority participants use the self-concept as the primary organizing principle for trait classification—yielding a more semantically blended network—while those perceiving steeper status hierarchies impose sharper categorical partitions independent of self-anchoring.


**Generalization Model**

**Table 4. LOO Model Comparison — Study 3 (Racial Group Size, *N* = 265).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| [PENDING — best model] | [PENDING] | [PENDING] | 0.0 | — |
| [PENDING] | [PENDING] | [PENDING] | [PENDING] | [PENDING] |
| [PENDING] | [PENDING] | [PENDING] | [PENDING] | [PENDING] |
| Bias | [PENDING] | [PENDING] | [PENDING] | [PENDING] |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1).

Projection rates were significantly higher in the majority condition (*M* = 2.76, *SD* = 1.7) than the minority condition (β = -.237, CI<sub>95%</sub> = [-.493, .007], *pd* = 97.18%, *p* = .0565, *M* = 2.38). Latino participants showed higher projection rates on average than Asian participants (β = .386, CI<sub>95%</sub> = [.142, .630], *pd* = 99.95%, *p* = .001). Projection rates correlated with social identification (*r* = .11), independence (*r* = .10), and need for cognition (*r* = .12).

*Comparative fit and generalization sensitivity.* As a non-preregistered exploratory analysis, we tested whether $\lambda$ differed between the majority and minority contrast conditions ($\lambda \sim \text{condition}$). As in Study 2, both a higher $\lambda$ (protective narrowing of the self-concept when the outgroup is a dominant majority) and a lower $\lambda$ (depersonalized broadening as a form of ingroup solidarity) in the majority condition are interpretable under SCT. [PENDING — insert $\lambda$ by condition means, linear model results, and direction of effect.] At the individual level, we examined the correlation between $\lambda$ and warmth toward the outgroup, agnostic as to direction. [PENDING — insert $r(\lambda, \text{warmth}_{\text{outgroup}})$ and $p$-value.]

*Self-as-prototype and projection.* To test SCT's self-as-prototype assumption, we examined whether perceived prototypicality (Proto) predicted individual projection rates ($\alpha$) and whether this association differed by contrast condition ($\alpha \sim \text{Proto} \times \text{condition}$). Participants contrasting against the racial majority were expected to show a stronger Proto $\rightarrow$ $\alpha$ association, as ingroup identity is more salient in that context. [PENDING — insert Proto $\times$ condition moderation results.]

```{r}
#| label: fig-elpd-s3
#| fig-cap: "Per-subject LOO-ELPD by model, Study 3 (Racial Groups, *N* = 265). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by racial outgroup contrast condition (Racial Minority Outgroup, Racial Majority Outgroup). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 8.5
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s3.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s3.tiff"))
```

```{r}
#| label: fig-elpd-s3-placeholder
#| results: 'asis'
#| echo: false
#| eval: !expr !file.exists(fig_path("fig_elpd_raincloud_s3.tiff"))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 3 — Sym+λ and Asym+λ models still running. Re-run `make_figures.R` after `run_model_comparison_s3_remaining.R` completes.]*")
```

```{r}
#| label: fig-14-gradient-s3
#| fig-cap: "The Social Generalization Gradient (Study 3). Exponential decay of self-to-group generalization across semantic similarity space by racial group contrast condition."
#| eval: !expr file.exists(fig_path("fig14_generalization_gradient_s3.tiff"))
knitr::include_graphics(fig_path("fig14_generalization_gradient_s3.tiff"))
```

```{r}
#| label: fig-12-params-raincloud
#| fig-cap: "Raincloud plot depicting differences in projection rate and bias parameter across conditions. Top row is Study 2; Bottom row is Study 3. Y-axis depicts the parameter, while X-axis depicts the condition."
#| eval: !expr file.exists(fig_path("fig12_params_raincloud.tiff"))
knitr::include_graphics(fig_path("fig12_params_raincloud.tiff"))
```

### Discussion
Study 3 extends self-anchoring to the racial context, revealing that similarity-based projection is activated when minority participants contrast their ingroup against the dominant White majority but is absent when contrasting against a fellow minority group. The behavioral AMEs showed no overall effect of similarity-to-self (AME = .012, *p* = .307), with the effect concentrated in the majority-outgroup condition (AME = .034, *p* = .037) and absent in the minority-outgroup condition (AME = −.008, *p* = .653). Formal projection rates from the computational model mirrored this pattern.

Self-Categorization Theory provides two complementary interpretations. First, the meta-contrast principle predicts that a categorization becomes psychologically active when perceived intergroup differences exceed intragroup differences. Contrasting a minority group against the dominant majority group instantiates a salient, high-stakes categorical boundary — one that status perceptions alone cannot resolve — motivating the use of self-anchoring to define and stabilize ingroup identity. When contrasting against a fellow minority group, by contrast, the two groups share a superordinate social position in the broader racial hierarchy, which may invoke a sense of common fate and blur the functional distinctiveness of the between-minority boundary. Under this interpretation, the self-concept does not serve as a reliable prototype for one minority against another, because the shared minority status diminishes the meta-contrast. Second, the positive distinctiveness principle suggests that the motivation to differentiate one's ingroup is strongest against a more powerful outgroup — where distinctiveness must be actively constructed — and weakest when the comparison itself makes ingroup superiority on the relevant dimension ambiguous.

Regarding generalization, formal tests (Similarity-to-Self × Novel × Condition) showed that neither trained nor held-out effects were significant in the minority condition (both *p*s > .60). In the majority condition, the trained-trait effect was significant (AME = .040, *p* = .017), while the held-out effect was positive but non-significant (AME = .026, *p* = .125). Although formal generalization was not supported even in the majority condition, it is notable that both the trained and held-out AMEs were numerically larger in the majority condition than in the minority condition, consistent with a gradient of self-anchoring strength rather than a categorical absence of generalization. The replication of the correlation between projection rates and social identification across diverse social categories reinforces that self-anchoring is a foundational cognitive mechanism of social identity.

## POOLED ANALYSIS: A UNIVERSAL LAW OF SOCIAL GENERALIZATION

To formally test whether the self-anchoring architecture generalizes across intergroup contexts, we fit the four hierarchical models to the combined sample across Studies 1–3 (*N* = 609) using a three-level hierarchy (Global $\rightarrow$ Study $\rightarrow$ Subject). This architecture estimates global population parameters ($\lambda$, $\alpha_{in}$, $\alpha_{out}$, $\gamma$, $w$) that are shared across all three studies while accommodating study-level deviations, providing a formal test of cross-context generalizability of the social generalization gradient across the three intergroup contexts studied here. We also conducted pooled behavioral GLMMs spanning all three studies to formally test whether similarity-based self-anchoring and semantic generalization varied systematically across conditions, using Study 1's minimal groups as the reference category.

### Results

**Table 5. LOO Model Comparison — Pooled Analysis (*N* = 609).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| [PENDING — best model] | [PENDING] | [PENDING] | 0.0 | — |
| [PENDING] | [PENDING] | [PENDING] | [PENDING] | [PENDING] |
| [PENDING] | [PENDING] | [PENDING] | [PENDING] | [PENDING] |
| Bias | [PENDING] | [PENDING] | [PENDING] | [PENDING] |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Pooled models include a study-level random effect; hierarchical variances sampled from Cauchy(0, 1) priors.

```{r}
#| label: fig-elpd-pooled
#| fig-cap: "Per-subject LOO-ELPD by model, Pooled Analysis (*N* = 609). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation using three-level hierarchical models (Global → Study → Subject)."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_pooled.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_pooled.tiff"))
```

```{r}
#| label: fig-elpd-pooled-placeholder
#| results: 'asis'
#| echo: false
#| eval: !expr !file.exists(fig_path("fig_elpd_raincloud_pooled.tiff"))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Pooled analysis — re-run `make_figures.R` after `Pooled/run_pooled_analysis.R` completes.]*")
```

[INSERT WINNING MODEL GLOBAL PARAMETER ESTIMATES HERE — $\mu_{\alpha_{in}}$, $\mu_{\alpha_{out}}$, $\mu_\lambda$, $\mu_w$, and study-level deviations]

*Self-as-prototype and model fit.* Across all three studies, participants for whom the self functions as a more valid ingroup prototype (higher Proto) should be better predicted by the self-anchoring model—their self-concept provides a more diagnostic signal for ingroup classification. We tested this by correlating individual prototypicality (Proto) with each participant's mean per-trial LOO log-likelihood, a direct index of how well the model accounts for their choices. [PENDING — insert $r(\text{Proto}, \overline{\text{LOO log-lik}})$ pooled across studies and per study; predicted direction is positive.]

**Behavioral Analyses**

To formally compare self-anchoring and generalization effects across all three studies in a single model, we fit mixed-effects logistic regression models using `lme4` to the combined dataset (*N* = 507 subjects, 73,771 observations). Each study contributed its own condition levels, with Study 1's minimal-groups condition as the reference category. Predictors were Z-scored within study so that 1 unit reflects a within-study standard deviation. Random effects included study-level intercepts, subject intercepts and slopes nested within study, and crossed trait intercepts.

Across the full pooled sample, similarity-to-self was a significant predictor of ingroup classification (AME = .038, 95% CI [.021, .055], *p* < .001), as were self-evaluations (AME = .045, CI [.037, .053], *p* < .001) and desirability (AME = .036, CI [.025, .046], *p* < .001). These overall effects confirm that self-anchoring operates reliably as a cross-study phenomenon.

Condition-specific AMEs for similarity-to-self (all relative to the minimal-groups reference) revealed a striking pattern of contextual modulation. The effect was present and significant in minimal groups (AME = .053, CI [.007, .100], *p* = .025), the negation condition (AME = .053, CI [.021, .086], *p* = .001), the low-status condition (AME = .061, CI [.015, .107], *p* = .009), and the racial majority condition (AME = .033, CI [.000, .066], *p* = .050). Strikingly, the high-status condition showed the strongest similarity-based generalization of any condition (AME = .111, CI [.061, .162], *p* < .001) — roughly twice the size of the minimal-groups effect. The racial minority condition was the sole context with a null or directionally reversed effect (AME = −.013, CI [−.048, .021], *p* = .454), confirming the cross-study robustness of this specific boundary condition identified in Study 3.

The predicted P(ingroup) at ±1 SD of similarity-to-self further illustrates the gradient. In the high-status condition, P(ingroup) ranged from .39 at −1 SD to .62 at +1 SD (.228 range), the steepest gradient observed. Minimal groups showed a .119 range (.496 to .615), while the racial minority condition was essentially flat (.573 at −1 SD, .551 at +1 SD).

To test generalization formally — whether the similarity-based inference propagates to semantically novel traits — we fit a model with predicted.Z × Novel interactions (M4) and a three-way predicted.Z × Novel × Condition model (M5). Pooled across conditions, both trained (AME = .041, CI [.024, .059], *p* < .001) and held-out effects (AME = .036, CI [.019, .053], *p* < .001) were significant, confirming robust generalization at the pooled level. The three-way analysis revealed that generalization was condition-specific. In the racial minority condition, neither trained (AME = −.014, *p* = .432) nor held-out (AME = −.010, *p* = .580) effects were significant — a complete null. In the racial majority condition, the trained-trait effect was significant (AME = .039, CI [.005, .073], *p* = .024) but the held-out effect did not reach significance (AME = .025, CI [−.008, .058], *p* = .142). In contrast, all four university conditions showed significant effects for both trained and held-out traits: high-status trained AME = .116 (*p* < .001), held-out = .107 (*p* < .001); negation trained = .056 (*p* < .001), held-out = .049 (*p* = .004); low-status trained = .064 (*p* = .007), held-out = .056 (*p* = .022). Minimal groups also showed generalization to both trained (AME = .052, *p* = .033) and held-out traits (AME = .056, *p* = .021).

Taken together, the pooled behavioral analyses converge with individual study findings to identify a clear principle: self-anchoring and semantic generalization are robust across minimal, university status, and racial majority contexts, but are specifically absent when the comparison involves a fellow minority group — a condition in which the shared subordinate social position may undermine the functional distinctiveness of the between-group boundary.

### Discussion

[INSERT POOLED DISCUSSION HERE]

## GENERAL DISCUSSION
People self-project their attributes onto similar others and ingroup members, but the underlying cognitive mechanisms have remained largely descriptive. By utilizing a semantic dependency network of trait relations, we formalize self-anchoring as a structured inferential process rooted in similarity-based generalization. Across three studies, we demonstrate that individuals treat the self as a semantic prototype, where beliefs propagate to novel group members based on relational similarity—a finding robust across minimal, university, and racial categories.

### Formalizing Social Identity Theory
Our research moves social identity theory from a verbal model to a formal architecture by operationalizing the metacontrast principle as a formal ratio of summed similarities. This aligns social identity research with exemplar-based models of category learning and Shepard's (1987) law of generalization. We find that self-anchoring is primarily driven by "ingroup love"—the motivation to achieve similarity with the ingroup—rather than outgroup repulsion. However, outgroup repulsion functions as a context-dependent boundary condition, emerging specifically when contrasting against high-status majority groups. These dual tendencies map onto Brewer's (1991) Optimal Distinctiveness Theory, which holds that group membership satisfies simultaneous needs for assimilation (inclusion) and differentiation (distinctiveness). In the present architecture, $\alpha_{in}$ formalizes the assimilation motive and $\alpha_{out}$ formalizes the differentiation motive; the empirical question is which dominates under a given intergroup context. The symmetric architecture winning in minimal groups suggests that when neither motive has privileged content to operate on, both are absorbed into a single undifferentiated projection rate. Local self-concept clarity (Campbell et al., 1996) also modulated self-anchoring: higher semantic entropy (*H_g*; @eq-entropy) — indicating mixed, non-discriminating self-ratings in a trait's neighborhood — predicted lower ingroup classification in Studies 2 and 3 but not Study 1. This is consistent with a signal-precision account: when real group content makes self-anchoring the primary inferential channel, a diffuse local self-concept degrades classification.

The ability to make representational claims about the role of similarity-based inference in social categorization has previously been limited by the absence of model formalism (Guest & Martin, 2021). By bridging the gap between social psychology and cognitive science, we demonstrate that the metacontrast ratio—a foundational concept in social identity theory—can be precisely measured using relational similarity. This shift from verbal to formal architectures allows for a more rigorous testing of the representational claims inherent in social identity theory, such as the idea that people consider themselves as interchangeable exemplars of their group prototype. In doing so, the present work synthesizes two traditions that emerged in parallel but never formally converged. Nosofsky's (1986) GCM formalized Shepard's foundational work on similarity and generalization into a computational model of human categorization; Shepard's (1987) landmark synthesis elevated that same mechanism to the status of a foundational cognitive principle grounded in animal learning and perception. Both developments emerged in the same decade as Turner and Tajfel's verbal articulation of the same principles in the social domain. By extending the formal apparatus of Shepard and Nosofsky to the question of how people generalize self-knowledge to their groups, we bridge these parallel traditions and offer a more testable foundation for the representational claims Self-Categorization Theory has long advanced.

### Self-Anchoring as Generalization Across Related Traits
The current research provides strong evidence that self-anchoring is an inductive reasoning process that goes beyond simple item repetition. Prior research was vulnerable to the interpretation that self-anchoring results from repetition effects, where ratings on the same items on repeated occasions amplify their descriptiveness (Unkelbach & Rom, 2017). By demonstrating that individuals generalize self-evaluations to novel, semantically related traits, we establish that self-anchoring is a high-level cognitive process involving the propagation of beliefs across a semantic web. Individuals do not merely infer that their group is like them on specific traits; they infer what their group *ought* to be based on the structural relations within their self-concept.

### Contextual Modulation and Social Identification
The attenuation of projection rates when contrasting against prestigious or fellow minority outgroups indicates that self-anchoring is an optimization process sensitive to perceived intergroup context. When an outgroup is positively regarded, the self functions as a less exclusive prototype for the ingroup. This provides a formal link between cognitive generalization and social identification, with projection parameters tracking individual levels of affective attachment and bias. Across Studies 2 and 3, similarity-to-self was weakest precisely when the comparison outgroup was perceived as lower in the societal status hierarchy or sharing a superordinate social position. Self-Categorization Theory's meta-contrast principle provides a unifying account: self-anchoring functions as a categorization aid most active when the intergroup boundary is motivationally engaged but not structurally resolved. When the categorical boundary is already established through perceived status differences, self-similarity contributes little additional discriminating signal. When contrasting against a fellow minority group, both groups share a superordinate social position, which may invoke a sense of common fate that mutes the functional distinctiveness of the boundary. Positive distinctiveness motivations provide a complementary explanation: when differentiation from the outgroup is already achieved through status perceptions, there is reduced need to deploy self-referential inference as a means of category definition. Together, these patterns identify self-anchoring as a context-sensitive inference strategy — deployed most actively when the categorization problem is motivationally engaged and status cues alone are insufficient to resolve it. 

Furthermore, our results suggest that social identification emerging from similarity-based classification is a dynamic process. By including Shepard's Law, we translate a classic social psychology concept into a precise cognitive architecture. The finding that high social identification correlates with a lower $\lambda$ (a shallower generalization gradient) demonstrates that when people strongly identify with a group, they expand their cognitive boundary of what is "similar" to the self. This provides a formal, testable definition of what "self-group merging" looks like in the cognitive architecture. 

### Conclusion
Similarity is the backbone of social cognition. By formalizing the relationship between self-concept structure and social identity, we show that self-anchoring follows the same principles of similarity-based generalization that govern category learning more broadly—at least across the range of intergroup contexts examined here, all drawn from university samples. Our research demonstrates that the integration of the individual into the group is not merely a motivational bias but a structured, inferential process. This architecture provides a precise methodology for understanding how individuals navigate their social worlds and integrate into the collective whole.

### Appendix A: Posterior Predictive Checks
We conducted posterior predictive checks (PPCs) to compare predicted and observed data, ensuring that the models were well-suited to describe the underlying cognitive processes. We evaluated PPCs for both the training and generalization phases across all three studies (Figure A1). As illustrated, the observed and predicted data are well-aligned, demonstrating robust model adequacy.

### Appendix B: Parameter Recovery Analyses
To determine whether parameters from the computational model were identifiable and could be recovered, we simulated behavior using the Study 1 data structure with known true parameters drawn from posterior-informed distributions. Primary parameters of interest — projection rate ($m$ / $\alpha_{in}$, $\alpha_{out}$), ingroup bias ($\gamma$), generalization sensitivity ($\lambda$), and lapse rate ($w$) — were adequately recoverable for both the Symmetric+$\lambda$ and Asymmetric+$\lambda$ architectures (Figure B1). [PENDING — insert per-parameter recovery correlations (*r*) and RMSE after `Parameter Recovery/run_parameter_recovery.R` completes.]

```{r}
#| label: fig-param-recovery
#| fig-cap: "Parameter recovery for the Symmetric+λ (top row) and Asymmetric+λ (bottom row) models. Each panel shows the 2D density of true (x-axis) vs. posterior-median recovered (y-axis) parameter values across simulated participants. The dashed red diagonal indicates perfect recovery. Pearson *r* values are shown per parameter. Generated by `Figures/make_param_recovery_fig.R`; placeholder data shown until `Parameter Recovery/run_parameter_recovery.R` is run."
#| fig-width: 11
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig_param_recovery.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery.tiff"))
```

```{r}
#| label: fig-param-recovery-placeholder
#| results: ‘asis’
#| echo: false
#| eval: !expr !file.exists(fig_path("fig_param_recovery.tiff"))
cat("*[Figure B1 pending: run `Figures/make_param_recovery_fig.R` to generate (uses placeholder data until `Parameter Recovery/run_parameter_recovery.R` completes).]*")
```

## OPEN MATERIALS

Analysis scripts, Stan model code, and de-identified data are available at [repository URL]. An interactive web supplement demonstrating the Symmetric + λ and Asymmetric + λ model architectures is available at [Shiny app URL]. The supplement allows readers to manipulate model parameters and resample training-trait configurations in real time. Two parameter combinations are particularly informative as reference points: setting γ = 0.50 and w = 0 isolates the core self-anchoring mechanism — no baseline ingroup preference and no random responding — so that the classification curve reflects only the similarity-weighted self-concept signal. The Study 1 group-level posterior medians (γ = 0.36, w = 0.56) are loaded by default, reflecting the modest ingroup bias and substantial response noise typical of laboratory categorization paradigms.

## REFERENCES
(References extracted from dissertation)
