---
title: "Building 'Us' in the Image of 'I': The Constructive Cognitive Architecture of Social Identity"
shorttitle: "Constructive Architecture of Social Identity"
author:
  - name: Jacob J. Elder
    affiliations:
      - name: University of California, Riverside
        department: Psychology
    corresponding: true
    email: jelder@ucr.edu
abstract: |
  People tend to see themselves as similar to their ingroup, often by projecting self-beliefs onto their perceptions of others. The within-person cognitive mechanisms underlying this process remain under-specified. This research formalizes self-anchoring as similarity-based generalization across a semantic trait network, establishing the relational (e.g., if I am outgoing, my group should be characteristic of semantically related traits like sociable) and contrastive (i.e., how the ingroup compares to a specific outgroup) mechanisms through which self-evaluations generalize to the ingroup. Across three studies using minimal groups (N = 61), university groups (N = 181), and racial groups (N = 265), individuals used semantic similarity among traits to infer group characteristics from their own attributes. Self-anchoring was primarily driven by a motivation to achieve similarity with the ingroup. In the racial context, minority participants contrasting against the racial majority were more strongly driven to achieve dissimilarity from the majority outgroup. The projection rate itself remained invariant across intergroup contexts, but the prior ingroup preference (γ) attenuated sharply when participants contrasted against a positively-regarded, higher-status outgroup (Study 2). In Study 3, similarity-based inference was suppressed entirely under minority–minority outgroup contrasts; in the racial context, pre-existing cultural stereotypes compete with self-anchoring, increasing classification noise and limiting generalization. Model-derived semantic contrast ratios (MCR) correlated with social identification, self-esteem, and prototypicality across studies.
keywords: [self-anchoring, social identity, category learning, semantic similarity, computational modeling]
format:
  apaquarto-docx: default
---

```{r}
#| label: setup
#| include: false
library(here)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.width = "100%")
# Figures are generated by Figures/make_figures.R.
# Run that script first if figures are missing.
fig_path <- function(...) here("Figures", ...)
```

## INTRODUCTION
People carry stable self-beliefs across situations (Markus & Wurf, 1987) yet maintain a sense of belonging (Baumeister & Leary, 1995) by assimilating into their social groups (Brewer, 1991; Ellemers et al., 2001). Through this similarity, social identification emerges—a sense of positive attachment central to group life (Tajfel, 1978; Turner et al., 1987). Social psychology has conceptualized group membership as "depersonalization," where the self is categorized as an interchangeable exemplar of a group prototype (Turner et al., 1987). This account—often termed "self-stereotyping"—emphasizes assimilation of group attributes into the self-concept but does not explain how people identify with novel groups or maintain self-beliefs that remain stable across group memberships (van Veelen et al., 2016).

Rather than only assimilating group attributes, people also project their own attributes onto how they represent their ingroups (M. Cadinu & Rothbart, 1996) and others in interpersonal contexts (Ames, 2004). This process, known as self-anchoring, serves as an informational base (Gramzow et al., 2001) from which people draw inferences about their social environment. Individuals engage in inductive reasoning, inferring unknown information about their group from their own self-knowledge (DiDonato et al., 2011; Krueger, 2007). Self-anchoring is most pronounced when group knowledge is ambiguous or diagnostic information is absent (van Veelen et al., 2013a), making it central to the emergence of social identity.

The present approach differs fundamentally from the social projection literature (Krueger, 1998; Ames, 2004; Van Boven & Loewenstein, 2003), which treats self-to-group inference as a Bayesian base-rate problem: one's own trait level adjusts a prior belief about the group mean, with each trait evaluated independently. We model self-anchoring instead as similarity-based generalization across a structured semantic network. This distinction is consequential: it allows us to test whether self-knowledge propagates *through relational structure* to traits the person never directly evaluated—a form of inference that base-rate accounts cannot generate and that directly constitutes generalization in the category learning sense.

### Inferences About the Ingroup Based on the Self
Despite the apparent strength of evidence for self-anchoring, the majority of research in this domain has relied on correlated ratings of identical traits across the self and group (M. Cadinu & Rothbart, 1996; Otten & Wentura, 2001). While these tests provide evidence of rating stability, they do not necessarily demonstrate *generalization* per se. Furthermore, traditional measures are vulnerable to repetition effects; the mere repetition of information can cause it to be perceived as more characteristic (Unkelbach et al., 2019). A rigorous test of the generalization-based theory of self-anchoring requires establishing that self-evaluations generalize across semantically related but novel traits (Heit & Rubinstein, 1994). For example, if an individual perceives themselves as "outgoing," do they infer that their group is characteristic of semantically similar traits like "sociable" and "fun," even if they have not explicitly evaluated themselves on those specific attributes?

In the current research, we move social identity theory from a verbal, descriptive model to a formal architecture by integrating principles of category learning. We frame the self as a semantic prototype in a high-dimensional space, where group beliefs emerge through similarity-based generalization consistent with Shepard's (1987) universal law of generalization. To formalize this process, we utilize a semantic dependency network of 147 positive traits, constructed using data from 178 Amazon Mechanical Turk participants with a 25% consensus threshold. From this network, we derive relational similarity measures (network-based Dice similarity; Equation 1) that allow us to quantify how self-representations propagate across the trait network.

This network approach enables the first formal implementation of the "metacontrast principle," which posits that group categorization is defined by the ratio of an individual’s similarity to the ingroup relative to the individual’s similarity to the outgroup (Turner et al., 1987). While the metacontrast principle has been central to social identity research for decades, it has remained a verbal description (Davis & Goldwater, 2021). Structurally, Turner's metacontrast ratio is formally isomorphic to Nosofsky's (1986) Generalized Context Model—both define category membership via a ratio of summed similarities; we provide the formal backbone Turner's verbal architecture required. By applying a category learning framework to social identity, we provide a formal test of whether intergroup contrast accentuates self-anchoring and how individuals balance the motivation for ingroup similarity against outgroup differentiation.

### Relational Similarity as the Basis for Self-Concept Generalization
Generalizing from known to novel stimuli based on similarity is a core cognitive capacity (Shepard, 1987). In prior work, we developed a semantic network of trait dependencies (J. Elder et al., 2023) to extract relational similarity based on shared semantic neighbors, moving beyond simple trait-for-trait matching. Similarity-based inference drives both classification within categories and contrast of distinctive features between them (Tversky, 1977).

Social identity research has borrowed heavily from cognitive science research on concept learning, yet it has rarely implemented the formalism leveraged by that field. The ability to make representational claims about the role of similarity-based inference in social categorization has previously been limited by the absence of model formalism (Guest & Martin, 2021). Here, we bridge this gap by implementing formal category learning models—such as the Generalized Context Model (Nosofsky, 1986)—to test the principles of social categorization in a self-anchoring context. This formal bridge between Shepard's (1987) universal law of generalization, Nosofsky's GCM, and Turner's metacontrast principle constitutes the paper's central theoretical ambition: to instantiate in a computational model what social identity theory has long claimed in words.

### The Current Design
We utilize a "training-to-generalization" paradigm common in concept learning research (Bowman et al., 2020). Participants first self-evaluate on a subset of traits (training phase), which serve as exemplars of the self-concept prototype. This is followed by a "generalization phase" where participants classify traits—including novel traits not seen during training—as more characteristic of either the ingroup or outgroup. Using the traits’ semantic similarities to the self-concept, we predict the likelihood of ingroup classification.

Across three studies, we examine how various intergroup contexts amplify or attenuate these generalization weights. Study 1 utilizes minimal groups to provide a proof-of-concept for similarity-based generalization. Study 2 examines the role of relative social status using university groups, testing whether status context modulates the prior ingroup preference (γ), the projection rate (α), or the breadth of self-concept generalization (λ)—and whether real social categories with meaningful status histories can dissociate ingroup assimilation from outgroup repulsion in ways that minimal groups cannot. Study 3 applies this framework to racial identities, examining how majority or minority outgroup contrasts exert differential effects on the tendency to self-anchor. This framework operationalizes the "sense of sameness" (James, 1890) underlying group identification.

## STUDY 1: SELF-ANCHORING BASED ON MINIMAL CONDITIONS
Study 1 provided a first proof-of-concept for similarity-based generalization in a minimal group context where group knowledge is absent. Study 1 was pre-registered at OSF (https://osf.io/7jn3e). We pre-registered three predictions: that Similarity-to-Self (SS) predicts ingroup classification, that this effect extends to novel unseen traits, and that individual differences in independent self-construal, self-esteem, need for cognition, and self-concept clarity would correlate with self-anchoring strength. Computational modeling analyses and MCR-based individual differences are exploratory.

### Methods
**Participants**
From an initial pool of 80 participants, 19 were excluded (final *N* = 61). Exclusions were applied for: failure to consent to data use after debriefing (*n* = 9), self-reported low task seriousness (< 4 on a 7-point item; *n* = 1), self-reported unusable data (*n* = 2), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 10). Participants were native English-speaking university students (40.98% Cisgender Female, 59.02% Cisgender Male; *M*<sub>Age</sub> = 19.95, *SD*<sub>Age</sub> = 1.51, Range<sub>Age</sub> = [18, 25]), with an ethnic composition of 9.84% White/Caucasian, 11.48% Mixed/Other, 32.79% Asian, 40.98% Hispanic/Latino, and 4.92% Native-American. A power analysis using *simr* (Green & MacLeod, 2016) on a prior relational similarity dataset indicated that *N* = 5 was sufficient to detect within-subjects effects at 95% power. This seemingly low threshold reflects the statistical structure of multilevel models: within-subjects fixed effects are powered by Level-1 observations — here, 148 binary classification trials per participant — rather than by the number of Level-2 clusters. With 148 observations per person, detecting fixed effects on within-person variation achieves high power at small N; the final sample of *N* = 61 provides substantial additional power and enables detection of between-person individual differences. Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 61 can detect correlations of *r* ≥ .34 at 80% power (α = .05, two-tailed).

**Network Procedure**
We utilized a semantic dependency network of 147 traits constructed using data from 178 Amazon Mechanical Turk participants (25% consensus threshold). This network captures psychological implication structure (e.g., "If I am brave, I am adventurous") rather than linguistic co-occurrence. Static word embeddings (e.g., GloVe) are ill-suited for this purpose on two grounds: antonyms acquire high cosine similarity because they appear in identical sentence contexts, and cosine similarity is symmetric, discarding the directional dependencies (e.g., *Thoughtful* → *Humble* but not vice versa) that the dependency network preserves. From this network, we derived network-based Dice similarity (@eq-dice), representing the proportion of shared neighbors between traits.

$$S_{ij} = \frac{2|N(i) \cap N(j)|}{|N(i)| + |N(j)|}$$ {#eq-dice}

where $N(i)$ and $N(j)$ denote the neighbor sets of traits $i$ and $j$ in the semantic dependency network.

A visualization of the full semantic trait network is provided in Supplementary Materials F.

**Design**
*Training phase.* Participants self-evaluated approximately 60% of the network (90 traits) on a Likert scale from 1 (*Not at all*) to 7 (*Extremely*). Following a dot-estimation minimal group assignment task (NEST), participants were randomly assigned to be "overestimators" or "underestimators." In the *generalization phase*, participants classified all 148 traits in the network as characteristic of either the ingroup or outgroup (148 trials). This included 90 repeated traits and 58 novel traits.

```{r}
#| label: fig-02-task-schematic
#| fig-cap: "Schematic of task design. Depicting training phase on top and generalization phase on bottom. Participants self-evaluate on 90 out of 148 traits on a Likert scale from 1 to 7. During generalization phase, 90 traits are thus repeated while 58 traits are novel and never received a self-evaluation. Participants then proceed through all traits in the semantic trait network, and classify whether each trait is characteristic of the ingroup or the outgroup."
#| eval: !expr file.exists(fig_path("fig02_task_schematic.tiff"))
knitr::include_graphics(fig_path("fig02_task_schematic.tiff"))
```

**Indices**
We computed *Similarity-to-Self* ($SS_g$; @eq-ss) as a similarity-weighted average of self-evaluations across training traits, capturing the degree to which the self-concept predicts the semantic neighborhood of each test trait. Results for a local self-concept clarity index (*H_g*) are reported in Supplementary Materials D.

$$SS_g = \frac{\sum_{t=1}^{T} E_t \cdot S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$ {#eq-ss}

where $E_t$ is the self-evaluation on training trait $t$, $S_{tg}$ is the Dice similarity between training trait $t$ and test trait $g$, and $T$ is the number of training traits.

Each computational model produces a *model-derived Metacontrast Ratio* (MCR) as a generated quantity (see *Computational Modeling* below), computed using parameter-calibrated similarity weights and individual projection gradients: $\text{MCR}_t = \text{simW}_{\text{in},t} / \text{simW}_{\text{out},t}$, where $\text{simW}_{\text{in}}$ and $\text{simW}_{\text{out}}$ are the generalization-weighted sums of projection onto ingroup- and outgroup-predictive self-knowledge, respectively. The subject-level MCR ($\overline{\text{MCR}}_s$) averages this ratio across trials, yielding a person-specific index of how strongly the semantic self-concept discriminates ingroup from outgroup classification.

**Computational Modeling**
We compared four cognitive architectures based on category learning principles (Nosofsky, 2011) to test the representational structure of self-anchoring.

**Level 1: Bias Model (Motivational Baseline).** This model represents a general tendency to choose the ingroup regardless of trait content, serving as a baseline for ingroup favoritism:
$$P(\text{Ingroup} | g) = \text{logit}^{-1}(\text{logit}(\gamma))$$
where $\gamma$ is the bias parameter.

**Level 2: Symmetric Model (Traditional Self-Anchoring).** This model utilizes a single projection rate ($\alpha$) assuming that the rate of ingroup assimilation is mathematically identical to the rate of outgroup repulsion:
$$P(\text{Ingroup} | g) = \frac{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta}{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta + (1-\gamma) \cdot (\sum_{t=1}^T S_{tg} \cdot (1-G_t))^\beta}$$
where $G_t = \frac{1}{1 + e^{-\alpha(E_t-4)}}$ represents the latent belief transformed from self-evaluations ($E_t$).

**Level 3: Symmetric + $\lambda$ Model (The Generalization Gradient).** This model introduces Shepard’s Law by adding a generalization sensitivity parameter ($\lambda$), representing the decay of inference across semantic similarity ($S_{tg} \rightarrow S_{tg}^\lambda$). This architecture treats $\lambda$ as a core parameter defining the structural reach of the self-concept, independent of social target or bias. 

```{r}
#| label: fig-05-lambda-identifiability
#| fig-cap: "How Shepard's Law (λ) Unlocks Parameter Identifiability. As λ increases, the generalization gradient becomes steeper, restricting the influence of self-evaluations to only local semantic neighbors. This 'flattening' of influence for more distant novel traits provides the mathematical leverage necessary to distinguish the structural reach of the self-concept (λ) from the extremity of social projection (α)."
#| eval: !expr file.exists(fig_path("fig05_lambda_identifiability.tiff"))
knitr::include_graphics(fig_path("fig05_lambda_identifiability.tiff"))
```

**Level 4: Asymmetric + $\lambda$ Model (The Full Architecture).** This model decouples the assimilation and repulsion processes into distinct parameters, $\alpha_{in}$ and $\alpha_{out}$, to test if social identity is driven by "ingroup love" or "outgroup hate":
$$G_{in,t} = \frac{1}{1 + e^{-\alpha_{in}(E_t-4)}} ; \quad G_{out,t} = \frac{1}{1 + e^{\alpha_{out}(E_t-4)}}$$
By utilizing novel traits to establish the baseline "semantic radius" via $\lambda$, the model possesses the mathematical leverage to decouple these otherwise collinear slopes, unlocking the asymmetric forces central to social identity theory. 

To ensure identifiability of these parameters within a 2AFC task, we leveraged three computational strategies. First, we exploited the unique information provided by novel versus repeated traits; while repeated traits primarily inform projection extremity ($\alpha$), novel traits isolate the signal for generalization sensitivity ($\lambda$) by forcing the model to rely entirely on the semantic similarity matrix ($S$). Second, we implemented the dual latent belief structure described above, allowing the model to distinguish choices driven by ingroup similarity from those driven by outgroup dissimilarity. Finally, we utilized hierarchical Bayesian regularization to stabilize individual estimates: by sharing statistical strength across participants, individual parameter estimates are shrunk toward the group mean, preventing extreme estimates from subjects with noisy or sparse data from distorting inference. To account for potential non-systematic noise in participant responses (e.g., accidental button presses or lapses in attention), we incorporated a lapse parameter ($w$) into all four architectures. This parameter estimates the probability that a given choice was a result of random guessing (fixed at $P = 0.5$) rather than the underlying cognitive model, such that the final probability of an ingroup choice is defined as:
$$P(\text{Ingroup}) = w \cdot 0.5 + (1 - w) \cdot P_{\text{model}}$$
This addition ensures that occasional outlying responses do not unduly bias the estimation of the structural parameters ($\lambda$, $\alpha$). Critically, $\gamma$ and $w$ are jointly identifiable because they exert influence at structurally distinct points on the choice function: $\gamma$ operates *inside* the logistic as an intercept shift, governing the response boundary when semantic evidence is ambiguous and balanced; $w$ operates *outside* the logistic, compressing only the asymptotes of the choice distribution and drawing its information from trials where the deterministic component predicts near-certainty but the participant responds inconsistently. Because each parameter leverages a different region of the psychometric function — the center versus the tails — they do not trade off in estimation. In addition to log-likelihood (used for LOO-CV model comparison), each model outputs, as generated quantities, trial-level predicted choice probabilities ($\hat{P}_t = w \cdot 0.5 + (1-w) \cdot P_{\text{model},t}$) and a model-derived Metacontrast Ratio ($\widehat{\text{MCR}}_t = \text{simW}_{in,t} / \text{simW}_{out,t}$), where $\text{simW}_{in,t}$ and $\text{simW}_{out,t}$ are the parameter-calibrated ingroup and outgroup similarity totals at trial $t$. This model-derived quantity is calibrated by each participant's posterior parameter estimates, incorporating both generalization breadth ($\lambda$) and projection slopes ($\alpha_{in}$, $\alpha_{out}$), making it person-specific: two participants with identical behavioral responses but different estimated parameters will yield different model MCRs, as the metric reflects each person's underlying representation of how strongly a given trait's semantic neighborhood predicts ingroup versus outgroup membership. This hierarchical structure was extended to a pooled analysis across all three studies, treating each study as an exchangeable sample of a broader human social-cognitive architecture (Global $\rightarrow$ Study $\rightarrow$ Subject). To ensure robust estimation across these distinct contexts, hierarchical variances were sampled from Cauchy distributions, providing the necessary regularization to accommodate the small hierarchical sample size. This architecture allowed for the formal estimation of "Global Mean" parameters ($\lambda$, $\alpha$, $w$) that capture cross-context structural properties of social generalization across the three intergroup contexts studied here. Models were fitted using Stan (four MCMC chains; 2,000 post-warmup samples per chain for individual-study models; 1,000 for the pooled three-level model). Convergence was confirmed via $\hat{R} < 1.01$ (Vehtari et al., 2021).

**Table 1. Summary of Computational Model Architectures.**

| Model | *k* | Parameters | Description |
|:------|:---:|:-----------|:------------|
| Bias | 2 | $\gamma$, $w$ | Ingroup favoritism baseline. Choices driven entirely by response bias; no role for trait similarity or self-knowledge. |
| Symmetric | 3 | $\alpha$, $\gamma$, $w$ | Single projection rate; ingroup assimilation and outgroup repulsion are mathematically yoked ($\alpha_{in} = \alpha_{out}$). |
| Symmetric+$\lambda$ | 4 | $\alpha$, $\gamma$, $\lambda$, $w$ | Adds Shepard's generalization gradient; the reach of the self-concept across semantic space is governed by a sensitivity parameter $\lambda$, but projection remains symmetric. |
| Asymmetric+$\lambda$ | 5 | $\alpha_{in}$, $\alpha_{out}$, $\gamma$, $\lambda$, $w$ | Full architecture. Decouples ingroup assimilation ($\alpha_{in}$) from outgroup repulsion ($\alpha_{out}$), allowing independent estimation of "ingroup love" and "outgroup hate." |

*Note.* $k$ = number of free parameters. $\alpha$ / $\alpha_{in}$ / $\alpha_{out}$ = projection rate(s) (0–10); $\gamma$ = response bias (0–1); $\lambda$ = generalization sensitivity (0–5); $w$ = lapse rate (0–1). All models estimated via hierarchical Bayesian inference; subject-level parameters are drawn from a group-level distribution with non-centered parameterization.


```{r}
#| label: fig-03-parameter-space
#| fig-cap: "Parameter space of the Self-Projection Model. Rows vary generalization sensitivity (λ: Low = 0.5, High = 4.0); columns vary projection rate (α: Low = 0.5, High = 3.5). Each panel shows how P(ingroup) changes as a function of a test trait's semantic similarity to the self-concept (x-axis) for a hypothetical participant. Low-λ curves are shallow (self-knowledge generalizes broadly across dissimilar traits); high-λ curves are steep (self-knowledge generalizes narrowly to close semantic neighbors only). Low-α curves cluster near chance (0.5; weak projection); high-α curves diverge strongly from chance (strong projection). The Venn diagrams at right illustrate the qualitative distinction: Low-λ/High-α produces a broad projection footprint spanning the full trait network (large circle overlap), whereas High-λ/Low-α produces a narrow footprint concentrated on the most similar traits (small overlap). Dashed line = chance (0.50)."
#| eval: !expr file.exists(fig_path("fig03_parameter_space_visualization.tiff"))
knitr::include_graphics(fig_path("fig03_parameter_space_visualization.tiff"))
```

```{r}
#| label: fig-04-parameter-illustration
#| fig-cap: "From self-ratings to ingroup classifications: the role of projection rate and generalization sensitivity. (A) Self-rating profile for eight hypothetical training traits forming two semantic clusters (social: Sociable, Warm, Outgoing, Friendly; quiet/neutral: Organized, Accurate, Quiet, Reserved). Dashed line = neutral midpoint (4). (B) Dice similarity heatmap showing the two-cluster semantic structure. (C) Predicted P(ingroup) for a *low-projection* participant (α = 0.5, λ = 1.0): predictions are broadly distributed and modestly above chance, with little contrast between social and quiet traits. (D) Predicted P(ingroup) for a *high-projection* participant (α = 3.0, λ = 3.5): predictions are sharply amplified—highly-rated social traits (trained and novel) approach 85–90% ingroup, while low-rated quiet traits drop to ~35–40%. Both profiles show that the model generalizes to semantically novel traits (light bars) by propagating beliefs through the similarity structure, not just repeating training-phase labels."
#| eval: !expr file.exists(fig_path("fig04_parameter_illustration.tiff"))
knitr::include_graphics(fig_path("fig04_parameter_illustration.tiff"))
```

### Results
Predictors of ingroup classification were estimated using mixed-effects logistic regression with crossed random effects for subjects and traits; random slopes were estimated for focal predictors; in models testing cross-level interactions (a within-person predictor × between-person moderator), a random slope was always included for the level-1 predictor. Subject random intercepts account for baseline differences in individuals' overall tendency to select the ingroup regardless of trait content — capturing stable between-person variation in ingroup favoritism. Trait random intercepts account for baseline differences in how often a given trait is attributed to the ingroup regardless of who is rating it — capturing stable between-trait variation in perceived ingroup typicality. This structure ensures that fixed-effect estimates reflect within-person, within-trait associations rather than confounds from person-level response tendencies or trait-level ingroup stereotypicality. We report average marginal effects (AMEs) with 95% confidence intervals and two-tailed *p*-values. Desirability reliability was good, ICC(C, 16) = .682 [.601, .753].

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in models for self-evaluations and similarity-to-self) quantified predictors of ingroup classification. Consistent with pre-registered predictions, a 1-SD increase in *Similarity-to-Self* increased P(ingroup) by 7.0 percentage points (AME = .070, 95% CI [.028, .111], *p* = .001), substantially larger than the 6.3 pp effect of direct self-evaluations (AME = .063, 95% CI [.040, .086], *p* < .001), replicating traditional self-anchoring. Desirability was non-significant (AME = .016, 95% CI [−.002, .034], *p* = .075). Across the Similarity-to-Self gradient, predicted P(ingroup) ranged from 48% at −1 SD to 56% at the mean to 64% at +1 SD. Also consistent with pre-registered predictions, the effect did not differ between trained and novel traits (Trained AME = .069, Novel AME = .073; difference = .004 pp, 95% CI [−.013, .020]), confirming practical equivalence and ruling out repetition as an explanation.
```{r}
#| label: fig-06-equivalence
#| fig-cap: "Depiction of probability of significance and equivalence test in Study 1. Vertical line denotes the threshold for significance (β > ±.18). Red = proportion within the Region of Practical Equivalence (ROPE); blue = proportion that is significant."
#| eval: false
knitr::include_graphics(fig_path("fig06_equivalence_test.tiff"))
```

```{r}
#| label: fig-07-marginal-effects
#| fig-cap: "Predictors of ingroup classification: Desirability, self-evaluations, and similarity-to-self. Plotted using average marginal predictions (marginaleffects package) ± 95% CI. Top row is Study 1 (Minimal Groups). Middle row is Study 2 (University Status). Bottom row is Study 3 (Racial Groups). Left column: desirability; center: self-evaluations; right: similarity-to-self. X-axis = Z-scored predictor (−1 SD, Mean, +1 SD); Y-axis = predicted P(ingroup classification). Colors denote outgroup conditions within each study. Dashed line = chance (0.50). Generated from Results/marginal_effects_s*_predictions.csv."
#| fig-width: 10
#| fig-height: 10
#| eval: !expr file.exists(fig_path("fig07_marginal_effects.tiff"))
knitr::include_graphics(fig_path("fig07_marginal_effects.tiff"))
```


*SCT depersonalization and self-anchoring.* SCT predicts that stronger identifiers should show tighter alignment between self-ratings and ingroup classification, as depersonalization aligns self-beliefs with group-predictive attributes. We tested this with interaction terms (self-evaluation × SI; self-evaluation × Prototypicality; self-evaluation × SING.Ind) added to the primary classification model, with a random slope for self-evaluations by subject. None reached significance in Study 1: social identification (β = −.018, *z* = −0.30, *p* = .768), prototypicality (β = .014, *z* = 0.23, *p* = .820), independent self-construal (β = .036, *z* = 0.56, *p* = .573). In minimal groups, identification strength does not amplify the self-to-group classification link — consistent with the absence of group content that could anchor identification-based depersonalization.

**Trait Segregation**

```{r}
#| label: fig-trait-segregation
#| fig-cap: "Conceptual illustration of trait segregation (network homophily) in a semantic trait network. Each node represents a personality trait; edges connect semantically similar traits. Node color indicates group classification (blue = Ingroup, pink = Outgroup). *Left:* High trait segregation — semantically similar traits receive the same group label, producing two spatially coherent ingroup and outgroup neighborhoods. *Right:* Low trait segregation — ingroup and outgroup labels are scattered across the semantic structure regardless of semantic proximity."
#| fig-width: 10
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_trait_segregation.tiff"))
knitr::include_graphics(fig_path("fig_trait_segregation.tiff"))
```

```{r}
#| label: fig-trait-segregation-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_trait_segregation.tiff")))
cat("*[Figure pending: run `Figures/make_trait_segregation_fig.R` to generate.]*")
```

*Trait segregation* (network nominal homophily) quantifies how much a participant's ingroup versus outgroup classifications cluster along the semantic similarity network—whether semantically connected traits tend to receive the same group label (*M* = .09, *SD* = .08; range [−.04, .26]). Higher values indicate that participants carved sharper, spatially coherent ingroup and outgroup regions out of the trait network; lower values indicate that ingroup and outgroup labels were intermixed across the semantic structure.

**Model Performance and Parameters**
We compared four cognitive architectures of social inference: Bias, Symmetric, Symmetric+$\lambda$, and Asymmetric+$\lambda$ (see Table 1 for architecture summary). Model selection used leave-one-out cross-validation (LOO-CV; Vehtari et al., 2017), with models ranked by expected log predictive density (ELPD); $\Delta$ELPD is reported relative to the best-fitting model. Log-likelihood was stored at the trial level rather than the subject level, enabling observation-level LOO and reliable Pareto $k$ diagnostics; greater than 95% of trials had $k < 0.7$ across models, confirming the validity of the PSIS approximation (Vehtari et al., 2017). To complement the group-level comparison, we computed each participant's *per-subject LOO ELPD difference* (per-subject $\Delta$ELPD = $\text{ELPD}_{\text{asymmetric}} - \text{ELPD}_{\text{symmetric}}$), summing pointwise ELPD values across that participant's valid trials. A positive per-subject $\Delta$ELPD indicates the asymmetric architecture better predicts that individual's choices; a negative value indicates the symmetric architecture is favored. This person-specific index was examined against individual-difference measures to test whether particular psychological characteristics predict which model best accounts for a given participant's behavior.

**Table 2. LOO Model Comparison — Study 1 (Minimal Groups, *N* = 61).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Symmetric+$\lambda$ | −5647.5 | 29.2 | 0.0 | — |
| Asymmetric+$\lambda$* | −5647.7 | 29.1 | −0.21 | 0.55 |
| Symmetric | −5760.4 | 25.6 | −112.9 | 13.0 |
| Bias | −5839.0 | 24.7 | −191.4 | 16.2 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy. *One divergent transition; $\hat{R}_{\max} = 1.006$.

The Symmetric+$\lambda$ model provided the best predictive fit (ELPD = $-5647.5$, SE = $29.2$), meaningfully outperforming the Symmetric model ($\Delta$ELPD = $-112.9$, SE = $13.0$; $|\Delta\text{ELPD}|/\Delta\text{SE} = 8.7$) and the Bias model ($\Delta$ELPD = $-191.4$, SE = $16.2$). The Asymmetric+$\lambda$ model was statistically indistinguishable from the winner ($\Delta$ELPD = $-0.21$, SE = $0.55$; $|\Delta\text{ELPD}|/\Delta\text{SE} = 0.38$), while producing one divergent transition ($\hat{R}_{\max} = 1.006$). Together these results indicate that in minimal groups, decoupling ingroup projection ($\alpha_{in}$) from outgroup discrimination ($\alpha_{out}$) affords no reliable improvement in predictive accuracy: a symmetric projection rate captures the data as well as an asymmetric one. Group-level parameter medians for the Symmetric+$\lambda$ model were: projection rate $\alpha = 2.80$ (95% CI $[1.50, 6.67]$), generalization sensitivity $\lambda = 3.56$ (95% CI $[2.79, 4.22]$), ingroup classification baseline $\gamma = 0.36$ (95% CI $[0.28, 0.45]$), and lapse rate $w = 0.56$ (95% CI $[0.39, 0.70]$). The elevated lapse rate under minimal group conditions is interpretable rather than artifactual: when groups carry no prior content, a substantial portion of trial-by-trial variability is structurally underdetermined — participants must classify 148 traits for a group defined by nothing beyond an arbitrary assignment label, producing genuine choice indeterminacy the similarity structure cannot fully resolve. Importantly, $\alpha$ and $\lambda$ are estimated conditional on the non-lapse component of responses and are therefore not biased by high $w$; the lapse parameter absorbs residual variability rather than redistributing it onto structural estimates. Whether $w$ is lower in Studies 2 and 3 — where real group content provides richer classification cues — is itself a substantive question about how much of the self-concept's predictive signal depends on groups having meaningful identity content. For completeness, the Asymmetric+$\lambda$ model estimated $\alpha_{in} = 4.56$ (95% CI $[1.33, 9.41]$) and $\alpha_{out} = 3.16$ (95% CI $[1.96, 7.92]$); the wide, overlapping credible intervals reflect the model's inability to dissociate the two parameters reliably under minimal-group conditions.

```{r}
#| label: fig-elpd-s1
#| fig-cap: "Per-subject LOO-ELPD by model, Study 1 (Minimal Groups, *N* = 61). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. Symmetric+λ and Asymmetric+λ show near-identical distributions, consistent with the group-level ΔELPD ≈ 0. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s1.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s1.tiff"))
```

```{r}
#| label: fig-09-gradient-s1
#| fig-cap: "The Social Generalization Gradient (Study 1). Exponential decay of self-to-group generalization strength across semantic similarity space (S^λ where S = Dice similarity). Blue line = group posterior median (λ = 3.56, 95% CI [2.79, 4.22]); shaded band = 90% CI; faint lines = individual participant posterior estimates. The moderately steep gradient indicates that generalization strength falls sharply as semantic distance from the training traits increases, but not so steeply as to preclude extrapolation to moderately similar novel traits. Because the Asymmetric+λ model was statistically indistinguishable from the winner, a single symmetric gradient is shown."
#| fig-width: 6
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig09_generalization_gradient_s1.tiff"))
knitr::include_graphics(fig_path("fig09_generalization_gradient_s1.tiff"))
```

The following individual-difference analyses are exploratory. We examined Pearson correlations between each model parameter ($m$, $\gamma$, $\lambda$, $w$) and the model-derived MCR against nine individual-difference scales (FDR correction applied separately for mechanism-personality tests [$k = 36$: $m$, $\gamma$, $\lambda$, MCR × 9 scales] and for ΔELPD-personality tests [$k = 9$]; $w$ reported descriptively). Structural parameters showed minimal associations: $m$, $\lambda$, and $w$ showed no nominal associations, and $\gamma$ showed no FDR-significant associations (best: SING.Inter $r = .27$, $p_{\text{raw}} = .039$, $p_{\text{FDR}} = .279$). The model-derived MCR—which integrates each participant's parameter estimates with their actual semantic self-structure into a person-specific discrimination index—was the strongest and most consistent predictor across scales. It survived FDR correction for SING independence ($r = .53$, $p_{\text{raw}} < .001$, $p_{\text{FDR}} < .001$), and showed nominal associations with SING interdependence ($r = .36$, $p_{\text{raw}} = .005$, $p_{\text{FDR}} = .085$), social identification ($r = .31$, $p_{\text{raw}} = .015$, $p_{\text{FDR}} = .170$), and perceived prototypicality ($r = .30$, $p_{\text{raw}} = .019$, $p_{\text{FDR}} = .170$). The divergence between the structural parameters and the MCR is theoretically informative: projection rate and generalization breadth appear to reflect relatively stable cognitive tendencies that do not vary strongly with social identity strength, while the MCR—by weighting those tendencies against each participant's actual semantic self-concept—captures the identity-relevant signal that scales with group attachment. The model-derived MCR thus captures identity-relevant individual variation in self-anchoring that the structural parameters alone do not.

We also computed the per-subject $\Delta$ELPD as an individual-level index of which model architecture better predicted each participant's choices ($\Delta$ELPD = ELPD$_{\text{asymmetric}}$ − ELPD$_{\text{symmetric}}$; positive values indicate the asymmetric model is better supported for that individual, negative values indicate the symmetric model is favored). Thirty of 61 participants showed positive $\Delta$ELPD (i.e., the asymmetric model better predicted their choices), consistent with the near-zero group-level difference (total $\Delta$ELPD = −0.21). $\Delta$ELPD was not reliably associated with any individual-difference scale (all *r*s ≤ .20, all *p*s ≥ .127 with FDR correction applied separately over the 9 ΔELPD-personality tests). In the minimal-group context, which model better fits an individual's choices does not meaningfully vary with their personality profile.

A pooled CCA combining all three studies (*N* = 507) is reported in Supplementary Materials E; individual-study CCAs are not reported given the sample-size constraints of single-study CCA with 15 variables.

```{r}
#| label: fig-mcr-personality
#| fig-cap: "MCR × Independent Self-Construal (SING.Ind) across Studies 1–3. Each panel shows the relationship between the model-derived Metacontrast Ratio and SING.Ind independence scores. The correlation was FDR-significant in all three studies (Study 1: *r* = .53; Study 2: *r* = .29; Study 3: *r* reported in text). Regression lines with 95% CI shown."
#| fig-width: 10
#| fig-height: 4
#| eval: !expr file.exists(fig_path("fig_mcr_personality.tiff"))
knitr::include_graphics(fig_path("fig_mcr_personality.tiff"))
```

```{r}
#| label: fig-mcr-personality-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_mcr_personality.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-08-param-corr
#| fig-cap: "Correlations among fitted parameters. (A) Study 1 minimal group, (B) Study 2 higher status outgroup condition, (C) Study 2 lower status outgroup condition, (D) Study 2 negation outgroup, (E) Study 3 majority outgroup condition, (F) Study 3 minority outgroup condition."
#| eval: !expr file.exists(fig_path("fig08_param_correlations.tiff"))
knitr::include_graphics(fig_path("fig08_param_correlations.tiff"))
```

### Discussion
Similarity-to-self predicted ingroup classification more strongly than one-to-one trait matching, confirming that self-anchoring is a structured inferential process rather than simple attribute replication. The effect held across both novel and repeated traits, ruling out repetition as an explanation. Model comparison revealed that the Symmetric+$\lambda$ architecture fit the data equivalently to the fully asymmetric model ($\Delta$ELPD = −0.21, SE = 0.55), indicating that in minimal groups, ingroup assimilation and outgroup discrimination are not architecturally dissociable — both are captured by a single projection rate. The model-derived MCR correlated with individual differences in group attachment, confirming that the computational index captures identity-relevant variation that structural parameters alone do not.

## STUDY 2: SELF-ANCHORING BASED ON RELATIVE STATUS OF UNIVERSITY GROUPS
Study 2 examined how social status modulates self-anchoring in real-world social categories. Study 2 was pre-registered at OSF (https://osf.io/q2vx7). We pre-registered the primary SS effect and its generalization to novel traits; a directional prediction that lower-status outgroup comparisons would produce stronger ingroup projection relative to negation (this prediction was disconfirmed — the high-status condition produced the strongest projection); that trait segregation would correlate positively with need to belong and dialectical self-views and negatively with self-esteem and independent self-construal; that self-anchoring strength would associate with social identification, perceived prototypicality, and status perceptions as tests of SCT's depersonalization account; and that generalization to novel traits would not differ from generalization to trained traits. Computational modeling analyses and MCR-based individual differences are exploratory. Minimal groups in Study 1 could not dissociate ingroup projection from outgroup discrimination—a symmetric architecture sufficed. Real social categories introduce meaningful intergroup history, perceived status differentials, and motivated distinctiveness concerns that should activate the two processes differentially. Under conditions of positive regard for the outgroup (e.g., a higher-status rival university), the prior motivation to classify traits as ingroup-characteristic (γ) may attenuate even while the projection mechanism (α) remains intact — or vice versa for derogated outgroups. Study 2 therefore tests both whether the asymmetric architecture is detectable under real intergroup conditions and whether status-modulated motivation manifests as changes in the projection rate or in the baseline ingroup preference.

Beyond the projection rate ($\alpha$), SCT's comparative fit principle predicts that categorization becomes most salient when intergroup differences are maximized relative to intragroup similarity (Turner et al., 1987). If $\lambda$ indexes the breadth of the self-concept's semantic reach, it may be sensitive to this contrast. As a non-preregistered exploratory test, we examined whether $\lambda$ varied across outgroup contrast conditions. The two directional predictions are: higher $\lambda$ (narrowing) in the high-status condition if participants restrict projection to guard against overlap with a prestigious outgroup; lower $\lambda$ (broadening) if intergroup salience expands the inferential gradient. Given the exploratory status and the expectation of small effects, these analyses should be interpreted with appropriate caution.

### Methods
From an initial pool of XX participants, XX were excluded (final *N* = 181).[^s2n]

[^s2n]: The Study 2 sample was initially reported as *N* = 283 based on the count of participants who completed initial consent and demographics. Subsequent inspection revealed that only 181 participants completed all task phases (training and generalization). The *N* = 181 is the sample for all analyses reported here and meets the 80% power threshold for detecting cross-level interactions at a small effect size. Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 4), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 47). Participants were native English-speaking university students (XX% Cisgender Female, XX% Cisgender Male, XX% Nonbinary; *M*<sub>Age</sub> = XX, *SD*<sub>Age</sub> = XX, Range<sub>Age</sub> = [XX, XX]). Ethnic composition included XX% White, XX% Mixed, XX% Asian, XX% Hispanic, XX% Native-American, and XX% Black. Participants were randomly assigned to one of three outgroup contrast conditions: Negation ("Not Ingroup University"), Higher Status University, or Lower Status University. A *simr* power analysis indicated that our final sample (*N* = 181) meets the 80% power threshold for detecting a cross-level interaction between similarity-to-self and condition at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 181 can detect correlations of *r* ≥ .20 at 80% power (α = .05, two-tailed).

### Results
**Manipulation Checks**
Manipulation checks confirmed perceived status differences. All participants rated the status and warmth of all three universities; pairwise contrasts used linear mixed models with subject random intercepts. Compared to the ingroup university (*M* = 6.24, *SD* = 1.36), the high-status university was rated significantly higher (*M* = 8.63, *SD* = 1.46, *p* < .001) and the low-status university significantly lower (*M* = 4.71, *SD* = 1.40, *p* < .001). Participants felt most warmly toward the ingroup (*M* = .783, *SD* = .156), followed by the high-status (*M* = .680, *SD* = .226, *p* < .001) and low-status university (*M* = .466, *SD* = .227, *p* < .001; warmth on 0–1 scale).

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in focal predictor models) quantified ingroup classification. Consistent with pre-registered predictions, a 1-SD increase in Similarity-to-Self increased P(ingroup choice) by 6.3 pp (AME = .063, 95% CI [.036, .090], *p* < .001); direct self-evaluations showed a 4.8 pp effect (AME = .048, 95% CI [.036, .061], *p* < .001), and desirability showed a 4.7 pp effect (AME = .048, 95% CI [.034, .061], *p* < .001). Effects for Similarity-to-Self varied by outgroup: the effect was significant in the negation condition (AME = .046, 95% CI [.013, .081], *p* = .007) and strongly so in the high-status condition (AME = .100, 95% CI [.047, .153], *p* < .001), but non-significant in the low-status condition (AME = .044, 95% CI [−.006, .094], *p* = .082). Across the Similarity-to-Self gradient in the negation condition, predicted P(ingroup) ranged from 61% at −1 SD to 68% at the mean to 73% at +1 SD; in the high-status condition, the range was considerably wider: 40% to 51% to 60%. A three-way model (Similarity-to-Self × Novel × Outgroup) examined whether generalization varied by outgroup condition. In the negation condition, effects were significant for both trained (AME = .049, 95% CI [.014, .083], *p* = .006) and novel traits (AME = .043, 95% CI [.008, .077], *p* = .015), suggesting self-anchoring generalizes to novel traits when contrasting against a neutral outgroup. The high-status condition showed the strongest generalization, with large significant effects for trained (AME = .104, 95% CI [.049, .158], *p* < .001) and novel traits (AME = .097, 95% CI [.043, .151], *p* < .001). The low-status condition again showed attenuation, with non-significant trained effects (AME = .047, 95% CI [−.003, .098], *p* = .064) and non-significant novel-trait effects (AME = .040, 95% CI [−.012, .091], *p* = .133), suggesting generalization may be selectively suppressed when the outgroup is perceived as lower status.
*SCT depersonalization and self-anchoring.* As a pre-registered test of SCT's depersonalization prediction (H6), we examined whether stronger identifiers show tighter alignment between self-ratings and ingroup classification. The same interaction tests (self-evaluation × SI; self-evaluation × Prototypicality; self-evaluation × SING.Ind; random slope for self-evaluations by subject) were significant for social identification (β = .090, *z* = 2.66, *p* = .008) and perceived prototypicality (β = .079, *z* = 2.33, *p* = .020). Independent self-construal was not significant (β = .053, *z* = 1.54, *p* = .123). When groups carry real identity content, stronger identifiers and those who perceive themselves as more prototypical ingroup members show a reliably stronger self-to-classification link — consistent with SCT's depersonalization account.

**Trait Segregation**
Trait segregation analyses showed that high-status contrast participants segregated traits more (*M* = .11, *SD* = .08) than low-status (*M* = .05) or negation (*M* = .04) participants—perceiving a more prestigious outgroup appears to sharpen the categorical boundaries participants drew between ingroup and outgroup trait profiles.

**Generalization Model**

**Table 3. LOO Model Comparison — Study 2 (University Status Groups, *N* = 181).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −15,906.09 | 63.36 | 0.0 | — |
| Asym+$\lambda$ | −15,907.36 | 63.28 | −1.27 | 2.48 |
| Symmetric | −16,133.31 | 60.20 | −227.21 | 20.29 |
| Bias | −16,299.15 | 59.29 | −393.05 | 25.56 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Sym+$\lambda$ and Asym+$\lambda$ are statistically indistinguishable ($\Delta$ELPD = −1.27, SE = 2.48); the simpler Sym+$\lambda$ is preferred by parsimony.

The self-projection models (Sym+$\lambda$, Asym+$\lambda$) substantially outperformed the Symmetric and Bias architectures across all conditions (see Table 3). As in Study 1, Sym+$\lambda$ and Asym+$\lambda$ were statistically indistinguishable overall ($\Delta$ELPD = −1.27, SE = 2.48), favoring the simpler symmetric architecture by parsimony. Per-condition model comparisons reveal a theoretically interpretable pattern: in the Negation condition (abstract outgroup "Not UCR"), Asym+$\lambda$ was numerically preferred ($\Delta$ELPD = +2.95 in favor of Asym+$\lambda$ over Sym+$\lambda$); in the High-Status condition, Sym+$\lambda$ was preferred ($\Delta$ELPD = +3.96); and in the Low-Status condition, architectures were essentially tied ($\Delta$ELPD = +0.26). The asymmetric advantage was significantly greater in the Negation condition than the High-Status condition ($\Delta\Delta$ELPD = 0.114, *t*(109) = 2.16, *p* = .033), suggesting that when the outgroup is concrete and positively-regarded, symmetric processing of in- and outgroup information is more strongly supported.

The primary parameter difference across conditions was not in the projection rate ($\alpha$; *F*(2, 178) = 0.33, *p* = .720) but in ingroup classification bias ($\gamma$). Participants in the High-Status condition showed dramatically reduced ingroup bias ($M$ = 0.36, *SD* = 0.19) relative to both Negation ($M$ = 0.60, *SD* = 0.23; $\beta$ = −0.246, *t*(178) = −6.65, *p* < .001) and Low-Status ($M$ = 0.61, *SD* = 0.20; *p* = .876 for Low-Status vs. Negation) participants. The Metacontrast Ratio was also lower in the High-Status condition ($M$ = 3.85, *SD* = 2.61) than in Negation ($M$ = 6.46, *SD* = 9.34; $\beta$ = −2.61, *t*(178) = −2.26, *p* = .025). Individual-level MCR correlated with RSE (*r* = .363, *p*<sub>FDR</sub> < .001), Prototypicality (*r* = .260, *p*<sub>FDR</sub> = .004), SING.Ind (*r* = .292, *p*<sub>FDR</sub> = .001), NFC (*r* = .292, *p*<sub>FDR</sub> = .001), and Social Identification (*r* = .224, *p*<sub>FDR</sub> = .015); generalization breadth ($\lambda$) independently correlated with Social Identification (*r* = .246, *p*<sub>FDR</sub> = .007). The ingroup bias parameter $\gamma$ showed no FDR-significant personality associations (all *p*<sub>FDR</sub> > .50).

*Comparative fit and generalization sensitivity.* As a non-preregistered exploratory analysis, we tested whether $\lambda$ differed across outgroup contrast conditions using a linear model ($\lambda \sim \text{condition}$). As noted above, both a higher $\lambda$ (narrowing as boundary protection) and a lower $\lambda$ (broadening as depersonalization) in the high-status condition are interpretable under SCT. $\lambda$ differed significantly across conditions (*F*(2, 178) = 3.64, *p* = .028, *R*² = .039), though differences were numerically small on the 0–5 scale. The Low-Status condition showed slightly narrower generalization than Negation ($M_{\text{Low}}$ = 3.47, *SD* = 0.10 vs. $M_{\text{Neg}}$ = 3.53, *SD* = 0.15; $\beta$ = −0.063, *t*(178) = −2.68, *p* = .008); the High-Status condition was intermediate and did not differ significantly from Negation ($M_{\text{High}}$ = 3.50, *SD* = 0.13; *p* = .127). The direction in the Low-Status condition—slight generalization contraction—is consistent with a meta-contrast sharpening account: a derogated outgroup makes categorical boundaries more salient, narrowing the scope of self-concept generalization. At the individual level, $\lambda$ correlated positively with outgroup warmth in the High-Status condition (*r* = .272, 95% CI [.007, .501], *p* = .045, *n* = 55) but not in the Low-Status condition (*r* = .055, *p* = .715, *n* = 46); overall the correlation was non-significant (*r* = .121, *p* = .229). The positive warmth–$\lambda$ association in the High-Status condition suggests that individuals who regard the prestigious outgroup more favorably generalize their self-concept more broadly during ingroup classification, consistent with reduced categorical rigidity when intergroup boundaries are perceived as permeable.

*Positive distinctiveness and ingroup bias.* If γ operationalizes the positive distinctiveness motive at the individual level, participants who view the higher-status outgroup more warmly should show attenuated ingroup bias. We tested this with Spearman's ρ between individual-level γ and outgroup warmth within each condition. The association was positive and directionally non-significant in the High-Status condition (ρ = .233, *n* = 55, *p* = .088) and null in the Low-Status condition (ρ = .208, *n* = 46, *p* = .166). The condition-level γ attenuation (High-Status *M* = 0.36 vs. Negation *M* = 0.60) is therefore a uniform structural shift — present for everyone in the High-Status condition — rather than a within-condition effect driven by individual variation in outgroup attitudes.

```{r}
#| label: fig-condition-effects-s2
#| fig-cap: "Study 2 Parameter Distributions by Outgroup Condition. Left: projection rate (α) shows no condition difference (*F*(2,178) = 0.33, *p* = .720), confirming that the inferential mechanism of self-anchoring is context-invariant. Right: ingroup bias (γ) drops dramatically in the High-Status condition (*M* = 0.36) relative to Negation (*M* = 0.60) and Low-Status (*M* = 0.61), *p* < .001. Individual participant values shown with jitter; boxplots show median and IQR."
#| fig-width: 8
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_condition_effects_s2.tiff"))
knitr::include_graphics(fig_path("fig_condition_effects_s2.tiff"))
```

```{r}
#| label: fig-condition-effects-s2-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_condition_effects_s2.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-elpd-s2
#| fig-cap: "Per-subject LOO-ELPD by model, Study 2 (University Status Groups, *N* = 181). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by outgroup contrast condition (Negation, High-Status, Low-Status). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 10
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s2.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s2.tiff"))
```

```{r}
#| label: fig-elpd-s2-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_s2.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 2 — re-run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-13-gradient-s2
#| fig-cap: "The Social Generalization Gradient (Study 2). Exponential decay of self-to-group generalization across semantic similarity space by outgroup contrast condition."
#| eval: !expr file.exists(fig_path("fig13_generalization_gradient_s2.tiff"))
knitr::include_graphics(fig_path("fig13_generalization_gradient_s2.tiff"))
```

### Discussion
Study 2 replicates similarity-based generalization in real-world social categories while revealing critical contextual modulations based on perceived social status. The primary computational finding is not an attenuation of the projection rate itself—$\alpha$ did not differ across conditions—but a dramatic reduction in the ingroup classification bias parameter ($\gamma$) when contrasting against the higher-status outgroup. Participants facing UCLA as their outgroup were less disposed to classify traits as ingroup-characteristic, suggesting that when the outgroup is positively-regarded and prestigious, the pull toward ingroup-exclusive attribution weakens. The projection mechanism (how self-attributes map to ingroup estimates via semantic similarity) remains intact; what changes is the prior disposition to choose the ingroup. The per-condition model comparisons reinforce this: the asymmetric architecture provided no benefit in the High-Status condition (Sym+$\lambda$ preferred), consistent with symmetric in/outgroup processing when the outgroup is positively-regarded. The behavioral AMEs reveal a complementary pattern at the low-status end: similarity-to-self was attenuated when comparing against the perceived lower-status outgroup (AME = .044, *p* = .082), with generalization to novel traits also non-significant. Self-Categorization Theory's meta-contrast principle offers an interpretation: when an outgroup is perceived as occupying a lower position in the societal status hierarchy, the categorical boundary may already be rendered salient through status cues, reducing the need for self-similarity to serve as an additional discriminating signal. The slight narrowing of generalization breadth ($\lambda$) in the Low-Status condition ($M$ = 3.47 vs. Negation $M$ = 3.53, *p* = .008) corroborates this account at the computational level. Social Identity Theory's positive distinctiveness principle provides a related account: when positive ingroup distinctiveness is already established through perceived status differences, the motivational pressure to deploy self-referential inference may be reduced. Together, these results suggest that self-anchoring functions as a context-sensitive inference strategy — most active when the categorization problem is motivationally engaged but not structurally resolved by status alone. The robust MCR–social identification correlation (*r* = .224, *p*<sub>FDR</sub> = .015) confirms that the semantic contrast ratio captures the strength of an individual's psychological ingroup attachment.

It is worth emphasizing that the γ–α dissociation was not the anticipated locus of contextual modulation—a priori, the projection rate (α) was the theoretically expected lever by which status context would exert its effects on self-anchoring. The finding that α remained invariant while γ shifted dramatically is therefore a post-hoc observation, albeit a theoretically clarifying one: it suggests that the inferential machinery of self-anchoring (how self-beliefs convert into ingroup beliefs via semantic similarity) is a surprisingly stable cognitive process, while the motivational prior that orients that machinery (the baseline attraction toward ingroup classification) is the context-sensitive component. This distinction—between process stability and motivational variability—has been largely implicit in social identity theory, and the present formal architecture makes it empirically tractable for the first time.

Notably, the magnitude of γ in the High-Status condition (*M* ≈ 0.36) converges precisely with the group-level posterior from Study 1 (*M* ≈ 0.36), despite very different intergroup contexts. This numerical convergence suggests that a concrete, positively-regarded, high-status outgroup can functionally neutralize the baseline ingroup preference that even purely arbitrary minimal groups produce—effectively resetting the motivational prior to its floor, as if the intergroup distinction carries no additional ingroup-pull beyond the bare fact of categorical membership. Put differently, the mere existence of a group boundary is sufficient to generate modest ingroup preference (Study 1); a high-status outgroup is sufficient to erase it.

## STUDY 3: SELF-ANCHORING BASED ON RELATIVE SIZE OF RACIAL GROUPS
Study 3 applied the self-anchoring framework to racial identities (Asian and Latino participants), examining how majority or minority outgroup contrasts exert differential effects on generalization. Study 3 was not formally pre-registered. It was designed as a conceptual replication and boundary-condition test of Study 2, following the same theoretical predictions: that SS predicts ingroup classification and generalizes to novel traits, that intergroup context modulates the parameters of that process, and that MCR correlates with individual differences in group identification. Analyses labeled "exploratory" below go beyond this confirmatory scope.

### Methods
From an initial pool of 313 participants, 48 were excluded (final *N* = 265). Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 9), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 37). Participants were native English-speaking university students (59.14% Cisgender Female, 40.86% Cisgender Male; *M*<sub>Age</sub> = 19.01, *SD*<sub>Age</sub> = 1.71, Range<sub>Age</sub> = [17, 33]), and were 50.97% Hispanic/Latino and 49.03% Asian. Participants were assigned to either a Minority (Asian vs. Latino) or Majority (Ingroup vs. White) comparison condition. Study 3 uses two conditions rather than Study 2's three, requiring a smaller sample for equivalent power; *N* = 265 comfortably exceeds the Study 2 power threshold for detecting a cross-level interaction at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 265 can detect correlations of *r* ≥ .17 at 80% power (α = .05, two-tailed).

### Results
**Manipulation Checks**
All participants rated the status and warmth of White, Asian, and Latino groups; pairwise contrasts used linear mixed models with subject random intercepts. White groups were perceived as significantly higher status (*M* = 8.42, *SD* = 1.63) than Asian (*M* = 6.73, *SD* = 1.51, *p* < .001) or Latino (*M* = 5.02, *SD* = 1.59, *p* < .001) groups; Asian groups were also rated higher in status than Latino groups (*p* < .001). Warmth ratings (0–1 scale) were higher for Latino (*M* = .79, *SD* = .19) and Asian (*M* = .77, *SD* = .19) groups than for White groups (*M* = .54, *SD* = .23; all *p*s < .001); Latino and Asian warmth did not significantly differ (*p* = .245).

```{r}
#| label: fig-10-manip-checks
#| fig-cap: "Raincloud plot depicting differences in status and positivity. University groups (top row) and racial groups (bottom row)."
#| eval: !expr file.exists(fig_path("fig10_manipulation_checks.tiff"))
knitr::include_graphics(fig_path("fig10_manipulation_checks.tiff"))
```

**Predictors of Ingroup Classification**
Average marginal effects (AMEs) from mixed-effects logistic regression (desirability controlled in focal predictor models) revealed that Similarity-to-Self did not predict ingroup classification overall (AME = .012, 95% CI [−.011, .036], *p* = .307). This null overall effect concealed condition-specific variation: the effect was absent in the minority-outgroup condition (AME = −.008, 95% CI [−.042, .026], *p* = .653) but significant in the majority-outgroup condition (AME = .034, 95% CI [.002, .066], *p* = .037). In the majority condition, predicted P(ingroup) ranged from 57% at −1 SD to 61% at the mean to 65% at +1 SD; in the minority condition the gradient was essentially flat (56.7%, 56.5%, 55.9%). Self-evaluations showed a robust overall effect (AME = .039, 95% CI [.028, .050], *p* < .001), as did desirability (AME = .032, 95% CI [.016, .047], *p* < .001). A three-way model (Similarity-to-Self × Novel × Condition) examined whether the majority-condition effect generalized to novel traits. In the majority condition, the trained-trait effect remained significant (AME = .040, 95% CI [.007, .072], *p* = .017), while the novel-trait effect was positive but non-significant (AME = .026, 95% CI [−.007, .058], *p* = .125). In the minority condition, neither trained nor novel-trait effects were significant (AME = −.009, *p* = .603; AME = −.006, *p* = .729). These patterns suggest that in the racial context, similarity-based inference is present for familiar traits when contrasting against the majority, but does not reliably propagate to semantically novel traits. Results from the computational model are reported in the Generalization Model section below, along with canonical correlation results.

*SCT depersonalization and self-anchoring.* The analogous interaction tests were null across all three moderators in Study 3: social identification (β = .027, *z* = 0.96, *p* = .336), prototypicality (β = .040, *z* = 1.46, *p* = .144), independent self-construal (β = .038, *z* = 1.39, *p* = .163). The elevated lapse rate (*w* = 0.64) in Study 3 likely reduces behavioral leverage for detecting identification-based modulation of the self-to-group mapping; the self-anchoring signal is noisier in racial contexts, attenuating the interaction's detectability.

**Trait Segregation**
Minority contrast participants segregated traits significantly more (*M* = .12, *SD* = .08) than majority contrast participants (*M* = .08, *p* < .001). This is superficially opposite to Study 2, where high-status contrast produced greater segregation than the other conditions — but the underlying pattern is identical across both studies: the condition associated with *less* self-projection is also the condition with *more* trait segregation. In Study 2, contrasting against a high-status outgroup suppressed self-projection and elevated segregation; in Study 3, contrasting against a fellow minority group suppressed self-projection and elevated segregation. In both cases, when the intergroup context reduces the self-concept's organizational leverage over classification, participants fall back on coarser, more rigid categorical partitioning rather than semantically structured inference.


**Generalization Model**

**Table 4. LOO Model Comparison — Study 3 (Racial Group Size, *N* = 265).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −24,573.70 | 58.56 | 0.0 | — |
| Asym+$\lambda$ | −24,575.83 | 58.53 | −2.13 | 1.20 |
| Symmetric | −24,813.25 | 53.77 | −239.55 | 21.45 |
| Bias | −25,019.26 | 52.67 | −445.57 | 27.06 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1).

As in Studies 1 and 2, the Sym+$\lambda$ model provided the best fit ($\Delta$ELPD = 0; reference). The Asym+$\lambda$ model was statistically indistinguishable (ΔELPD = −2.13, SE = 1.20; ratio = 1.78), and models with a generalization sensitivity parameter substantially outperformed architectures without one (Symmetric: ΔELPD = −239.55, SE = 21.45; Bias: ΔELPD = −445.57, SE = 27.06). Per-subject ELPD by condition showed no differential advantage for Asym+$\lambda$ in either the Minority (mean ΔELPD = −0.010, *t*(137) = −1.13, *p* = .262) or Majority (mean ΔELPD = −0.006, *t*(126) = −0.73, *p* = .466) condition, and these did not differ from each other (ΔΔELPD = −0.003, *t*(262) = −0.26, *p* = .794). Symmetric projection was therefore sufficient across both racial contrast conditions.

Group-level back-transformed parameters from the winning Sym+$\lambda$ model were: projection rate $\alpha$ = 2.27 [1.67, 3.20], ingroup bias $\gamma$ = 0.59 [0.53, 0.67], generalization sensitivity $\lambda$ = 3.50 [3.12, 4.04], and lapse rate $w$ = 0.64 [0.56, 0.71]. Neither projection rate ($\alpha$: F(1, 263) = 0.19, *p* = .667; Minority *M* = 2.28, Majority *M* = 2.27) nor ingroup bias ($\gamma$: F(1, 263) = 1.84, *p* = .177; Minority *M* = 0.53, Majority *M* = 0.57) differed by condition. The lapse rate $w$ was modestly higher in the Minority condition (Minority *M* = 0.64 vs. Majority *M* = 0.56; F(1, 263) = 4.62, *p* = .033, R² = .017), indicating that minority–minority contrast participants showed somewhat less deterministic classification overall. The semantic contrast ratio (MCR) did not differ by condition (Minority *M* = 6.22 vs. Majority *M* = 6.49; F(1, 263) = 0.08, *p* = .780).

FDR-corrected correlations between model-derived MCR and individual differences revealed that MCR was positively associated with independent self-construal (SING.Ind: *r* = .349, *p*~FDR~ < .001), self-esteem (RSE: *r* = .309, *p*~FDR~ < .001), self-concept clarity (SCC: *r* = .214, *p*~FDR~ = .005), and social identification (SI: *r* = .172, *p*~FDR~ = .025), and negatively associated with dialectical self-views (DS: *r* = −.212, *p*~FDR~ = .005). The ingroup bias parameter $\gamma$ showed FDR-significant personality associations in Study 3, in contrast to its null pattern in Studies 1 and 2: higher self-esteem predicted lower ingroup bias (RSE: *r* = −.191, *p*~FDR~ = .014), higher self-concept clarity predicted lower ingroup bias (SCC: *r* = −.185, *p*~FDR~ = .016), more dialectical self-views predicted higher ingroup bias (DS: *r* = .182, *p*~FDR~ = .017), and stronger need to belong predicted higher ingroup bias (NTB: *r* = .163, *p*~FDR~ = .033). These associations suggest that in racial contexts, where group boundaries carry real-world valence, the positive distinctiveness motive is more strongly linked to self-concept organization: individuals with more stable, clearly bounded self-concepts show less categorical favoritism, while those with more ambivalent self-structures and stronger affiliation needs show more. No other theoretical parameters ($\alpha$, $\lambda$, ΔELPD) survived FDR correction; generalization sensitivity $\lambda$ was not associated with self-concept clarity ($r$ = .062, *p* = .319), indicating that broader semantic projection does not co-occur with clearer self-organization in racial contexts.
*Comparative fit and generalization sensitivity.* As a non-preregistered exploratory analysis, we tested whether $\lambda$ differed between the majority and minority contrast conditions ($\lambda \sim \text{condition}$). Unlike Study 2, where the Low-Status condition showed a small but significant reduction in $\lambda$, generalization sensitivity was identical across conditions in Study 3 (Minority *M* = 3.49, Majority *M* = 3.49; F(1, 263) = 0.26, *p* = .611). Generalization breadth was not modulated by racial outgroup contrast type. At the individual level, $\lambda$ was positively associated with ingroup-relative preference (own-minority preference over other-minority; *r* = .147, *p* = .024), driven primarily by the Majority condition (*r* = .215, *p* = .023; Minority: *r* = .094, *p* = .302; interaction *p* = .314). Participants who feel more strongly that their own racial group is preferable to the other minority group project their self-concept more broadly when their contrast is against White — consistent with stronger group identification amplifying the reach of self-anchoring.

*Intergroup preference and ingroup bias.* A significant condition × ingroup-over-majority preference interaction emerged for $\gamma$ (F(1, 225) = 4.32, *p* = .039): in the Majority condition, stronger preference for own minority over White (*r*= .171, *p* = .074) was directionally associated with higher ingroup classification bias, while in the Minority condition this association was absent or reversed (*r* = −.108, *p* = .244). The pattern indicates that when participants are contrasting their own group against the racial majority, those who feel more strongly that their group is better than Whites also classify more traits as ingroup — consistent with activated positive distinctiveness motivations driving both affective and cognitive ingroup favoritism simultaneously.

*Race of participant as a moderator.* The overall condition effects on $\gamma$ were significantly moderated by participant race (F(1, 261) = 6.53, *p* = .011). Asian participants showed higher ingroup classification bias in the Minority condition ($M$ = 0.69) than the Majority condition ($M$ = 0.63), while Latino participants showed the opposite pattern (Minority $M$ = 0.41, Majority $M$ = 0.50; Majority condition *p* = .032). Within the Minority condition, Asian participants exhibited substantially higher ingroup bias than Latino participants, despite both groups facing a structurally symmetrical contrast. This asymmetry is not unexpected: within the same Asian-vs-Latino contrast, Asians and Latinos occupy reversed ingroup/outgroup roles, and the two groups may differ in their baseline readiness to use racial self-categorization as a classification heuristic. The lapse rate condition effect (Minority > Majority) was driven entirely by Latino participants (within-Latino: *p* = .021; within-Asian: *p* = .360). Stratifying the MCR–personality correlations by race revealed that the MCR–prototypicality association observed in Study 2 replicated for Latino participants (*r* = .227, *p* = .009) but not Asian participants (*r* = −.028, *p* = .753; Fisher *z* = −2.06, *p* = .039). MCR–self-esteem (RSE) and MCR–independent self-construal (SING.Ind) were significant in both racial groups (*r*s ≥ .203, *p*s ≤ .022). A full breakdown of condition × race interactions for all parameters is provided in Supplementary Materials C.

*Self-as-prototype and projection.* To test SCT's self-as-prototype assumption, we examined whether perceived prototypicality (Proto) predicted individual projection rates ($\alpha$) and whether this association differed by contrast condition ($\alpha \sim \text{Proto} \times \text{condition}$). The interaction was null (F(1, 256) = 0.13, *p* = .721), and Proto showed no association with $\alpha$ in either condition (Minority: *r* = .030, *p* = .724; Majority: *r* = −.015, *p* = .871). Perceived prototypicality did not modulate projection rate in the racial context, consistent with the pattern across Studies 1 and 2 where prototypicality correlated with MCR but not $\alpha$ directly.

```{r}
#| label: fig-elpd-s3
#| fig-cap: "Per-subject LOO-ELPD by model, Study 3 (Racial Groups, *N* = 265). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by racial outgroup contrast condition (Racial Minority Outgroup, Racial Majority Outgroup). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 8.5
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s3.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s3.tiff"))
```

```{r}
#| label: fig-elpd-s3-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_s3.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 3 — re-run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-14-gradient-s3
#| fig-cap: "The Social Generalization Gradient (Study 3). Exponential decay of self-to-group generalization across semantic similarity space by racial group contrast condition."
#| eval: !expr file.exists(fig_path("fig14_generalization_gradient_s3.tiff"))
knitr::include_graphics(fig_path("fig14_generalization_gradient_s3.tiff"))
```

```{r}
#| label: fig-12-params-raincloud
#| fig-cap: "Raincloud plot depicting differences in projection rate and bias parameter across conditions. Top row is Study 2; Bottom row is Study 3. Y-axis depicts the parameter, while X-axis depicts the condition."
#| eval: !expr file.exists(fig_path("fig12_params_raincloud.tiff"))
knitr::include_graphics(fig_path("fig12_params_raincloud.tiff"))
```

### Discussion
Study 3 extends self-anchoring to the racial context, revealing that similarity-based projection is activated when minority participants contrast their ingroup against the dominant White majority but is absent when contrasting against a fellow minority group. The behavioral AMEs showed no overall effect of similarity-to-self (AME = .012, *p* = .307), with the effect concentrated in the majority-outgroup condition (AME = .034, *p* = .037) and absent in the minority-outgroup condition (AME = −.008, *p* = .653). The computational model largely mirrored this pattern, with one notable addition: the lapse rate $w$ was modestly higher in the Minority condition (Minority *M* = 0.64 vs. Majority *M* = 0.56; *p* = .033), indicating less deterministic classification when contrasting against a fellow minority group. Neither the projection rate $\alpha$ nor ingroup bias $\gamma$ differed by condition as main effects (*p*s > .177), though the $\gamma$ null was qualified by a significant condition × participant race interaction — and — unlike Study 2 — the generalization sensitivity $\lambda$ was identical across conditions (*p* = .611). The Sym+$\lambda$ architecture was again sufficient; no improvement from allowing asymmetric projection was observed in either condition. This provides further evidence that the suppression of self-anchoring in the minority-minority contrast is not due to a reduction in projection rate or a narrowing of generalization breadth, but to an increase in response stochasticity — suggesting that the contrast problem itself is less tractable under fellow-minority comparison. MCR correlated with independent self-construal, self-esteem, self-concept clarity, and social identification (all *p*~FDR~ ≤ .025), replicating the MCR-personality structure from Study 2 in a racial group context.

Self-Categorization Theory provides two complementary interpretations. First, the meta-contrast principle predicts that a categorization becomes psychologically active when perceived intergroup differences exceed intragroup differences. Contrasting a minority group against the dominant majority group instantiates a salient, high-stakes categorical boundary — one that status perceptions alone cannot resolve — motivating the use of self-anchoring to define and stabilize ingroup identity. When contrasting against a fellow minority group, by contrast, the two groups share a superordinate social position in the broader racial hierarchy, which may invoke a sense of common fate and blur the functional distinctiveness of the between-minority boundary. Under this interpretation, the self-concept does not serve as a reliable prototype for one minority against another, because the shared minority status diminishes the meta-contrast. Second, the positive distinctiveness principle suggests that the motivation to differentiate one's ingroup is strongest against a more powerful outgroup — where distinctiveness must be actively constructed — and weakest when the comparison itself makes ingroup superiority on the relevant dimension ambiguous.

*Race moderation.* The condition × race interaction on $\gamma$ reveals that the Minority condition is not psychologically equivalent for Asian and Latino participants: the two groups play structurally opposite roles (one is always the ingroup, the other the outgroup), and their ingroup bias reflects this. Asian participants showed higher ingroup classification bias when the outgroup was Latino ($M$ = 0.69) than when it was White ($M$ = 0.63); Latino participants showed the reverse, with higher bias against White ($M$ = 0.50) than against Asian ($M$ = 0.41). One reading of this pattern is racial identification asymmetry: Asians in this sample may have stronger within-minority boundary sensitivity (or weaker common-fate identification with Latinos), while Latinos show stronger ingroup-outgroup accentuation when the outgroup is the dominant racial majority. The MCR–prototypicality association also diverged by race: it replicated in Latino participants but was absent in Asians. If prototypicality indexes how representative one's individual traits are of the ingroup, this replication for Latinos — but not Asians — may reflect differences in the degree to which racial identity is organized around self-concept overlap versus other sources (e.g., shared adversity, language, cultural practice). These patterns are exploratory, and should be interpreted cautiously given cell sizes of 56–79 participants. The supplementary materials provide full parameter tables stratified by condition and race.

Regarding generalization, formal tests (Similarity-to-Self × Novel × Condition) showed that neither trained nor novel-trait effects were significant in the minority condition (both *p*s > .60). In the majority condition, the trained-trait effect was significant (AME = .040, *p* = .017), while the novel-trait effect was positive but non-significant (AME = .026, *p* = .125). Although formal generalization was not supported even in the majority condition, it is notable that both the trained and novel-trait AMEs were numerically larger in the majority condition than in the minority condition, consistent with a gradient of self-anchoring strength rather than a categorical absence of generalization.

*Warmth, generalization breadth, and ingroup bias.* Two intergroup preference variables modulated distinct computational parameters. Stronger own-minority preference over the other minority ($\lambda$ × inMinorityTherm: *r* = .215 in Majority condition) predicted broader self-concept generalization — consistent with participants who maintain clear within-minority group boundaries projecting their self-concept more widely when the contrast shifts to the racial majority. The relationship appears specific to the majority-outgroup condition: when participants contrast against Whites, having a sharper intragroup affective boundary (preferring own minority over the other) amplifies rather than constrains the generalization reach. This could reflect the role of group-identity coherence in self-anchoring: participants with well-defined minority identities (marked by both group loyalty and inter-minority distinction) may draw on a more organized and generative self-concept when the categorization task activates cross-racial boundaries. Separately, stronger preference for own minority over White ($\gamma$ × inMajorityTherm) predicted higher ingroup classification bias in the Majority condition (*p* = .039), a pattern absent in the Minority condition. Higher ingroup bias (γ) reflects a stronger prior for classifying traits as ingroup regardless of their similarity to self. When participants feel more strongly that their minority group surpasses the racial majority, this evaluative ingroup advantage appears to function as a classification prior — they default to ingroup assignment more strongly, independent of trait similarity. Together these two patterns suggest the warmth-to-behavior pathway in self-anchoring is decomposable: within-minority affective distinctions modulate the breadth of self-concept projection (λ), while cross-racial evaluative comparisons modulate the motivational prior for ingroup preference (γ). This mirrors the theoretical decomposition proposed by the model: inferential reach and ingroup preference are separable, and different aspects of intergroup affect differentially recruit these components.

*Study 2 versus Study 3: Why did generalization attenuate under racial group contrasts?* In Study 2, similarity-based generalization to novel traits was robust in the negation and high-status conditions. In Study 3, trained-trait effects were significant only in the majority condition and did not reliably extend to novel traits in either condition. One interpretation is that racial categories carry more pre-structured, culturally ingrained content than university affiliations: participants already hold clear expectations about which traits "belong" to racial ingroups and outgroups, leaving less room for flexible self-based inference to shape classification. van Veelen et al. (2017) proposed that self-anchoring is most active when people face genuine uncertainty about their group's content — when group membership is newly formed or contested. University groups provide relatively thin stereotypic content, making participants reliant on self-referential inference; racial groups come pre-loaded with cultural stereotypes that may preempt or compete with self-anchoring as a classification strategy. Consistent with this, the computational model found the lapse rate $w$ was higher in Study 3 overall ($M$ = 0.64) compared to Studies 1 ($M$ = 0.56) and 2 ($M$ = 0.56), suggesting that racial classification is more probabilistic and noisy — less driven by the clean semantic self-concept signal that powers generalization. When self-concept inference contributes a noisier signal against a backdrop of entrenched categorical knowledge, generalization to semantically similar but untrained traits is less likely to emerge reliably. The replication of MCR–personality correlations across all three studies confirms that self-anchoring remains operative as an individual-difference tendency; the group-level suppression of generalization in Study 3 may reflect contextual competition rather than a categorical absence of the mechanism.

## POOLED ANALYSIS: A UNIVERSAL LAW OF SOCIAL GENERALIZATION

To formally test whether the self-anchoring architecture generalizes across intergroup contexts, we fit the four hierarchical models to the combined sample across Studies 1–3 (*N* = 507) using a three-level hierarchy (Global $\rightarrow$ Study $\rightarrow$ Subject). This architecture estimates global population parameters ($\lambda$, $\alpha_{in}$, $\alpha_{out}$, $\gamma$, $w$) that are shared across all three studies while accommodating study-level deviations, providing a formal test of cross-context generalizability of the social generalization gradient. We also conducted pooled behavioral GLMMs spanning all three studies to formally test whether similarity-based self-anchoring and semantic generalization varied systematically across conditions, using Study 1's minimal groups as the reference category.

### Results

**Table 5. LOO Model Comparison — Pooled Analysis (*N* = 507).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −46,126.9 | 91.2 | 0.0 | — |
| Asym+$\lambda$ | [PENDING] | [PENDING] | [PENDING] | [PENDING] |
| Symmetric | −46,703.4 | 84.8 | −576.5 | 32.3 |
| Bias | −47,157.0 | 83.2 | −1,030.1 | 40.6 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Pooled models include a study-level random effect with half-normal(0, 0.5) priors on hierarchical variance components. Asym+$\lambda$ results pending.

```{r}
#| label: fig-elpd-pooled
#| fig-cap: "Per-subject LOO-ELPD by model, Pooled Analysis (*N* = 507). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation using three-level hierarchical models (Global → Study → Subject)."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_pooled.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_pooled.tiff"))
```

```{r}
#| label: fig-elpd-pooled-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_pooled.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Pooled analysis — re-run `make_figures.R` after `Pooled/run_pooled_analysis.R` completes.]*")
```

Based on results available at time of writing, Sym+$\lambda$ leads model comparison and is treated as the provisional winning model pending Asym+$\lambda$ completion; if Asym+$\lambda$ wins or ties, the parameter section and figure below will be updated accordingly. As in individual studies, the two models were statistically tied in Studies 1–3, so either outcome is consistent with the symmetric architecture being sufficient to describe self-anchoring across group contexts.

**Table 6. Pooled Sym+$\lambda$ Parameter Estimates: Global and Study-Specific Means.**

| Parameter | Global | Study 1 (Minimal) | Study 2 (Status) | Study 3 (Racial) |
|:----------|-------:|------------------:|-----------------:|-----------------:|
| $\alpha$ (projection rate) | 2.02 | 2.09 | 1.83 | 2.09 |
| $\gamma$ (ingroup bias) | 0.515 | 0.401 | 0.554 | 0.580 |
| $\lambda$ (generalization) | 3.56 | 3.63 | 3.53 | 3.54 |
| $w$ (lapse rate) | 0.501 | 0.525 | 0.364 | 0.623 |

*Note.* All parameters back-transformed from probit scale: $\alpha = \Phi(\mu_{pr}) \times 10$; $\gamma = \Phi(\mu_{pr})$; $\lambda = \Phi(\mu_{pr}) \times 5$; $w = \Phi(\mu_{pr})$. Study-specific estimates are study_mu_pr posteriors, which are shrunk toward the global mean by the three-level hierarchy.

The most consistent finding is $\lambda$. The generalization sensitivity parameter estimated separately in each study — 3.57, 3.48, and 3.50 — replicated almost exactly in the pooled model (3.63, 3.53, 3.54) and converged on a global mean of 3.56. This parameter appears to reflect a stable property of how trait similarity is weighted in social generalization, independent of group type or social context.

Ingroup bias ($\gamma$) showed the clearest study-level variation. Participants in Study 1 (minimal groups) showed lower bias (pooled $\gamma$ = 0.40) than participants in Studies 2 and 3 (0.55 and 0.58, respectively). This replicates the individual study pattern and is consistent with the view that minimal group boundaries generate weaker ingroup preference than social categories carrying real-world significance. The projection rate ($\alpha$) and lapse rate ($w$) both showed hierarchical shrinkage toward the global mean relative to individual study estimates, with the most notable shift in $w$: Study 2's unusually low individual estimate (0.298) was pulled toward the global mean (0.364 in the pooled model), suggesting the extreme determinism observed in Study 2 individually was partly a sampling artifact tempered by cross-study pooling.

[PLACEHOLDER: Forest plot of study-level parameter estimates (Figure X) — to be generated from winning pooled model after Asym+$\lambda$ completes. See forest plot plan below.]

*Self-as-prototype and model fit.* Across all three studies, participants for whom the self functions as a more valid ingroup prototype (higher Proto) should be better predicted by the self-anchoring model—their self-concept provides a more diagnostic signal for ingroup classification. We tested this by correlating individual prototypicality (Proto) with each participant's mean per-trial LOO log-likelihood, a direct index of how well the model accounts for their choices. [PENDING — insert $r(\text{Proto}, \overline{\text{LOO log-lik}})$ pooled across studies and per study; predicted direction is positive.]

**Behavioral Analyses**

To formally compare self-anchoring and generalization effects across all three studies in a single model, we fit mixed-effects logistic regression models using `lme4` to the combined dataset (*N* = 507 subjects, 73,771 observations). Each study contributed its own condition levels, with Study 1's minimal-groups condition as the reference category. Predictors were Z-scored within study so that 1 unit reflects a within-study standard deviation. Random effects included study-level intercepts, subject intercepts and slopes nested within study, and crossed trait intercepts.

Across the full pooled sample, similarity-to-self was a significant predictor of ingroup classification (AME = .038, 95% CI [.021, .055], *p* < .001), as were self-evaluations (AME = .045, CI [.037, .053], *p* < .001) and desirability (AME = .036, CI [.025, .046], *p* < .001). These overall effects confirm that self-anchoring operates reliably as a cross-study phenomenon.

Condition-specific AMEs for similarity-to-self (all relative to the minimal-groups reference) revealed a striking pattern of contextual modulation. The effect was present and significant in minimal groups (AME = .053, CI [.007, .100], *p* = .025), the negation condition (AME = .053, CI [.021, .086], *p* = .001), the low-status condition (AME = .061, CI [.015, .107], *p* = .009), and the racial majority condition (AME = .033, CI [.000, .066], *p* = .050). The high-status condition showed the strongest similarity-based generalization of any condition (AME = .111, CI [.061, .162], *p* < .001) — roughly twice the size of the minimal-groups effect. The racial minority condition was the sole context with a null or directionally reversed effect (AME = −.013, CI [−.048, .021], *p* = .454), confirming the cross-study robustness of this specific boundary condition identified in Study 3.

The predicted P(ingroup) at ±1 SD of similarity-to-self further illustrates the gradient. In the high-status condition, P(ingroup) ranged from .39 at −1 SD to .62 at +1 SD (.228 range), the steepest gradient observed. Minimal groups showed a .119 range (.496 to .615), while the racial minority condition was essentially flat (.573 at −1 SD, .551 at +1 SD).

To test generalization formally — whether the similarity-based inference propagates to semantically novel traits — we fit a model with predicted.Z × Novel interactions (M4) and a three-way predicted.Z × Novel × Condition model (M5). Pooled across conditions, both trained (AME = .041, CI [.024, .059], *p* < .001) and novel-trait effects (AME = .036, CI [.019, .053], *p* < .001) were significant, confirming robust generalization at the pooled level. The three-way analysis revealed that generalization was condition-specific. In the racial minority condition, neither trained (AME = −.014, *p* = .432) nor novel-trait (AME = −.010, *p* = .580) effects were significant — a complete null. In the racial majority condition, the trained-trait effect was significant (AME = .039, CI [.005, .073], *p* = .024) but the novel-trait effect did not reach significance (AME = .025, CI [−.008, .058], *p* = .142). In contrast, all four university conditions showed significant effects for both trained and novel traits: high-status trained AME = .116 (*p* < .001), novel = .107 (*p* < .001); negation trained = .056 (*p* < .001), novel = .049 (*p* = .004); low-status trained = .064 (*p* = .007), novel = .056 (*p* = .022). Minimal groups also showed generalization to both trained (AME = .052, *p* = .033) and novel traits (AME = .056, *p* = .021).

Taken together, the pooled behavioral analyses converge with individual study findings to identify a clear principle: self-anchoring and semantic generalization are robust across minimal, university status, and racial majority contexts, but are specifically absent when the comparison involves a fellow minority group — a condition in which the shared subordinate social position may undermine the functional distinctiveness of the between-group boundary.

### Discussion

[INSERT POOLED DISCUSSION HERE]

## GENERAL DISCUSSION
People project their attributes onto ingroup members, but the underlying cognitive mechanisms have remained largely descriptive. Using a semantic dependency network of trait relations, we formalize self-anchoring as a structured inferential process based on similarity-based generalization. Across three studies, individuals treated the self as a semantic prototype, with beliefs propagating to novel group members via relational similarity—a finding robust across minimal, university, and racial categories. Figure X shows the group-level posterior estimates for all four model parameters across all three studies, illustrating both the stability of the projection mechanism (α, λ) and the context-sensitivity of the motivational prior (γ, w) across intergroup contexts.

```{r}
#| label: fig-cross-study-params
#| fig-cap: "Cross-study parameter estimates (Symmetric+λ model). Posterior medians with 90% credible intervals for projection rate (α), ingroup bias (γ), generalization sensitivity (λ), and lapse rate (w) across Studies 1–3. The projection rate and generalization sensitivity are stable across intergroup contexts; ingroup bias and lapse rate show the most contextual variation."
#| fig-width: 12
#| fig-height: 3.8
#| eval: !expr file.exists(fig_path("fig_cross_study_params.tiff"))
knitr::include_graphics(fig_path("fig_cross_study_params.tiff"))
```

```{r}
#| label: fig-cross-study-params-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_cross_study_params.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

Figure X shows the generalization gradient (S^λ) by study and condition. The gradient was remarkably stable: λ estimates clustered near 3.5 across all three studies and all conditions, confirming that the steepness of self-to-group generalization decay does not depend on group type or status context.

```{r}
#| label: fig-generalization-gradients
#| fig-cap: "Self-to-group generalization gradients across studies and conditions. Each panel shows the exponential decay of generalization weight (S^λ) as a function of semantic similarity (Dice coefficient) to training traits. Solid lines show condition posterior means; shaded bands show ±1 SD of the individual-level λ distribution; faint lines show individual participants. λ is stable across all three studies and all conditions, indicating that the breadth of self-concept generalization is context-invariant."
#| fig-width: 7
#| fig-height: 10
#| eval: !expr file.exists(fig_path("fig_generalization_gradients.tiff"))
knitr::include_graphics(fig_path("fig_generalization_gradients.tiff"))
```

```{r}
#| label: fig-generalization-gradients-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_generalization_gradients.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

### Formalizing Social Identity Theory
Our research moves social identity theory from a verbal model to a formal architecture by operationalizing the metacontrast principle as a formal ratio of summed similarities. This aligns social identity research with exemplar-based models of category learning and Shepard's (1987) law of generalization. We find that self-anchoring is primarily driven by "ingroup love"—the motivation to achieve similarity with the ingroup—rather than outgroup repulsion. However, the asymmetric architecture's added value is context-dependent: the asymmetric model was marginally preferred over the symmetric model in the abstract Negation condition (where the outgroup has no concrete identity), while the symmetric model was more clearly preferred when outgroups were concrete and status-differentiated. The asymmetric architecture provided no detectable advantage in the High-Status or racial majority conditions. These dual tendencies map onto Brewer's (1991) Optimal Distinctiveness Theory, which holds that group membership satisfies simultaneous needs for assimilation (inclusion) and differentiation (distinctiveness). In the present architecture, $\alpha_{in}$ formalizes the assimilation motive and $\alpha_{out}$ formalizes the differentiation motive; the empirical question is which dominates under a given intergroup context. The symmetric architecture winning in minimal groups suggests that when neither motive has privileged content to operate on, both are absorbed into a single undifferentiated projection rate.
Prior representational claims about similarity-based inference in social categorization have been constrained by the absence of model formalism (Guest & Martin, 2021). We demonstrate that the metacontrast ratio—a central concept in social identity theory—can be precisely measured using relational similarity, and that this formalization yields testable predictions about self-anchoring that verbal accounts cannot generate. Shepard's (1987) law was derived from animal conditioning and perceptual psychophysics: organisms generalize a learned response to novel stimuli in proportion to their similarity to the training exemplar, with that gradient decaying exponentially at a rate governed by a single sensitivity parameter. Nosofsky (1986) showed the same formal structure accounts for human perceptual categorization. That an identical mathematical law appears here—where the prototype is the self, the stimuli are personality traits distributed across a semantic network, and the task is social group classification—is significant because the representational substrate is as different as possible from those original domains. The result suggests Shepard's generalization law is not perceptual or behavioral in origin but reflects a domain-general solution to a common inference problem: given what I know about one exemplar, how strongly should I predict a property of a novel one? Social identity formation, at the computational level, appears to operate via the same inference machinery Shepard identified in animal learning and Nosofsky formalized for perception—with the self functioning as a social prototype in much the same way a conditioned stimulus functions as a perceptual anchor. Both traditions emerged in parallel with Turner and Tajfel's verbal articulation of the same principles in the social domain. By extending their formal apparatus to how people generalize self-knowledge to their groups, we connect these traditions and provide an empirically tractable foundation for the representational claims Self-Categorization Theory has long advanced. A notable result within this framework is the empirical identification of $\lambda$—Shepard's generalization sensitivity—as a recoverable parameter in human social categorization data. In principle, $\lambda$ and $\alpha$ are mathematically entangled (both govern how similarity maps to categorization probability), and their joint identifiability is not guaranteed; it requires the graded semantic structure of a trait network combined with a training-to-generalization paradigm that creates distinct behavioral fingerprints for each parameter. Demonstrating that $\lambda$ is estimable from social categorization data provides a new measurement handle on self-concept breadth that cannot be reduced to projection strength, enabling researchers to formally distinguish how far the self-concept's inferential reach extends ($\lambda$) from how strongly self-beliefs are weighted in that inference ($\alpha$)—a distinction that verbal theories of self-anchoring have never been able to draw.

To close the formal loop: Turner et al. (1987) defined the metacontrast ratio verbally as the ratio of perceived intergroup difference to intragroup similarity, with categorization becoming psychologically active when this ratio is maximized. The model-derived MCR — $\text{simW}_{in} / \text{simW}_{out}$ — is the direct computational implementation of that definition, not an analogy. $\text{simW}_{in}$ and $\text{simW}_{out}$ are generalization-weighted sums of self-beliefs projected onto ingroup- versus outgroup-predictive training traits, calibrated to each participant's posterior parameter estimates. The consistent replication of MCR correlations with social identification, self-esteem, and prototypicality across all three studies validates this operationalization as capturing what Turner's verbal construct intended. The self functions here as a social prototype in the sense Rosch (1978) formalized for natural categories: the reference point relative to which group category membership is inferred.

SCT's self-as-prototype assumption predicts that participants who perceive themselves as more representative of their ingroup should show stronger social projection. Across all three studies, perceived prototypicality (Proto) did not directly predict the projection rate $\alpha$ — a null that is itself theoretically informative. $\alpha$ reflects the slope of self-to-group mapping, a process that appears to operate independently of whether participants consciously regard themselves as typical ingroup exemplars. By contrast, in Study 2, prototypicality correlated with the model-derived MCR ($r$ = .260, $p_\text{FDR}$ = .004) — the ratio of self-concept similarity signal favoring the ingroup over the outgroup. This dissociation suggests that the self-as-prototype assumption holds at the level of the *semantic contrast structure* of the self-concept (how much its organization discriminates ingroup from outgroup) rather than at the level of how steeply self-beliefs slope into ingroup classification. It is the architecture of the self-concept — not the subjective sense of representativeness — that drives differentiation.

### Self-Anchoring as Generalization Across Related Traits
Self-anchoring is an inductive reasoning process, not simple item repetition. Prior research was vulnerable to the interpretation that self-anchoring reflects repetition effects, where ratings on the same items amplify descriptiveness (Unkelbach & Rom, 2017). Demonstrating that self-evaluations generalize to novel, semantically related traits establishes that self-anchoring involves belief propagation through the trait network. Individuals do not merely infer that their group shares specific traits; they infer what their group ought to be based on the structural relations within their self-concept.

### Contextual Modulation and Social Identification
Context systematically modulates self-anchoring, though through distinct parameters across studies. In Study 2, the projection rate (α) was invariant across outgroup conditions; what changed dramatically was the prior ingroup preference (γ), which fell to near-minimal-group levels when the outgroup was a prestigious, positively-regarded rival university. This indicates that when the outgroup is desirable, participants' baseline disposition to attribute traits to the ingroup weakens—even while their similarity-weighted inference machinery operates unchanged. This pattern—invariant α, attenuated γ—was not the anticipated locus of contextual modulation; it emerged as a post-hoc observation that illuminates a distinction social identity theory has typically left implicit: the inferential process of self-anchoring and the motivational prior that activates it are separable, and only the latter appears to be contextually modulated. Behaviorally, the High-Status condition actually produced the strongest similarity-to-self effects (AME = .100), while the Low-Status condition showed attenuation (AME = .044, *p* = .082). These two patterns are not contradictory: γ is the intercept of ingroup preference, while the AME reflects the slope of similarity-based inference; a lower γ and steeper slope can co-occur if participants rely more heavily on self-information in the absence of a strong default ingroup prior. In Study 3, self-anchoring was suppressed under minority–minority contrasts, with similarity-to-self predicting ingroup classification only in the majority-outgroup condition. Self-Categorization Theory's meta-contrast principle provides a unifying account: self-anchoring functions as a categorization aid most active when the intergroup boundary is motivationally engaged but not structurally resolved. When the categorical boundary is already established through perceived status differences, self-similarity contributes little additional discriminating signal. When contrasting against a fellow minority group, both groups share a superordinate social position, which may invoke a sense of common fate that mutes the functional distinctiveness of the boundary. Positive distinctiveness motivations provide a complementary explanation: when differentiation from the outgroup is already achieved through status perceptions, self-referential inference contributes less to category definition. Together, these patterns identify self-anchoring as a context-sensitive inference strategy — deployed most actively when the categorization problem is motivationally engaged and status cues alone are insufficient to resolve it. Trait segregation analyses provide a converging signature. Across Studies 2 and 3, the condition that most suppressed self-anchoring also produced the highest trait segregation: high-status contrast in Study 2 (where γ fell sharply and behavioral AMEs were strongest) and minority-outgroup contrast in Study 3 (where AMEs were null). The direction reverses superficially — high-status produced more segregation in Study 2, minority-outgroup produced more in Study 3 — but the logic is identical in both cases: when the intergroup context removes the self-concept's organizational leverage over classification, participants impose coarser, more rigid categorical partitioning on the trait network rather than semantically structured inference. This has broader implications: the same contextual conditions that disable the assimilative inference engine — status inequality, social marginalization, outgroups that cannot be assimilated into the self-concept's semantic structure — shift group perception from graded, similarity-based categorization toward binary Us-versus-Them partitioning. The cognitive signature of trait segregation is structurally identical to what is invoked in accounts of intergroup conflict and political polarization; the present framework suggests these phenomena may share a common computational origin in the disruption of similarity-based social inference.

Within this framework, γ is the formal operationalization of SIT's positive distinctiveness motive — the baseline prior for ingroup attribution, independent of the projection mechanism. The High-Status condition in Study 2 provides the clearest empirical signature: γ fell to $M = 0.36$ when participants contrasted against a positively-regarded, higher-status outgroup — numerically identical to the group-level γ estimated in Study 1's minimal groups ($M = 0.36$). A prestigious outgroup fully erodes the ingroup preference that even a meaningless categorical assignment produces. This convergence is not coincidental: under SIT, positive distinctiveness motivation is highest when ingroup superiority is uncertain or contested. A high-status outgroup resolves the comparison unfavorably, reducing the motivational pressure to mark traits as ingroup-characteristic. The projection mechanism (α) operates unchanged; only the prior for using it shifts. Notably, γ did not similarly attenuate in Study 3's majority-outgroup condition ($M = 0.57$) — nearly matching the Negation baseline ($M = 0.60$) rather than the High-Status floor. Not all high-status outgroups are psychologically equivalent, and the γ pattern across studies reflects this. A prestigious rival university is an *aspirational* outgroup: the intergroup boundary is permeable (students could have attended UCLA instead of UCR), the outgroup is positively regarded, and no historical power asymmetry structures the comparison. Under these conditions, positive distinctiveness is already contested — the outgroup is objectively superior on the relevant status dimension — reducing the motivational need to mark traits as ingroup-characteristic. A dominant racial majority is a *marginalized* outgroup comparison: the boundary is relatively impermeable, the power asymmetry is entrenched, and minority identity is bound up with protection against that asymmetry. Facing the racial majority activates a defensive ingroup prior — sustaining γ near baseline levels ($M = 0.57$) despite the status differential — because positive distinctiveness under these conditions requires active maintenance rather than passive erosion. In Study 3, the lapse rate $w$ — rather than γ — was the contextually sensitive parameter, rising in the minority-outgroup condition ($M = 0.64$) relative to the majority condition ($M = 0.56$) and relative to both Studies 1 and 2 ($M \approx 0.56$). This cross-study pattern in $w$ is substantive, not artifactual: Studies 1 and 2 produced equivalent lapse rates despite differing in group content richness (arbitrary minimal groups vs. real universities), while Study 3's racial context elevated noise. This is consistent with van Veelen et al.'s (2017) account that self-anchoring is most tractable when group content is uncertain — racial categories carry pre-loaded stereotypic content that competes with self-based inference, increasing classification stochasticity without suppressing the self-anchoring mechanism entirely (as confirmed by the replication of MCR–personality correlations across all three studies).

Including the generalization sensitivity parameter, λ, operationalizes the decay of self-anchoring across the semantic network and functions as a person-specific index of cognitive style. High λ indicates a steep, narrow generalization gradient, where inference is restricted to only the most semantically proximal traits; low λ indicates a shallow, broad gradient where self-knowledge propagates more liberally. The finding that higher social identification correlated with higher λ in Study 2 (*r* = .25) is informative. It suggests that stronger group identification does not produce a more expansive or all-encompassing ingroup category; instead, it sharpens the inferential boundary. Strongly identified individuals appear to use a more selective, high-fidelity mapping from self to group, anchoring primarily on their most diagnostic attributes. This provides a formal, mechanistic account for how group attachment shapes the *structure*, not just the magnitude, of social inference.

### Limitations
Although $\lambda$ enables formal estimation of the asymmetric model with separate $\alpha_{in}$ and $\alpha_{out}$ parameters, the binary forced-choice paradigm imposes a structural constraint on the behavioral leverage available to dissociate these quantities. Because each trial yields a single ingroup-or-outgroup response, ingroup attractiveness and outgroup repulsion cannot vary independently within a trial—both are absorbed into the same binary outcome, limiting the data's informativeness for pulling the two projection rates apart. This means that even in contexts where $\alpha_{in}$ and $\alpha_{out}$ genuinely differ, the forced-choice design may be insufficiently sensitive to detect the asymmetry. Paradigms that solicit independent ingroup and outgroup typicality ratings, or that present single-group classification trials, would provide richer behavioral signatures for estimating these parameters separately. The consistent symmetric-architecture preference across most intergroup contexts should therefore be interpreted cautiously: it may partly reflect task design constraints rather than a genuine cognitive indistinguishability of ingroup love and outgroup hate. Future work with paradigms better suited to generating independent behavioral signatures for $\alpha_{in}$ and $\alpha_{out}$ would provide a stronger test of whether the symmetric constraint is empirically warranted. The trait pool used across all three studies consisted entirely of positively valenced traits. This is a meaningful constraint on interpretation of the ingroup bias parameter ($\gamma$). Because all traits are desirable, a $\gamma$ above 0.5 — indicating preferential classification of trait-bearers as ingroup members — is consistent with positive ingroup distinctiveness: participants attribute valued characteristics to their group at above-chance rates. The higher $\gamma$ observed in real social category contexts (Studies 2 and 3, $\gamma \approx$ 0.55–0.59) relative to minimal groups (Study 1, $\gamma \approx$ 0.36–0.40) is interpretable as heightened positive ingroup bias when group boundaries carry social meaning. However, because the design includes no negatively valenced traits, the model cannot separately estimate whether participants are attributing positive traits to the ingroup, withholding positive traits from the outgroup, or both. Outgroup derogation via negative trait assignment — a distinct component of intergroup bias — is entirely outside the paradigm's scope. Future work incorporating both positive and negative traits would allow $\gamma$ to reflect the full valence structure of ingroup favoritism and outgroup derogation independently. Of SCT's four fit criteria, neither normative fit nor perceiver readiness is directly assessed. Normative fit — whether trait content matches expectations for a group label — is not measured; the task does not ask participants to evaluate content-label consistency. Perceiver readiness is imposed by the task structure: all participants classify traits for an experimentally salient group, so the model describes how self-anchoring operates once a category is engaged, not who spontaneously activates social categorization in naturalistic settings. Comparative fit was explored via λ variation across Study 2 conditions, but effects were small (R² = .039) and the mapping from λ to categorical distinctiveness is indirect — these analyses should be understood as exploratory rather than as formal tests of comparative fit.

### Conclusion
By formalizing the relationship between self-concept structure and social identity, we show that self-anchoring follows the same principles of similarity-based generalization that govern category learning—at least across the intergroup contexts examined here, all drawn from university samples. Group membership is not merely a motivational bias; it is a structured, inferential process grounded in semantic self-knowledge. In this sense, the self-concept functions as a generative engine of social identity: beliefs about social groups are not stored as fixed templates but constructed on-the-fly by propagating self-knowledge through relational semantic structure—the same inferential machinery used for any categorical judgment. This generative architecture explains both the robustness of self-anchoring across heterogeneous group contexts and its vulnerability to disruption when the intergroup structure renders the self-concept's semantic geometry an unreliable guide. This architecture provides a precise, testable framework for understanding social identity as a cognitive process.

### Appendix A: Posterior Predictive Checks
We conducted posterior predictive checks (PPCs) to verify model fit to observed data, evaluating both the training and generalization phases across all three studies (Figure A1). Observed and predicted data were well-aligned, confirming adequate fit.

### Appendix B: Parameter Recovery Analyses
We assessed parameter identifiability by simulating behavior from known true parameters, then fitting the model to the simulated data and comparing recovered posteriors to ground truth. The simulation used the Study 1 trial structure (*N* = 61), real trait similarity matrices, and two design choices described below.

**Parameter generation.** True parameters for each simulated participant were drawn from distributions calibrated to the Study 1 posterior rather than from the prior. Group-level means ($\mu_{pr}$) and individual-level standard deviations ($\sigma$) on the probit scale were taken directly from the Study 1 posterior summaries for each model (Sym+$\lambda$: $\sigma_m = 0.286$, $\sigma_\gamma = 0.709$, $\sigma_\lambda = 0.334$, $\sigma_w = 1.181$; Asym+$\lambda$: $\sigma_{\alpha_{in}} = 0.220$, $\sigma_{\alpha_{out}} = 0.226$, $\sigma_\gamma = 0.721$, $\sigma_\lambda = 0.377$, $\sigma_w = 1.188$). This ensures simulated individual differences match the range actually observed in the data rather than an arbitrary prior specification.

**Self-rating generation.** Each simulated participant received synthetic self-ratings drawn from a Gaussian Markov Random Field (GMRF) defined on the trait network. We computed the precision matrix $\mathbf{P} = \alpha\mathbf{L} + \varepsilon\mathbf{I}_{148}$, where $\mathbf{L} = \mathbf{D} - \mathbf{A}$ is the combinatorial graph Laplacian of the trait network, $\alpha = 1.0$ controls network smoothness, and $\varepsilon = 0.01$ regularizes the singular Laplacian. Each participant received an independent draw $\mathbf{x} \sim \mathcal{N}(\mathbf{0},\, \mathbf{P}^{-1})$, standardized to the observed within-person SD (1.13), centered at 4, and rounded to integers 1–7. Intuitively, the graph Laplacian encodes which traits are structurally proximate in the network; inverting the regularized Laplacian produces a covariance matrix in which connected traits covary — a participant who rates *Warm* highly will tend to rate *Friendly* similarly, exactly the structure the projection model assumes. Centering ratings at the scale midpoint (4) ensures that self-ratings span both the self-descriptive and non-self-descriptive range, which is required for $m$ to be identifiable from the data.

Primary parameters of interest — projection rate ($m$ / $\alpha_{in}$, $\alpha_{out}$), ingroup bias ($\gamma$), generalization sensitivity ($\lambda$), and lapse rate ($w$) — were recoverable for both the Symmetric+$\lambda$ and Asymmetric+$\lambda$ architectures (Figure B1). [PENDING — insert per-parameter recovery correlations (*r*) and RMSE after `Parameter Recovery/run_parameter_recovery.R` completes.] Figure B2 shows the parameter confusion matrix: each cell gives the Pearson *r* between true parameter *i* and recovered parameter *j*, with diagonal cells (outlined) reflecting self-recovery and off-diagonal cells reflecting cross-parameter confusability.

```{r}
#| label: fig-param-recovery
#| fig-cap: "**Figure B1.** Parameter recovery for the Symmetric+λ (top row) and Asymmetric+λ (bottom row) models. Each panel shows the 2D density of true (x-axis) vs. posterior-median recovered (y-axis) parameter values across simulated participants (*N* = 61, Study 1 structure). The dashed red diagonal indicates perfect recovery. Pearson *r* values are shown per parameter. Placeholder data shown until `Parameter Recovery/run_parameter_recovery.R` is run."
#| fig-width: 11
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig_param_recovery.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery.tiff"))
```

```{r}
#| label: fig-param-recovery-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery.tiff")))
cat("*[Figure B1 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

```{r}
#| label: fig-param-recovery-heatmap
#| fig-cap: "**Figure B2.** Parameter recovery confusion matrix for the Symmetric+λ (left) and Asymmetric+λ (right) models. Each cell shows the Pearson *r* between the true value of parameter *i* (rows) and the posterior-median recovered value of parameter *j* (columns). Diagonal cells (black outline) give self-recovery correlations; off-diagonal cells reflect cross-parameter confusability. Higher off-diagonal values indicate that two parameters' behavioral signatures are difficult to disentangle."
#| fig-width: 9
#| fig-height: 5
#| eval: !expr file.exists(fig_path("fig_param_recovery_heatmap.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery_heatmap.tiff"))
```

```{r}
#| label: fig-param-recovery-heatmap-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery_heatmap.tiff")))
cat("*[Figure B2 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

### Supplementary Materials C: Race Moderation Analyses (Study 3)

Study 3 pools Asian and Latino participants within each contrast condition, an assumption that warrants direct examination. We tested whether participant race (Asian vs. Latino) moderated the condition effects reported in the main text by adding a condition × race interaction term to each parameter model.

**Parameter estimates by condition × race.** Cell means for key parameters are shown in Table C1.

| Condition | Race | $\gamma$ | $\lambda$ | $w$ | MCR |
|:---|:---|---:|---:|---:|---:|
| Minority | Asian | 0.69 | 3.49 | 0.65 | 4.62 |
| Minority | Latino | 0.41 | 3.49 | 0.64 | 7.42 |
| Majority | Asian | 0.63 | 3.49 | 0.60 | 6.78 |
| Majority | Latino | 0.50 | 3.50 | 0.52 | 6.12 |

*Note.* N(Asian) = 130, N(Latino) = 135; Minority: Asian N=59, Latino N=79; Majority: Asian N=71, Latino N=56.

**Condition × race interaction.** A significant condition × race interaction emerged for $\gamma$ (F(1, 261) = 6.53, *p* = .011). Within the Minority condition, Asian participants showed substantially higher ingroup classification bias ($M$ = 0.69) than Latino participants ($M$ = 0.41). This asymmetry arises because within the Minority (Asian-vs-Latino) contrast, Asians and Latinos occupy opposite ingroup/outgroup roles: an Asian participant's ingroup is Asian, while a Latino participant's ingroup is Latino. The apparent "low bias" for Latinos in the Minority condition may reflect that Latinos in the sample were less activated by the intergroup contrast, or that within-minority contrasts have different salience by racial group. A Latino participant's condition effect (Minority $M$ = 0.41 vs. Majority $M$ = 0.50, *p* = .032) shows higher bias against the racial majority than against a fellow minority, whereas Asian participants showed no significant condition difference (*p* = .149). The lapse rate condition effect was driven entirely by Latino participants (within-Latino: Minority $M$ = 0.64 vs. Majority $M$ = 0.52, *p* = .021; within-Asian: *p* = .360). No condition × race interactions were significant for $\alpha$ (F = 0.17, *p* = .679), $\lambda$ (F = 0.32, *p* = .571), or $\Delta$ELPD (F = 0.72, *p* = .399). The MCR × condition × race interaction was marginal (F(1, 261) = 3.30, *p* = .070).

**MCR–personality correlations by race.** MCR correlated with independent self-construal (SING.Ind) and self-esteem (RSE) in both Asian and Latino participants (all *p*s ≤ .021), confirming the core MCR-personality structure across both groups. Self-prototypicality (Proto) correlated with MCR in Latino participants (*r* = .227, *p* = .009) but not Asian participants (*r* = −.028, *p* = .753; Fisher *z* = −2.06, *p* = .039), suggesting that the Proto → MCR pathway observed in Study 2 replicates for Latinos but not Asians. Social identification (SI) correlated with MCR in Asian participants (*r* = .225, *p* = .011) but not Latinos (*r* = .093, *p* = .289; *p*~diff~ = .225). These race-stratified patterns should be interpreted cautiously given sample sizes within each race × condition cell (N = 56–79).

**Warmth moderation by race.** A marginal race × ingroup-over-minority preference interaction for MCR (F(1, 230) = 3.14, *p* = .078) suggested opposite directions for Asian (*β* = −.059) and Latino (*β* = +.034) participants, though neither within-race slope was significant. No other warmth × race interactions reached significance. All race moderation results are exploratory, were not pre-registered, and should be replicated before interpretation.

### Supplementary Materials D: Self-Concept Entropy (*H_g*) and Ingroup Classification

We computed a *local self-concept clarity* index (*H_g*) as a similarity-weighted Shannon entropy over the self-evaluation distribution in each test trait's semantic neighborhood:

$$H_g = -\sum_{e=1}^{7} p_e \log_2 p_e, \quad p_e = \frac{\sum_{t:\, E_t = e} S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$

where $p_e$ is the similarity-weighted proportion of training traits rated at level $e$ on the 7-point scale. Low $H_g$ indicates coherent, concentrated self-ratings near the test trait; high $H_g$ indicates mixed, diffuse self-ratings. This operationalizes Campbell et al.'s (1996) self-concept clarity at the local semantic level. Each study used a separate mixed-effects logistic regression with desirability controlled and a by-subject random slope for $H_g$.

$H_g$ was non-significant in Study 1 (AME = −.058, 95% CI [−.152, .036], *p* = .225), consistent with low statistical power and the high lapse rate under minimal-group conditions. $H_g$ significantly predicted lower ingroup classification in Study 2 (AME = −.058, 95% CI [−.099, −.017], *p* = .005) and Study 3 (AME = −.051, 95% CI [−.096, −.006], *p* = .027). These results are consistent with a signal-precision account: when group content is real and self-anchoring is the primary inferential channel, a diffuse local self-concept degrades classification. The null in Study 1 is consistent with the high lapse rate (*w* = 0.56) under minimal-group conditions attenuating behavioral leverage for detecting entropy effects.

### Supplementary Materials E: Canonical Correlation Analysis

**Study 1 CCA (Minimal Groups, *N* = 61).** To examine the multivariate personality structure of model-derived indices, we conducted an exploratory CCA of model parameters (X: $\alpha$, $\lambda$, $\gamma$, $w$, MCR, trait segregation; $k = 6$) against personality scales (Y: DS, Prototypicality, SCC, Social Identity, RSE, NTB, NFC, SING-Ind, SING-Inter; $k = 9$). Statistical significance was assessed via permutation test (*B* = 5,000). *N* = 61 falls below recommended guidelines for CCA with 15 variables; results should be regarded as preliminary and interpreted with caution. The first canonical variate was significant (*r* = .720, *p*~perm~ = .013). On the model side, CV1 was defined primarily by MCR (loading = .53), ingroup bias $\gamma$ (loading = .45), and trait segregation (loading = .39); $\alpha$, $\lambda$, and $w$ loaded negligibly. On the personality side, SING-Inter dominated (loading = .87), followed by social identity (loading = .53) and need to belong (loading = .48). A second variate was also significant (*r* = .623, *p*~perm~ = .005) but is not interpreted given the sample size. The pooled CCA below provides better-powered replication.

**Pooled CCA (*N* = 507).** *[Pending — pooled individual-difference parameters are being finalized. Results will be inserted here prior to submission.]*

### Supplementary Materials F: Semantic Trait Network

The semantic dependency network used in all three studies comprised 148 personality traits. Figure F1 displays a force-directed layout of the 80 most-connected traits (Fruchterman–Reingold algorithm). Node size and color reflect degree centrality. Traits with high connectivity occupy the network's densely interconnected core and have broad semantic influence during the similarity-weighted inference process; low-degree traits at the periphery exert narrower inferential reach and primarily receive rather than propagate generalization weight.

```{r}
#| label: fig-f1-trait-network
#| fig-cap: "Semantic trait network (top 80 traits by connectivity). Nodes represent personality traits; edges represent adjacency in the semantic dependency network. Node size and color indicate degree centrality (number of connections). Force-directed layout (Fruchterman–Reingold). Trait labels omitted for clarity; the full adjacency matrix is available in the Open Materials."
#| fig-width: 8
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig01_trait_network.tiff"))
knitr::include_graphics(fig_path("fig01_trait_network.tiff"))
```

```{r}
#| label: fig-f1-trait-network-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig01_trait_network.tiff")))
cat("*[Figure F1 pending: run `Figures/make_figures.R` to generate.]*")
```

## OPEN MATERIALS

Analysis scripts, Stan model code, and de-identified data are available at [repository URL]. An interactive web supplement demonstrating the Symmetric + λ and Asymmetric + λ model architectures is available at [Shiny app URL]. The supplement allows readers to manipulate model parameters and resample training-trait configurations in real time. Two parameter combinations are particularly informative as reference points: setting γ = 0.50 and w = 0 isolates the core self-anchoring mechanism — no baseline ingroup preference and no random responding — so that the classification curve reflects only the similarity-weighted self-concept signal. The Study 1 group-level posterior medians (γ = 0.36, w = 0.56) are loaded by default, reflecting the modest ingroup bias and substantial response noise typical of laboratory categorization paradigms.

## REFERENCES

Adler, N. E., Boyce, T., Chesney, M. A., Cohen, S., Folkman, S., Kahn, R. L., & Syme,
S. L. (1994). Socioeconomic status and health: The challenge of the gradient.
*American Psychologist*, *49*, 15–24. https://doi.org/10.1037/0003-066X.49.1.15

Ahn, W.-Y., Haines, N., & Zhang, L. (2017). Revealing neurocomputational
mechanisms of reinforcement learning and decision-making with the
hBayesDM package. *Computational Psychiatry*, *1*, 24–57.
https://doi.org/10.1162/CPSY_a_00002

Ahn, W.-Y., Krawitz, A., Kim, W., Busmeyer, J. R., & Brown, J. W. (2011). A model-based fMRI analysis with hierarchical Bayesian parameter estimation. *Journal of Neuroscience, Psychology, and Economics*, *4*(2), 95–110.
https://doi.org/10.1037/a0020684

Ames, D. R. (2004). Inside the mind reader's tool kit: Projection and stereotyping in
mental state inference. *Journal of Personality and Social Psychology*, *87*(3), 340–353. https://doi.org/10.1037/0022-3514.87.3.340

Baayen, R. H., Davidson, D. J., & Bates, D. M. (2008). Mixed-effects modeling with
crossed random effects for subjects and items. *Journal of Memory and Language*,
*59*(4), 390–412. https://doi.org/10.1016/j.jml.2007.12.005

Bafumi, J., & Gelman, A. (2007). *Fitting multilevel models when predictors and group
effects correlate* (SSRN Scholarly Paper No. 1010095).
https://doi.org/10.2139/ssrn.1010095

Balliet, D., Wu, J., & De Dreu, C. K. W. (2014). Ingroup favoritism in cooperation: A
meta-analysis. *Psychological Bulletin*, *140*, 1556–1581.
https://doi.org/10.1037/a0037737

Barr, D. J., Levy, R., Scheepers, C., & Tily, H. J. (2013). Random effects structure for
confirmatory hypothesis testing: Keep it maximal. *Journal of Memory and
Language*, *68*(3). https://doi.org/10.1016/j.jml.2012.11.001

Baumeister, R. F., & Leary, M. R. (1995). The need to belong: Desire for interpersonal
attachments as a fundamental human motivation. *Psychological Bulletin*, *117*,
497–529. https://doi.org/10.1037/0033-2909.117.3.497

Bianchi, M., Machunsky, M., Steffens, M. C., & Mummendey, A. (2009). Like me or
like us: Is ingroup projection just social projection? *Experimental Psychology*, *56*,
198–205. https://doi.org/10.1027/1618-3169.56.3.198

Blake, K. R., & Gangestad, S. (2020). On attenuated interactions, measurement error, and
statistical power: Guidelines for social and personality psychologists. *Personality
and Social Psychology Bulletin*, *46*, 1702–1711.
https://doi.org/10.1177/0146167220913363

Bowman, C. R., Iwashita, T., & Zeithamova, D. (2020). Tracking prototype and exemplar
representations in the brain across learning. *ELife*, *9*, e59360.
https://doi.org/10.7554/eLife.59360

Brewer, M. B. (1991). The social self: On being the same and different at the same time.
*Personality and Social Psychology Bulletin*, *17*(5), 475–482.

Brewer, M. B. (1993). Social identity, distinctiveness, and in-group homogeneity. *Social
Cognition*, *11*, 150–164. https://doi.org/10.1521/soco.1993.11.1.150

Brewer, M. B. (1999). The psychology of prejudice: Ingroup love and outgroup hate?
*Journal of Social Issues*, *55*(3), 429–444. https://doi.org/10.1111/0022-4537.00126

Brown, R. (2000). Social identity theory: Past achievements, current problems and future
challenges. *European Journal of Social Psychology*, *30*(6), 745–778.
https://doi.org/10.1002/1099-0992(200011/12)30:6<745::AID-EJSP24>3.0.CO;2-O

Brown, R. J. (1984). The role of similarity in intergroup relations. In H. Tajfel (Ed.), *The
social dimension: European developments in social psychology* (Vol. 2, pp.
603–623). Cambridge University Press.
https://doi.org/10.1017/CBO9780511759154.012

Cacioppo, J. T., & Petty, R. E. (1982). The need for cognition. *Journal of Personality and
Social Psychology*, *42*(1), 116–131.

Cadinu, M., Carnaghi, A., & Guizzo, F. (2020). Group meaningfulness and the causal
direction of influence between the ingroup and the self or another individual:
Evidence from the induction-deduction paradigm. *PLoS ONE*, *15*(3), e0229321.
https://doi.org/10.1371/journal.pone.0229321

Cadinu, M., & De Amicis, L. (1999). The relationship between the self and the ingroup:
When having a common conception helps. *Swiss Journal of Psychology*, *58*,
226–232. https://doi.org/10.1024/1421-0185.58.4.226

Cadinu, M., Latrofa, M., & Carnaghi, A. (2013). Comparing self-stereotyping with
ingroup-stereotyping and out-group-stereotyping in unequal-status groups: The
case of gender. *Self and Identity*, *12*(6), 582–596.
https://doi.org/10.1080/15298868.2012.712753

Cadinu, M., & Rothbart, M. (1996). Self-anchoring and differentiation processes in the
minimal group setting. *Journal of Personality and Social Psychology*, *70*, 661–677. https://doi.org/10.1037/0022-3514.70.4.661

Campbell, D. T. (1958). Common fate, similarity, and other indices of the status of
aggregates of persons as social entities. *Behavioral Science*, *3*(1), 14–25.
https://doi.org/10.1002/bs.3830030103

Campbell, J. D., Trapnell, P. D., Heine, S. J., Katz, I. M., Lavallee, L. F., & Lehman, D.
R. (1996). Self-concept clarity: Measurement, personality correlates, and cultural
boundaries. *Journal of Personality and Social Psychology*, *70*(1), 141–156.
https://doi.org/10.1037/0022-3514.70.1.141

Clement, R. W., & Krueger, J. (2000). The primacy of self-referent information in
perceptions of social consensus. *British Journal of Social Psychology*, *39*, 279–299. https://doi.org/10.1348/014466600164471

Clement, R. W., & Krueger, J. (2002). Social categorization moderates social
projection. *Journal of Experimental Social Psychology*, *38*(3), 219–231.
https://doi.org/10.1006/jesp.2001.1503

Coats, S., Smith, E. R., Claypool, H. M., & Banner, M. J. (2000). Overlapping mental
representations of self and in-group: Reaction time evidence and its relationship
with explicit measures of group identification. *Journal of Experimental Social
Psychology*, *36*, 304–315. https://doi.org/10.1006/jesp.1999.1416

Davis, T., & Goldwater, M. (2021). Using model-based neuroimaging to adjudicate
structured and continuous representational accounts in same-different
categorization and beyond. *Current Opinion in Behavioral Sciences*, *37*, 103–108.
https://doi.org/10.1016/j.cobeha.2020.11.011

Davis, T., & Love, B. C. (2010). Memory for category information is idealized through
contrast with competing options. *Psychological Science*, *21*(2), 234–242.
https://doi.org/10.1177/0956797609357712

Davis, T., Love, B. C., & Preston, A. R. (2012a). Striatal and hippocampal entropy and
recognition signals in category learning: Simultaneous processes revealed by
model-based fMRI. *Journal of Experimental Psychology: Learning, Memory, and
Cognition*, *38*(4), 821–839. https://doi.org/10.1037/a0027865

Davis, T., Love, B. C., & Preston, A. R. (2012b). Learning the exception to the rule:
Model-based fMRI reveals specialized representations for surprising category
members. *Cerebral Cortex*, *22*(2), 260–273.
https://doi.org/10.1093/cercor/bhr036

Daw, N. D. (2011). Trial-by-trial data analysis using computational models. In
*Decision making, affect, and learning: Attention and performance XXIII* (Vol. 23).
Oxford University Press.

de la Haye, A.-M. (2000). A methodological note about the measurement of the false-consensus effect. *European Journal of Social Psychology*, *30*(4), 569–581.
https://doi.org/10.1002/1099-0992(200007/08)30:4<569::AID-EJSP8>3.0.CO;2-V

DiDonato, T. E., Ullrich, J., & Krueger, J. I. (2011). Social perception as induction and
inference: An integrative model of intergroup differentiation, ingroup favoritism,
and differential accuracy. *Journal of Personality and Social Psychology*, *100*, 66–83. https://doi.org/10.1037/a0021051

Don, H. J., Otto, A. R., Cornwall, A. C., Davis, T., & Worthy, D. A. (2019). Learning
reward frequency over reward probability: A tale of two learning rules. *Cognition*,
*193*, 104042. https://doi.org/10.1016/j.cognition.2019.104042

Don, H. J., & Worthy, D. A. (2022). Frequency effects in action versus value learning.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *48*,
1311–1327. https://doi.org/10.1037/xlm0000896

Doosje, B., Ellemers, N., & Spears, R. (1995). Perceived intragroup variability as a
function of group status and identification. *Journal of Experimental Social
Psychology*, *31*(5), 410–436. https://doi.org/10.1006/jesp.1995.1018

Eager, C., & Roy, J. (2017). *Mixed effects models are sometimes terrible*
(arXiv:1701.04858). arXiv. https://doi.org/10.48550/arXiv.1701.04858

Elder, J., Cheung, B., Davis, T., & Hughes, B. (2023). Mapping the self: A network
approach for understanding psychological and neural representations of self-concept structure. *Journal of Personality and Social Psychology*, *124*(2), 237–263. https://doi.org/10.1037/pspa0000315

Elder, J., Davis, T. H., & Hughes, B. L. (2023). A fluid self-concept: How the brain
maintains coherence and positivity across an interconnected self-concept while
incorporating social feedback. *Journal of Neuroscience*.
https://doi.org/10.1523/JNEUROSCI.1951-22.2023

Elder, J., Davis, T., & Hughes, B. (2022a). Self-concept certainty and stability are
associated with semantic relations between self-beliefs. *PsyArXiv*.
https://doi.org/10.31234/osf.io/8y2vr

Elder, J., Davis, T., & Hughes, B. (2022b). Self-derogating to align with group norms:
Similarity-based learning drives assimilation of the group to the self. *PsyArXiv*.
https://doi.org/10.31234/osf.io/38bf7

Elder, J., Davis, T., & Hughes, B. L. (2022c). Learning about the self: Motives for
coherence and positivity constrain learning from self-relevant social feedback.
*Psychological Science*, *33*(4), 629–647.
https://doi.org/10.1177/09567976211045934

Ellemers, N., Spears, R., & Doosje, B. (2001). Self and social identity. *Annual Review of Psychology*, *53*, 161–186.

Estes, W. K. (1976). The cognitive side of probability learning. *Psychological Review*,
*83*, 37–64. https://doi.org/10.1037/0033-295X.83.1.37

FeldmanHall, O., & Shenhav, A. (2019). Resolving uncertainty in a social world. *Nature
Human Behaviour*, *3*(5), 426–435. https://doi.org/10.1038/s41562-019-0590-x

Fielding, K. S., & Hogg, M. A. (1997). Social identity, self-categorization, and
leadership: A field study of small interactive groups. *Group Dynamics: Theory,
Research, and Practice*, *1*(1), 39–51. https://doi.org/10.1037/1089-2699.1.1.39

Fiske, S. T., Dupree, C. H., Nicolas, G., & Swencionis, J. K. (2016). Status, power, and
intergroup relations: The personal is the societal. *Current Opinion in Psychology*,
*11*, 44–48. https://doi.org/10.1016/j.copsyc.2016.05.012

Gaertner, S. L., Dovidio, J. F., Guerra, R., Hehman, E., & Saguy, T. (2016). A common
ingroup identity: Categorization, identity, and intergroup relations. In *Handbook of prejudice, stereotyping, and discrimination* (2nd ed., pp. 433–454). Psychology
Press. https://doi.org/10.4324/9781841697772

Goldstone, R. L., Medin, D. L., & Gentner, D. (1991). Relational similarity and the
nonindependence of features in similarity judgments. *Cognitive Psychology*,
*23*(2), 222–262. https://doi.org/10.1016/0010-0285(91)90010-L

Gramzow, R. H., & Gaertner, L. (2005). Self-esteem and favoritism toward novel in-groups: The self as an evaluative base. *Journal of Personality and Social
Psychology*, *88*(5), 801–815. https://doi.org/10.1037/0022-3514.88.5.801

Gramzow, R. H., Gaertner, L., & Sedikides, C. (2001). Memory for in-group and out-group information in a minimal group context: The self as an informational base.
*Journal of Personality and Social Psychology*, *80*(2), 188–205.
https://doi.org/10.1037/0022-3514.80.2.188

Green, P., & MacLeod, C. J. (2016). SIMR: An R package for power analysis of
generalized linear mixed models by simulation. *Methods in Ecology and
Evolution*, *7*(4), 493–498. https://doi.org/10.1111/2041-210X.12504

Griffiths, T. L., Steyvers, M., & Tenenbaum, J. B. (2007). Topics in semantic
representation. *Psychological Review*, *114*, 211–244.
https://doi.org/10.1037/0033-295X.114.2.211

Guest, O., & Martin, A. E. (2021). How computational modeling can force theory
building in psychological science. *Perspectives on Psychological Science*, *16*(4),
789–802. https://doi.org/10.1177/1745691620970585

Guillaume, J. H. A., Jakeman, J. D., Marsili-Libelli, S., Asher, M., Brunner, P., Croke,
B., Hill, M. C., Jakeman, A. J., Keesman, K. J., Razavi, S., & Stigter, J. D.
(2019). Introductory overview of identifiability analysis: A guide to evaluating
whether you have the right type of data for your modeling purpose.
*Environmental Modelling & Software*, *119*, 418–432.
https://doi.org/10.1016/j.envsoft.2019.07.007

Haslam, S. A., Oakes, P. J., Turner, J. C., & McGarty, C. (1995). Social categorization
and group homogeneity: Changes in the perceived applicability of stereotype
content as a function of comparative context and trait favourableness. *British
Journal of Social Psychology*, *34*(2), 139–160. https://doi.org/10.1111/j.2044-8309.1995.tb01054.x

Heit, E., & Rubinstein, J. (1994). Similarity and property effects in inductive reasoning.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *20*(2),
411–422. https://doi.org/10.1037/0278-7393.20.2.411

Hewstone, M., Rubin, M., & Willis, H. (2002). Intergroup bias. *Annual Review of
Psychology*, *53*, 575–604.
https://doi.org/10.1146/annurev.psych.53.100901.135109

Hirsh, J. B., Mar, R. A., & Peterson, J. B. (2012). Psychological entropy: A framework
for understanding uncertainty-related anxiety. *Psychological Review*, *119*(2),
304–320. https://doi.org/10.1037/a0026767

Hogg, M. A. (2007). Uncertainty-identity theory. In *Advances in experimental social
psychology* (Vol. 39, pp. 69–126). Elsevier Academic Press.
https://doi.org/10.1016/S0065-2601(06)39002-8

Hogg, M. A. (2014). From uncertainty to extremism: Social categorization and identity
processes. *Current Directions in Psychological Science*, *23*(5), 338–342.
https://doi.org/10.1177/0963721414540168

Hogg, M. A., & Abrams, D. (1988). *Social identifications: A social psychology of
intergroup relations and group processes*. Routledge.

Hogg, M. A., Abrams, D., Otten, S., & Hinkle, S. (2004). The social identity
perspective: Intergroup relations, self-conception, and small groups. *Small Group
Research*, *35*(3), 246–276. https://doi.org/10.1177/1046496404263424

Hogg, M. A., & Hains, S. C. (1996). Intergroup relations and group solidarity: Effects of
group identification and social beliefs on depersonalized attraction. *Journal of
Personality and Social Psychology*, *70*(2), 295–309. https://doi.org/10.1037/0022-3514.70.2.295

Hogg, M. A., Hardie, E. A., & Reynolds, K. J. (1995). Prototypical similarity, self-categorization, and depersonalized attraction: A perspective on group
cohesiveness. *European Journal of Social Psychology*, *25*(2), 159–177.
https://doi.org/10.1002/ejsp.2420250204

Hong, Y., & Ratner, K. G. (2021). Minimal but not meaningless: Seemingly arbitrary
category labels can imply more than group membership. *Journal of Personality
and Social Psychology*, *120*(3), 576–600. https://doi.org/10.1037/pspa0000255

Hornsey, M. J., & Hogg, M. A. (1999). Subgroup differentiation as a response to an
overly-inclusive group: A test of optimal distinctiveness theory. *European
Journal of Social Psychology*, *29*, 543–550.

Hornsey, M. J., & Hogg, M. A. (2000). Assimilation and diversity: An integrative model
of subgroup relations. *Personality and Social Psychology Review*, *4*, 143–156.
https://doi.org/10.1207/S15327957PSPR0402_03

Huys, Q. J. M., Cools, R., Gölzer, M., Friedel, E., Heinz, A., Dolan, R. J., & Dayan, P.
(2011). Disentangling the roles of approach, activation and valence in
instrumental and Pavlovian responding. *PLOS Computational Biology*, *7*(4),
e1002028. https://doi.org/10.1371/journal.pcbi.1002028

Iyengar, S., Lelkes, Y., Levendusky, M., Malhotra, N., & Westwood, S. J. (2019). The
origins and consequences of affective polarization in the United States. *Annual
Review of Political Science*, *22*(1), 129–146. https://doi.org/10.1146/annurev-polisci-051117-073034

James, W. (1890). *The principles of psychology* (Vol. 1). Henry Holt and Co.
https://doi.org/10.1037/10538-000

Jost, J. T., & Banaji, M. R. (1994). The role of stereotyping in system-justification and
the production of false consciousness. *British Journal of Social Psychology*,
*33*(1), 1–27. https://doi.org/10.1111/j.2044-8309.1994.tb01008.x

Judd, C. M., Westfall, J., & Kenny, D. A. (2012). Treating stimuli as a random factor in
social psychology: A new and comprehensive solution to a pervasive but largely
ignored problem. *Journal of Personality and Social Psychology*, *103*(1), 54–69.
https://doi.org/10.1037/a0028347

Krueger, J. (2007). From social projection to social behaviour. *European Review of
Social Psychology*, *18*(1), 1–35. https://doi.org/10.1080/10463280701284645

Krueger, J., & Clement, R. W. (1994). The truly false consensus effect: An ineradicable
and egocentric bias in social perception. *Journal of Personality and Social
Psychology*, *67*, 596–610. https://doi.org/10.1037/0022-3514.67.4.596

Krueger, J., & Clement, R. W. (1996). Inferring category characteristics from sample
characteristics: Inductive reasoning and social projection. *Journal of
Experimental Psychology: General*, *125*(1), 52–68.

Kubinec, R. (2022). Ordered beta regression: A parsimonious, well-fitting model for
continuous data with lower and upper bounds. *Political Analysis*, *31*, 519–536. https://doi.org/10.1017/pan.2022.20

Lakens, D., Scheel, A. M., & Isager, P. M. (2018). Equivalence testing for psychological
research: A tutorial. *Advances in Methods and Practices in Psychological
Science*, *1*(2), 259–269. https://doi.org/10.1177/2515245918770963

Latrofa, M., Vaes, J., & Cadinu, M. (2012). Self-stereotyping: The central role of an
ingroup threatening identity. *The Journal of Social Psychology*, *152*(1), 92–111.
https://doi.org/10.1080/00224545.2011.565382

Latrofa, M., Vaes, J., Pastore, M., & Cadinu, M. (2009). "United we stand, divided we
fall"! The protective function of self-stereotyping for stigmatised members'
psychological well-being. *Applied Psychology: An International Review*, *58*(1),
84–104. https://doi.org/10.1111/j.1464-0597.2008.00383.x

Leach, C. W., van Zomeren, M., Zebel, S., Vliek, M. L. W., Pennekamp, S. F., Doosje,
B., Ouwerkerk, J. W., & Spears, R. (2008). Group-level self-definition and self-investment: A hierarchical (multicomponent) model of in-group identification.
*Journal of Personality and Social Psychology*, *95*(1), 144–165.
https://doi.org/10.1037/0022-3514.95.1.144

Leary, M. R., Kelly, K. M., Cottrell, C. A., & Schreindorfer, L. S. (2013). Construct
validity of the need to belong scale: Mapping the nomological network.
*Journal of Personality Assessment*, *95*(6), 610–624.
https://doi.org/10.1080/00223891.2013.819511

Lelkes, Y., & Westwood, S. J. (2017). The limits of partisan prejudice. *The Journal of
Politics*, *79*(2), 485–501. https://doi.org/10.1086/688223

Leonardelli, G. J., Pickett, C. L., & Brewer, M. B. (2010). Optimal distinctiveness theory:
A framework for social identity, social cognition, and intergroup relations. In
*Advances in experimental social psychology* (Vol. 43, pp. 63–113). Elsevier.

Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., & Makowski, D. (2021).
performance: An R package for assessment, comparison and testing of
statistical models. *Journal of Open Source Software*, *6*(60), 3139.
https://doi.org/10.21105/joss.03139

Luhtanen, R., & Crocker, J. (1992). A collective self-esteem scale: Self-evaluation of
one's social identity. *Personality and Social Psychology Bulletin*, *18*(3), 302–318. https://doi.org/10.1177/0146167292183006

Maddox, W. T., & Ashby, F. G. (1993). Comparing decision bound and exemplar models
of categorization. *Perception & Psychophysics*, *53*(1), 49–70.
https://doi.org/10.3758/BF03211715

Makowski, D., Ben-Shachar, M. S., Chen, S. H. A., & Lüdecke, D. (2019). Indices of
effect existence and significance in the Bayesian framework. *Frontiers in
Psychology*, *10*, 2767. https://doi.org/10.3389/fpsyg.2019.02767

Markus, H., & Wurf, E. (1987). The dynamic self-concept: A social psychological
perspective. *Annual Review of Psychology*, *38*, 299–337.
https://doi.org/10.1146/annurev.ps.38.020187.001503

Mullen, B. (1991). Group composition, salience, and cognitive representations: The
phenomenology of being in a group. *Journal of Experimental Social Psychology*,
*27*, 297–323. https://doi.org/10.1016/0022-1031(91)90028-5

Murayama, K., Usami, S., & Sakaki, M. (2022). Summary-statistics-based power
analysis: A new and practical method to determine sample size for mixed-effects
modeling. *Psychological Methods*. https://doi.org/10.1037/met0000330

Nelson, L. J., & Miller, D. T. (1995). The distinctiveness effect in social categorization:
You are what makes you unusual. *Psychological Science*, *6*, 246–249.
https://doi.org/10.1111/j.1467-9280.1995.tb00600.x

Nicenboim, B., & Vasishth, S. (2016). Statistical methods for linguistic research:
Foundational ideas—Part II. *Language and Linguistics Compass*, *10*(11), 591–613. https://doi.org/10.1111/lnc3.12207

Nosofsky, R. M. (1984). Choice, similarity, and the context theory of classification.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *10*, 104–114. https://doi.org/10.1037/0278-7393.10.1.104

Nosofsky, R. M. (1986). Attention, similarity, and the identification–categorization
relationship. *Journal of Experimental Psychology: General*, *115*(1), 39–57.
https://doi.org/10.1037/0096-3445.115.1.39

Nosofsky, R. M. (1988). Similarity, frequency, and category representations. *Journal of
Experimental Psychology: Learning, Memory, and Cognition*, *14*(1), 54–65.
https://doi.org/10.1037/0278-7393.14.1.54

Nosofsky, R. M. (1991). Typicality in logically defined categories: Exemplar-similarity
versus rule instantiation. *Memory & Cognition*, *19*(2), 131–150.
https://doi.org/10.3758/BF03197110

Nosofsky, R. M. (2011). The generalized context model: An exemplar model of
classification. In A. J. Wills & E. M. Pothos (Eds.), *Formal approaches in
categorization* (pp. 18–39). Cambridge University Press.
https://doi.org/10.1017/CBO9780511921322.002

Obst, P., White, K., Mavor, K., & Baker, R. (2011). Social identification dimensions as
mediators of the effect of prototypicality on intergroup behaviours. *Psychology*,
*2*, 265–269. https://doi.org/10.4236/psych.2011.25066

Otten, S. (2003). "Me and us" or "us and them"? The self as a heuristic for defining
minimal ingroups. *European Review of Social Psychology*, *13*(1), 1–33.
https://doi.org/10.1080/10463280240000028

Otten, S. (2004). Self-anchoring as predictor of in-group favoritism: Is it applicable to
real group contexts? *Current Psychology of Cognition*, *22*(4/5), 427–444.

Otten, S., & Epstude, K. (2006). Overlapping mental representations of self, ingroup, and
outgroup: Unraveling self-stereotyping and self-anchoring. *Personality & Social
Psychology Bulletin*, *32*(7), 957–969. https://doi.org/10.1177/0146167206287254

Otten, S., & Wentura, D. (2001). Self-anchoring and in-group favoritism: An individual
profiles analysis. *Journal of Experimental Social Psychology*, *37*(6), 525–532.
https://doi.org/10.1006/jesp.2001.1479

Postmes, T., Haslam, S. A., & Jans, L. (2013). A single-item measure of social
identification: Reliability, validity, and utility. *British Journal of Social
Psychology*, *52*(4), 597–617. https://doi.org/10.1111/bjso.12006

Rabinovich, A., & Morton, T. A. (2011). Subgroup identities as a key to cooperation
within large social groups. *British Journal of Social Psychology*, *50*(1), 36–51.
https://doi.org/10.1348/014466610X486356

Riketta, M., & Sacramento, C. A. (2008). "They cooperate with us, so they are like me":
Perceived intergroup relationship moderates projection from self to outgroups.
*Group Processes & Intergroup Relations*, *11*(1), 115–131.
https://doi.org/10.1177/1368430207084849

Robinaugh, D. J., Haslbeck, J. M. B., Ryan, O., Fried, E. I., & Waldorp, L. J. (2021).
Invisible hands and fine calipers: A call to use formal theory as a toolkit for
theory construction. *Perspectives on Psychological Science*, *16*(4), 725–743.
https://doi.org/10.1177/1745691620974697

Rosch, E., & Lloyd, B. B. (1978). *Principles of categorization*. Lawrence Erlbaum Associates.

Rosenberg, M. (1965). *Society and the adolescent self-image*. Princeton University Press.

Roth, J., Steffens, M. C., & Vignoles, V. L. (2018). Group membership, group change,
and intergroup attitudes: A recategorization model based on cognitive
consistency principles. *Frontiers in Psychology*, *9*, 479.
https://doi.org/10.3389/fpsyg.2018.00479

Schneider, M. J., Rubin-McGregor, J., Elder, J., Hughes, B., & Tamir, D. (2022).
Simulation requires activation of self-knowledge to change self-concept.
*PsyArXiv*. https://doi.org/10.31234/osf.io/92mru

Schubert, T. W., & Otten, S. (2002). Overlap of self, ingroup, and outgroup: Pictorial
measures of self-categorization. *Self and Identity*, *1*, 353–376.
https://doi.org/10.1080/152988602760328012

Shannon, C. E. (1948). A mathematical theory of communication. *Bell System
Technical Journal*, *27*(3), 379–423. https://doi.org/10.1002/j.1538-7305.1948.tb01338.x

Shepard, R. N. (1987). Toward a universal law of generalization for psychological
science. *Science*, *237*(4820), 1317–1323. https://doi.org/10.1126/science.3629243

Sherman, D. K., & Kim, H. S. (2005). Is there an "I" in "team"? The role of the self in
group-serving judgments. *Journal of Personality and Social Psychology*, *88*,
108–120. https://doi.org/10.1037/0022-3514.88.1.108

Simon, B., & Brown, R. (1987). Perceived intragroup homogeneity in minority-majority
contexts. *Journal of Personality and Social Psychology*, *53*, 703–711.
https://doi.org/10.1037/0022-3514.53.4.703

Smith, E. R., & Henry, S. (1996). An in-group becomes part of the self: Response time
evidence. *Personality and Social Psychology Bulletin*, *22*, 635–642.
https://doi.org/10.1177/0146167296226008

Sorensen, T., Hohenstein, S., & Vasishth, S. (2016). Bayesian linear mixed models using
Stan: A tutorial for psychologists, linguists, and cognitive scientists. *The
Quantitative Methods for Psychology*, *12*(3), 175–200.
https://doi.org/10.20982/tqmp.12.3.p175

Spears, R., Doosje, B., & Ellemers, N. (1997). Self-stereotyping in the face of threats to
group status and distinctiveness: The role of group identification. *Personality
and Social Psychology Bulletin*, *23*(5), 538–553.
https://doi.org/10.1177/0146167297235009

Spencer-Rodgers, J., Srivastava, S., Boucher, H. C., English, T., Paletz, S. B., & Peng, K.
(2015). *The dialectical self scale*. Unpublished manuscript.
https://doi.org/10.13140/RG.2.1.3695.5928

Tajfel, H. (1974). Social identity and intergroup behaviour. *Social Science Information*,
*13*(2), 65–93. https://doi.org/10.1177/053901847401300204

Tajfel, H. (1978). *Differentiation between social groups: Studies in the social psychology
of intergroup relations*. Academic Press.

Tajfel, H., & Billig, M. (1974). Familiarity and categorization in intergroup behavior.
*Journal of Experimental Social Psychology*, *10*, 159–170.
https://doi.org/10.1016/0022-1031(74)90064-X

Tajfel, H., Sheikh, A. A., & Gardner, R. C. (1964). Content of stereotypes and the
inference of similarity between members of stereotyped groups. *Acta
Psychologica*, *22*, 191–201.

Tropp, L. R., & Wright, S. C. (2001). Ingroup identification as the inclusion of ingroup in
the self. *Personality and Social Psychology Bulletin*, *27*, 585–600.
https://doi.org/10.1177/0146167201275007

Turner, J. C., Hogg, M. A., Oakes, P. J., Reicher, S. D., & Wetherell, M. S. (1987).
*Rediscovering the social group: A self-categorization theory*. Basil Blackwell.

Turner, J. C., Oakes, P. J., Haslam, S. A., & McGarty, C. (1994). Self and collective:
Cognition and social context. *Personality and Social Psychology Bulletin*, *20*(5),
454–463.

Tversky, A. (1977). Features of similarity. *Psychological Review*, *84*(4), 327–352.
https://doi.org/10.1037/0033-295X.84.4.327

Tyler, L. K., & Moss, H. E. (2001). Towards a distributed account of conceptual
knowledge. *Trends in Cognitive Sciences*, *5*, 244–252.
https://doi.org/10.1016/S1364-6613(00)01651-X

Unkelbach, C. (2007). Reversing the truth effect: Learning the interpretation of
processing fluency in judgments of truth. *Journal of Experimental Psychology:
Learning, Memory, and Cognition*, *33*(1), 219–230. https://doi.org/10.1037/0278-7393.33.1.219

Unkelbach, C., Koch, A., Silva, R. R., & Garcia-Marques, T. (2019). Truth by repetition:
Explanations and implications. *Current Directions in Psychological Science*,
*28*(3), 247–253. https://doi.org/10.1177/0963721419827854

Unkelbach, C., & Rom, S. C. (2017). A referential theory of the repetition-induced truth
effect. *Cognition*, *160*, 110–126. https://doi.org/10.1016/j.cognition.2016.12.016

van Veelen, R., Eisenbeiss, K. K., & Otten, S. (2016). Newcomers to social categories:
Longitudinal predictors and consequences of ingroup identification. *Personality
and Social Psychology Bulletin*, *42*(6), 811–825.
https://doi.org/10.1177/0146167216643937

van Veelen, R., Otten, S., Cadinu, M., & Hansen, N. (2016). An integrative model of
social identification: Self-stereotyping and self-anchoring as two cognitive
pathways. *Personality and Social Psychology Review*, *20*(1), 3–26.
https://doi.org/10.1177/1088868315576642

van Veelen, R., Otten, S., & Hansen, N. (2011). Linking self and ingroup: Self-anchoring
as distinctive cognitive route to social identification. *European Journal of Social
Psychology*, *41*(5), 628–637. https://doi.org/10.1002/ejsp.792

van Veelen, R., Otten, S., & Hansen, N. (2013a). Social identification when an in-group
identity is unclear: The role of self-anchoring and self-stereotyping. *British
Journal of Social Psychology*, *52*(3), 543–562. https://doi.org/10.1111/j.2044-8309.2012.02110.x

van Veelen, R., Otten, S., & Hansen, N. (2013b). A personal touch to diversity: Self-anchoring increases minority members' identification in a diverse group. *Group
Processes & Intergroup Relations*, *16*(6), 671–683.
https://doi.org/10.1177/1368430212473167

Vehtari, A., Gelman, A., & Gabry, J. (2017). Practical Bayesian model evaluation using
leave-one-out cross-validation and WAIC. *Statistics and Computing*, *27*(5), 1413–1432. https://doi.org/10.1007/s11222-016-9696-4

Vehtari, A., Gelman, A., Simpson, D., Carpenter, B., & Bürkner, P.-C. (2021). Rank-normalization, folding, and localization: An improved R-hat for assessing
convergence of MCMC (with discussion). *Bayesian Analysis*, *16*(2), 667–718.
https://doi.org/10.1214/20-BA1221

Vogel, T., Carr, E. W., Davis, T., & Winkielman, P. (2018). Category structure
determines the relative attractiveness of global versus local averages. *Journal of
Experimental Psychology: Learning, Memory, and Cognition*, *44*, 250–267.
https://doi.org/10.1037/xlm0000446

Yarkoni, T. (2022). The generalizability crisis. *Behavioral and Brain Sciences*, *45*, e1.
https://doi.org/10.1017/S0140525X20001685

Zeithamova, D., Maddox, W. T., & Schnyer, D. M. (2008). Dissociable prototype
learning systems: Evidence from brain imaging and behavior. *Journal of
Neuroscience*, *28*(49), 13194–13201. https://doi.org/10.1523/JNEUROSCI.2915-08.2008
