---
title: "Building 'Us' in the Image of 'I': The Constructive Cognitive Architecture of Social Identity"
shorttitle: "Constructive Architecture of Social Identity"
author:
  - name: Jacob J. Elder
    affiliations:
      - name: University of California, Riverside
        department: Psychology
    corresponding: true
    email: jelder@ucr.edu
abstract: >-
  People tend to see themselves as similar to their ingroup, often by projecting self-beliefs onto their perceptions of others. The within-person cognitive mechanisms underlying this process remain under-specified. This research formalizes self-anchoring as similarity-based generalization across a semantic trait network, establishing the relational (e.g., if I am outgoing, my group should be characteristic of semantically related traits like sociable) and contrastive (i.e., how the ingroup compares to a specific outgroup) mechanisms through which self-evaluations generalize to the ingroup. Across three studies using minimal groups (N = 61), university groups (N = 181), and racial groups (N = 265), individuals used semantic similarity among traits to infer group characteristics from their own attributes. Self-anchoring operated through a single symmetric projection slope — ingroup assimilation and outgroup repulsion were not architecturally dissociable across any of the three studies. The projection slope and generalization sensitivity showed cross-context variation, but the prior ingroup preference (γ) was most systematically context-sensitive: it attenuated sharply when participants contrasted against a positively-regarded, higher-status outgroup (Study 2), and was elevated when minority-group members contrasted against the racial majority (Study 3). Similarity-based inference was absent under minority–minority racial contrasts, consistent with shared subordinate status reducing the functional distinctiveness of the between-group boundary. Model-derived semantic contrast ratios (MCR) correlated with self-esteem, self-concept clarity, and dialectical self-views in Studies 1 and 2 and in a pooled cross-contextual canonical correlation analysis.
keywords: [self-anchoring, social identity, category learning, semantic similarity, computational modeling]
format:
  apaquarto-docx: default
---

```{r}
#| label: setup
#| include: false
library(here)
here::i_am("Manuscript/ElderJacob_JPSP_Submission.qmd")
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.pos = "H", out.width = "100%")
# Figures are generated by Figures/make_figures.R.
# Run that script first if figures are missing.
fig_path <- function(...) file.path(here(), "Figures", ...)
```

## INTRODUCTION
People carry stable self-beliefs across situations (Markus & Wurf, 1987) yet maintain a sense of belonging (Baumeister & Leary, 1995) by assimilating into their social groups (Brewer, 1991; Ellemers et al., 2001). Through this similarity, social identification is sustained and strengthened—a sense of positive attachment central to group life (Tajfel, 1978; Turner et al., 1987). Social psychology has conceptualized group membership as "depersonalization," where the self is categorized as an interchangeable exemplar of a group prototype (Turner et al., 1987). This account—often termed "self-stereotyping"—emphasizes assimilation of group attributes into the self-concept but does not explain how people identify with novel groups or maintain self-beliefs that remain stable across group memberships (van Veelen et al., 2016).

Rather than only assimilating group attributes, people also project their own attributes onto their ingroup (M. Cadinu & Rothbart, 1996) and others in interpersonal contexts (Ames, 2004). This process, known as self-anchoring, provides an informational base (Gramzow et al., 2001) for inductive inference about the group from self-knowledge (DiDonato et al., 2011; Krueger, 2007). Self-anchoring is most pronounced when group knowledge is ambiguous or diagnostic information is absent (van Veelen et al., 2013a), making it central to the emergence of social identity.

The present approach builds on, but departs from, two prior accounts in a common way: both retained the self as a valid informational anchor but left the generalization mechanism unspecified. Dawes (1989) and Krueger (1998) showed that projecting one's own traits to the group is statistically rational: the self is a sample of one, and a sample beats no data. We retain that logic — the self as a valid informational anchor — but replace trait-independent updating with inference through the network's relational structure. Cadinu and Rothbart's (1996) analogical transfer account identified the self-to-group direction and its centrality to minimal-group identity, but left the process as a verbal description. Formalizing it via Shepard's (1987) generalization law and Turner et al.'s (1987) metacontrast principle yields predictions about how people use relational similarity to generalize self-knowledge, bridging these different accounts.

### Inferences About the Ingroup Based on the Self
Despite the apparent strength of evidence for self-anchoring, most research in this domain has relied on correlated ratings of identical traits across the self and group (M. Cadinu & Rothbart, 1996; Otten & Wentura, 2001). These tests provide evidence of rating stability but do not demonstrate *generalization* per se. Traditional measures are also vulnerable to repetition effects; mere repetition of information can cause it to be perceived as more characteristic (Unkelbach et al., 2019). A rigorous test of the generalization-based theory requires establishing that self-evaluations propagate across semantically related but novel traits (Heit & Rubinstein, 1994). If an individual perceives themselves as "outgoing," do they infer that their group is characteristic of semantically similar traits like "sociable" and "fun," even without explicitly evaluating those attributes?

In the current research, we move social identity theory from a verbal, descriptive model to a formal architecture by integrating principles of category learning. We frame the self as a semantic prototype in a high-dimensional space, where group beliefs emerge through similarity-based generalization consistent with Shepard's (1987) universal law of generalization. To formalize this process, we utilize a semantic dependency network of 148 positive traits, constructed using data from 178 Amazon Mechanical Turk participants with a 25% consensus threshold. From this network, we derive relational similarity measures (network-based Dice similarity; Equation 1) that quantify how self-representations propagate across the trait network.

This network approach enables the first formal implementation of the "metacontrast principle," which posits that group categorization is defined by the ratio of an individual’s similarity to the ingroup relative to the individual’s similarity to the outgroup (Turner et al., 1987). While the metacontrast principle has been central to social identity research for decades, it has remained a verbal description (Davis & Goldwater, 2021). Structurally, Turner’s metacontrast ratio is formally isomorphic to Nosofsky’s (1986) Generalized Context Model—both define category membership via a ratio of summed similarities; this formal equivalence provides the mathematical structure Turner’s verbal account required. The present model borrows the GCM’s formal ratio structure, not its exemplar architecture: the self functions here as a prototype rather than a stored exemplar set. Importantly, similarity-based inference drives both classification within categories and contrast of distinctive features between them (Tversky, 1977): the same semantic network developed in prior work (J. Elder et al., 2023) that supports ingroup assimilation also licenses contrastive differentiation from the outgroup. This formal bridge between Shepard’s (1987) universal law of generalization, Nosofsky’s GCM, and Turner’s metacontrast principle formalizes computationally what social identity theory has described verbally.

### The Current Design
We utilize a "training-to-generalization" paradigm common in concept learning research (Bowman et al., 2020). Participants first self-evaluate on a subset of traits (training phase), which serve as exemplars of the self-concept prototype. This is followed by a "generalization phase" where participants classify traits—including novel traits not seen during training—as more characteristic of either the ingroup or outgroup. Using the traits’ semantic similarities to the self-concept, we predict the likelihood of ingroup classification.

Across three studies, we examine how various intergroup contexts amplify or attenuate these generalization weights. A cross-cutting question is whether ingroup assimilation and outgroup repulsion are architecturally dissociable — or whether a single projection slope absorbs both within the paradigm's binary forced-choice structure. Study 1 utilizes minimal groups to provide a proof-of-concept for similarity-based generalization. Study 2 examines the role of relative social status using university groups, testing whether status context modulates the prior ingroup preference (γ), the projection slope (α), or the breadth of self-concept generalization (λ)—and whether real social categories with meaningful status histories can dissociate ingroup assimilation from outgroup repulsion in ways that minimal groups cannot. Study 3 applies this framework to racial identities, examining how majority or minority outgroup contrasts exert differential effects on the tendency to self-anchor.

## STUDY 1: SELF-ANCHORING BASED ON MINIMAL CONDITIONS
Study 1 provided a first proof-of-concept for similarity-based generalization in a minimal group context where group knowledge is absent. Study 1 was pre-registered at OSF (https://osf.io/7jn3e). We pre-registered three predictions: that Similarity-to-Self predicts ingroup classification, that this effect extends to novel unseen traits, and that individual differences in independent self-construal, self-esteem, need for cognition, and self-concept clarity would correlate with self-anchoring strength. Computational modeling analyses and MCR-based individual differences are exploratory.

### Methods
**Participants**
From an initial pool of 80 participants, 19 were excluded (final *N* = 61). Exclusions were applied for: failure to consent to data use after debriefing (*n* = 9), self-reported low task seriousness (< 4 on a 7-point item; *n* = 1), self-reported unusable data (*n* = 2), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 10). Participants were native English-speaking university students (40.98% Cisgender Female, 59.02% Cisgender Male; *M*<sub>Age</sub> = 19.95, *SD*<sub>Age</sub> = 1.51, Range<sub>Age</sub> = [18, 25]), with an ethnic composition of 9.84% White/Caucasian, 11.48% Mixed/Other, 32.79% Asian, 40.98% Hispanic/Latino, and 4.92% Native-American. A power analysis using *simr* (Green & MacLeod, 2016) on a prior relational similarity dataset indicated that *N* = 5 was sufficient to detect within-subjects effects at 95% power. This seemingly low threshold reflects the statistical structure of multilevel models: within-subjects fixed effects are powered by Level-1 observations — here, 148 binary classification trials per participant — rather than by the number of Level-2 clusters. With 148 observations per person, detecting fixed effects on within-person variation achieves high power at small N; the final sample of *N* = 61 provides substantial additional power and enables detection of between-person individual differences. Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 61 can detect correlations of *r* ≥ .34 at 80% power (α = .05, two-tailed).

**Network Procedure**
We utilized a semantic dependency network of 148 traits constructed using data from 178 Amazon Mechanical Turk participants (25% consensus threshold). This network captures psychological implication structure (e.g., "If I am brave, I am adventurous") rather than linguistic co-occurrence. Static word embeddings (e.g., GloVe) are ill-suited for this purpose on two grounds: antonyms acquire high cosine similarity because they appear in identical sentence contexts, and cosine similarity is symmetric, discarding the directional dependencies (e.g., *Thoughtful* → *Humble* but not vice versa) that the dependency network preserves. From this network, we derived network-based Dice similarity (@eq-dice), representing the proportion of shared neighbors between traits.

$$S_{ij} = \frac{2|N(i) \cap N(j)|}{|N(i)| + |N(j)|}$$ {#eq-dice}

where $N(i)$ and $N(j)$ denote the neighbor sets of traits $i$ and $j$ in the semantic dependency network.

A visualization of the full semantic trait network is provided in Supplementary Materials F.

**Design**
*Training phase.* Participants self-evaluated approximately 60% of the network (90 traits) on a Likert scale from 1 (*Not at all*) to 7 (*Extremely*). Following a dot-estimation minimal group assignment task (NEST), participants were randomly assigned to be "overestimators" or "underestimators." In the *generalization phase*, participants classified all 148 traits in the network as characteristic of either the ingroup or outgroup (148 trials). This included 90 repeated traits and 58 novel traits.

```{r}
#| label: fig-02-task-schematic
#| fig-cap: "Schematic of task design. Depicting training phase on top and generalization phase on bottom. Participants self-evaluate on 90 out of 148 traits on a Likert scale from 1 to 7. During generalization phase, 90 traits are thus repeated while 58 traits are novel and never received a self-evaluation. Participants then proceed through all traits in the semantic trait network, and classify whether each trait is characteristic of the ingroup or the outgroup."
#| eval: !expr file.exists(fig_path("fig02_task_schematic.tiff"))
knitr::include_graphics(fig_path("fig02_task_schematic.tiff"))
```

**Indices**
We computed *Similarity-to-Self* ($SS_g$; @eq-ss) as a similarity-weighted average of self-evaluations across training traits, capturing the degree to which the self-concept predicts the semantic neighborhood of each test trait. Results for a local self-concept clarity index (*H_g*) are reported in Supplementary Materials D.

$$SS_g = \frac{\sum_{t=1}^{T} E_t \cdot S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$ {#eq-ss}

where $E_t$ is the self-evaluation on training trait $t$, $S_{tg}$ is the Dice similarity between training trait $t$ and test trait $g$, and $T$ is the number of training traits.

Each computational model produces a *model-derived Metacontrast Ratio* (MCR) as a generated quantity (see *Computational Modeling* below), computed using parameter-calibrated similarity weights and individual projection gradients: $\text{MCR}_t = \text{simW}_{\text{in},t} / \text{simW}_{\text{out},t}$, where $\text{simW}_{\text{in}}$ and $\text{simW}_{\text{out}}$ are the generalization-weighted sums of projection onto ingroup- and outgroup-predictive self-knowledge, respectively. The subject-level MCR ($\overline{\text{MCR}}_s$) averages this ratio across trials, yielding a person-specific index of how strongly the semantic self-concept discriminates ingroup from outgroup classification. Because MCR is derived from similarity-weighted ingroup and outgroup evidence accumulated across trials, it is not simply a relabeling of the projection slope: it integrates projection slope, generalization sensitivity, and the person's actual self-rating profile into a single summary of ingroup-relative semantic contrast.

**Computational Modeling**
We compared four cognitive architectures based on category learning principles (Nosofsky, 2011) to test the representational structure of self-anchoring.

**Level 1: Bias Model (Motivational Baseline).** This model represents a general tendency to choose the ingroup regardless of trait content, serving as a baseline for ingroup favoritism:
$$P(\text{Ingroup} | g) = \text{logit}^{-1}(\text{logit}(\gamma))$$
where $\gamma$ is the bias parameter.

**Level 2: Symmetric Model (Traditional Self-Anchoring).** This model utilizes a single projection slope ($\alpha$) assuming that the rate of ingroup assimilation is mathematically identical to the rate of outgroup repulsion:
$$P(\text{Ingroup} | g) = \frac{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta}{\gamma \cdot (\sum_{t=1}^T S_{tg} \cdot G_t)^\beta + (1-\gamma) \cdot (\sum_{t=1}^T S_{tg} \cdot (1-G_t))^\beta}$$
where $G_t = \frac{1}{1 + e^{-\alpha(E_t-4)}}$ represents the latent belief transformed from self-evaluations ($E_t$).

**Level 3: Symmetric + $\lambda$ Model (The Generalization Gradient).** This model introduces Shepard’s Law by adding a generalization sensitivity parameter ($\lambda$), representing the decay of inference across semantic similarity ($S_{tg} \rightarrow S_{tg}^\lambda$). This architecture treats $\lambda$ as a core parameter defining the structural reach of the self-concept, independent of social target or bias. 

**Level 4: Asymmetric + $\lambda$ Model (The Full Architecture).** This model decouples the assimilation and repulsion processes into distinct parameters, $\alpha_{in}$ and $\alpha_{out}$, to test if social identity is driven by "ingroup love" or "outgroup hate":
$$G_{in,t} = \frac{1}{1 + e^{-\alpha_{in}(E_t-4)}} ; \quad G_{out,t} = \frac{1}{1 + e^{\alpha_{out}(E_t-4)}}$$
Novel traits—which have no training-phase self-evaluation and therefore carry only the $\lambda$-weighted similarity signal—provide the information needed to decouple $\alpha_{in}$ and $\alpha_{out}$ from each other and from the generalization sensitivity parameter ($\lambda$), allowing the model to separately estimate the assimilation and repulsion forces central to social identity theory.

To ensure identifiability of these parameters within a 2AFC task, we leveraged three computational strategies. First, we exploited the unique information provided by novel versus repeated traits; while repeated traits primarily inform projection extremity ($\alpha$), novel traits isolate the signal for generalization sensitivity ($\lambda$) by forcing the model to rely entirely on the semantic similarity matrix ($S$), as there are no self-beliefs available for information to project to novel traits. Second, we implemented the dual latent belief structure described above, allowing the model to distinguish choices driven by ingroup similarity from those driven by outgroup dissimilarity. Finally, we utilized hierarchical Bayesian regularization to stabilize individual estimates: by sharing statistical strength across participants, individual parameter estimates are shrunk toward the group mean, preventing extreme estimates from subjects with noisy or sparse data from distorting inference. To address a structural identifiability tradeoff between $\alpha$ and $\lambda$ — both of which amplify the ingroup-over-outgroup evidence ratio and therefore partially compete for trial-by-trial variance — we assigned a tighter dispersion prior to the individual-level $\lambda$ standard deviation ($\sigma_\lambda \sim \text{Half-Normal}(0, 0.1)$) relative to the projection slope ($\sigma_\alpha \sim \text{Half-Normal}(0, 0.3)$). This targeted shrinkage stabilizes individual $\lambda$ estimates toward the group mean, directing residual variance toward $\alpha$ and improving its individual-level identifiability; a schematic of this leverage is shown in Supplementary Figure B5. The empirical basis for this choice is detailed in Supplementary Materials B. Parameter-recovery analyses using both simulated and empirical parameter settings further showed that the Symmetric+$\lambda$ model is adequately identifiable for the present design. The fully asymmetric architecture was less recoverable under random-parameter simulation, but recovered substantially better under empirical recovery when true parameters were set to participants' observed posterior medians and their observed self-rating structure was preserved, suggesting that the weak random-simulation recovery partly reflects unrealistic parameter combinations and the loss of empirically occurring structure between ingroup and outgroup projection components (Supplementary Materials B; Figures B1-B4). In addition to log-likelihood (used for LOO-CV model comparison), each model outputs, as generated quantities, trial-level predicted choice probabilities ($\hat{P}_t = P_{\text{model},t}$) and a model-derived Metacontrast Ratio ($\widehat{\text{MCR}}_t = \text{simW}_{in,t} / \text{simW}_{out,t}$), where $\text{simW}_{in,t}$ and $\text{simW}_{out,t}$ are the parameter-calibrated ingroup and outgroup similarity totals at trial $t$. This model-derived quantity is calibrated by each participant's posterior parameter estimates, incorporating both generalization sensitivity ($\lambda$), projection slope ($\alpha$), and the participant's actual self-rating profile, making it person-specific: two participants with identical mean self-evaluations but different semantic self-concept structure can yield different model MCRs.

Group-level parameter estimates are reported as the arithmetic mean of individual-level posterior medians (grand means) throughout; see Supplementary Materials L for rationale.

Models were fitted using Stan (four MCMC chains; 2,000 post-warmup samples per chain for individual-study models; 1,000 for the pooled three-level model). Convergence was confirmed via $\hat{R} < 1.01$ for all models (Vehtari et al., 2021).

**Table 1. Summary of Computational Model Architectures.**

| Model | *k* | Parameters | Description |
|:------|:---:|:-----------|:------------|
| Bias | 1 | $\gamma$ | Ingroup favoritism baseline. Choices driven entirely by response bias; no role for trait similarity or self-knowledge. |
| Symmetric | 2 | $\alpha$, $\gamma$ | Single projection slope; ingroup assimilation and outgroup repulsion are mathematically yoked ($\alpha_{in} = \alpha_{out}$). |
| Symmetric+$\lambda$ | 3 | $\alpha$, $\gamma$, $\lambda$ | Adds Shepard's generalization sensitivity parameter ($\lambda$); the reach of the self-concept across semantic space decays exponentially with semantic distance, but projection remains symmetric. |
| Asymmetric+$\lambda$ | 4 | $\alpha_{in}$, $\alpha_{out}$, $\gamma$, $\lambda$ | Full architecture. Decouples ingroup assimilation ($\alpha_{in}$) from outgroup repulsion ($\alpha_{out}$), allowing independent estimation of "ingroup love" and "outgroup hate." |

*Note.* $k$ = number of free parameters per subject-level distribution. $\alpha$ / $\alpha_{in}$ / $\alpha_{out}$ = projection slope(s) (0–10); $\gamma$ = response bias (0–1); $\lambda$ = generalization sensitivity (0–5). All models estimated via hierarchical Bayesian inference; subject-level parameters are drawn from a group-level distribution with non-centered parameterization.


```{r}
#| label: fig-03-parameter-space
#| fig-cap: "Parameter space of the Self-Projection Model. Rows vary generalization sensitivity (λ: Low = 0.5, High = 4.0); columns vary projection slope (α: Low = 0.5, High = 3.5). Each panel shows how P(ingroup) changes as a function of a test trait's semantic similarity to the self-concept (x-axis) for a hypothetical participant. Low-λ curves are shallow (self-knowledge generalizes broadly across dissimilar traits); high-λ curves are steep (self-knowledge generalizes narrowly to close semantic neighbors only). Low-α curves cluster near chance (0.5; weak projection); high-α curves diverge strongly from chance (strong projection). The Venn diagrams at right illustrate the qualitative distinction: Low-λ/High-α produces a broad projection footprint spanning the full trait network (large circle overlap), whereas High-λ/Low-α produces a narrow footprint concentrated on the most similar traits (small overlap). Dashed line = chance (0.50)."
#| eval: !expr file.exists(fig_path("fig03_parameter_space_visualization.tiff"))
knitr::include_graphics(fig_path("fig03_parameter_space_visualization.tiff"))
```

```{r}
#| label: fig-04-parameter-illustration
#| fig-cap: "From self-ratings to ingroup classifications: the role of projection slope and generalization sensitivity. (A) Self-rating profile for eight hypothetical training traits forming two semantic clusters (social: Sociable, Warm, Outgoing, Friendly; quiet/neutral: Organized, Accurate, Quiet, Reserved). Dashed line = neutral midpoint (4). (B) Dice similarity heatmap showing the two-cluster semantic structure. (C) Predicted P(ingroup) for a *low-projection* participant (α = 0.5, λ = 1.0): predictions are broadly distributed and modestly above chance, with little contrast between social and quiet traits. (D) Predicted P(ingroup) for a *high-projection* participant (α = 3.0, λ = 3.5): predictions are sharply amplified—highly-rated social traits (trained and novel) approach 85–90% ingroup, while low-rated quiet traits drop to ~35–40%. Both profiles show that the model generalizes to semantically novel traits (light bars) by propagating beliefs through the similarity structure, not just repeating training-phase labels."
#| eval: !expr file.exists(fig_path("fig04_parameter_illustration.tiff"))
knitr::include_graphics(fig_path("fig04_parameter_illustration.tiff"))
```

### Results
Predictors of ingroup classification were estimated using mixed-effects logistic regression with crossed random effects for subjects and traits; random slopes were estimated for focal predictors; in models testing cross-level interactions (a within-person predictor × between-person moderator), a random slope was always included for the level-1 predictor. Subject random intercepts account for baseline differences in individuals' overall tendency to select the ingroup regardless of trait content, and trait random intercepts account for baseline differences in how often a given trait is attributed to the ingroup regardless of who is rating it. This structure ensures that fixed-effect estimates reflect within-person, within-trait associations rather than confounds from person-level response tendencies or trait-level ingroup typicality. For interpretability, we summarize focal effects using estimated marginal means and average marginal effects (Lenth, 2026; Arel-Bundock, 2026), and we report the full fixed-effect coefficients for all reported behavioral models in Supplementary Materials H. Desirability reliability was good, ICC(C, 16) = .682 [.601, .753].

#### Trait Desirability and Ingroup Choice
Trait desirability was not a significant predictor of ingroup classification in Study 1 (AME = .016, 95% CI [−.002, .034], *z* = 1.78, *p* = .075), reflecting only weak ingroup enhancement in a minimal group context.

#### Self-Evaluations and Ingroup Choice
Direct self-evaluations predicted ingroup classification, replicating the traditional self-anchoring effect: a 1-SD increase in self-evaluation increased P(ingroup) by 6.3 percentage points (AME = .063, 95% CI [.040, .086], *z* = 5.28, *p* < .001). This establishes the baseline self-anchoring signal in a context where group categories carry no prior social meaning.

#### Similarity-to-Self and Ingroup Choice
The hypothesized self-anchoring effect was stronger when self-knowledge was measured via relational similarity. A 1-SD increase in *Similarity-to-Self* increased P(ingroup) by 7.0 percentage points (AME = .070, 95% CI [.028, .111], *z* = 3.31, *p* = .001), numerically larger than the 6.3 pp effect of direct self-evaluations. Across the Similarity-to-Self gradient, predicted P(ingroup) ranged from 48% at −1 SD to 56% at the mean to 64% at +1 SD.

#### Similarity-to-Self Generalizes to Novel Traits
This effect extended to novel traits rather than being limited to repeated items. The Similarity-to-Self effect did not differ detectably between trained and novel traits (Trained AME = .069 (*z* = 3.29, *p* = .001), Novel AME = .073 (*z* = 3.43, *p* < .001); difference = .004 pp, 95% CI [−.013, .020]), arguing against a simple repetition-based account. A TOST equivalence test on the Similarity-to-Self × Novel interaction coefficient also supported practical equivalence within a small-effect interval of $|b| < 0.10$ (interaction $b$ = 0.022, 90% CI [−0.05, 0.10], *p* = .046). Exploratory Similarity-to-Self moderation models were uniformly null in Study 1: self-esteem, social identification, perceived prototypicality, and independent self-construal did not significantly moderate the Similarity-to-Self slope (all *p*s ≥ .425; Supplementary Materials H).
```{r}
#| label: fig-07-marginal-effects
#| fig-cap: "Predictors of ingroup classification: Desirability, self-evaluations, and similarity-to-self. Plotted using average marginal predictions (marginaleffects package) ± 95% CI. Top row is Study 1 (Minimal Groups). Middle row is Study 2 (University Groups). Bottom row is Study 3 (Racial Groups). Left column: desirability; center: self-evaluations; right: similarity-to-self. X-axis = Z-scored predictor (−1 SD, Mean, +1 SD); Y-axis = predicted P(ingroup classification). Colors denote outgroup conditions within each study. Dashed line = chance (0.50)."
#| fig-width: 10
#| fig-height: 10
#| eval: !expr file.exists(fig_path("fig07_marginal_effects.tiff"))
knitr::include_graphics(fig_path("fig07_marginal_effects.tiff"))
```


#### Trait Segregation
*Trait segregation* (network nominal homophily) quantifies how much a participant's ingroup versus outgroup classifications cluster along the semantic similarity network (*M* = .09, *SD* = .08; range [−.04, .26]). This index was developed and validated as an exploratory network-based metric; full results across all three studies are reported in Supplementary Materials K.

#### Computational Model Comparison
We compared four cognitive architectures of social inference: Bias, Symmetric, Symmetric+$\lambda$, and Asymmetric+$\lambda$ (see Table 1 for architecture summary). Model selection used leave-one-out cross-validation (LOO-CV; Vehtari et al., 2017), with models ranked by expected log predictive density (ELPD); $\Delta$ELPD is reported relative to the best-fitting model. Log-likelihood was stored at the trial level rather than the subject level, enabling observation-level LOO and reliable Pareto $k$ diagnostics; greater than 95% of trials had $k < 0.7$ across models, confirming the validity of the PSIS approximation (Vehtari et al., 2017). To complement the group-level comparison, we computed each participant's *per-subject LOO ELPD difference* (per-subject $\Delta$ELPD = $\text{ELPD}_{\text{asymmetric}} - \text{ELPD}_{\text{symmetric}}$), summing pointwise ELPD values across that participant's valid trials. A positive per-subject $\Delta$ELPD indicates the asymmetric architecture better predicts that individual's choices; a negative value indicates the symmetric architecture is favored. This person-specific index was examined against individual-difference measures to test whether particular psychological characteristics predict which model best accounts for a given participant's behavior.

**Table 2. LOO Model Comparison — Study 1 (Minimal Groups, *N* = 61).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Symmetric+$\lambda$ | −5653.6 | 29.6 | 0.0 | — |
| Asymmetric+$\lambda$ | −5661.9 | 29.2 | −8.31 | 2.51 |
| Symmetric | −5766.9 | 26.2 | −113.3 | 13.0 |
| Bias | −5842.2 | 24.8 | −188.7 | 16.2 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy.

The Symmetric+$\lambda$ model provided the best predictive fit (ELPD = −5653.6, SE = 29.6), meaningfully outperforming the Symmetric model ($\Delta$ELPD = −113.3, SE = 13.0; $|\Delta\text{ELPD}|/\Delta\text{SE} = 8.7$) and the Bias model ($\Delta$ELPD = −188.7, SE = 16.2). The Asymmetric+$\lambda$ model performed clearly worse than the winner ($\Delta$ELPD = −8.31, SE = 2.51; $|\Delta\text{ELPD}|/\Delta\text{SE} = 3.3$). Together these results indicate that in minimal groups, decoupling ingroup projection ($\alpha_{in}$) from outgroup discrimination ($\alpha_{out}$) reduces predictive accuracy: a symmetric projection slope captures the data better than an asymmetric one. Group-level parameter means (averages of individual posterior medians) for the Symmetric+$\lambda$ model were: projection slope $\alpha = 0.63$ (group median = 0.34, 95% CI $[0.20, 0.54]$), generalization sensitivity $\lambda = 3.72$ (95% CI $[3.30, 4.23]$), and ingroup bias $\gamma = 0.46$ (95% CI $[0.41, 0.49]$). The Asymmetric+$\lambda$ model estimated $\alpha_{in} = 0.21$ (95% CI $[0.07, 0.45]$) and $\alpha_{out} = 0.39$ (95% CI $[0.20, 0.68]$); the wide, overlapping credible intervals reflect the model's inability to reliably dissociate ingroup and outgroup projection slopes under minimal-group conditions.

```{r}
#| label: fig-elpd-s1
#| fig-cap: "Per-subject LOO-ELPD by model, Study 1 (Minimal Groups, *N* = 61). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. Symmetric+λ outperforms Asymmetric+λ (group-level ΔELPD = −8.31, SE = 2.51). *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s1.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s1.tiff"))
```


#### Parameter Estimates and Individual Differences
The following individual-difference analyses are exploratory. We examined Pearson correlations between each model parameter ($\alpha$, $\gamma$, $\lambda$) and the model-derived MCR against nine individual-difference scales (FDR correction applied separately for mechanism-personality tests [$k = 36$: $\alpha$, $\gamma$, $\lambda$, MCR × 9 scales] and for ΔELPD-personality tests [$k = 9$]). Two associations survived FDR correction. The model-derived MCR, a person-specific index of ingroup-relative-to-outgroup similarity weighting, correlated negatively with dialectical self-views ($r(59) = -.41$, $p_{\text{raw}} = .001$, $p_{\text{FDR}} = .032$): participants with less differentiated, more holistic self-views showed stronger ingroup-favoring semantic contrast. Generalization sensitivity $\lambda$ also correlated negatively with dialectical self-views ($r(59) = -.39$, $p_{\text{raw}} = .002$, $p_{\text{FDR}} = .038$), suggesting that narrower semantic generalization co-occurs with a less differentiated self-concept. The MCR additionally showed a nominal association with self-concept clarity ($r(59) = .36$, $p_{\text{raw}} = .005$, $p_{\text{FDR}} = .060$). Structural parameters $\alpha$ and $\gamma$ showed no FDR-significant associations. The two FDR-surviving correlations converge on a coherent pattern: self-anchoring that produces strong ingroup-relative discrimination reflects a particular relationship to the self-concept, one that integrates traits more holistically rather than dialectically. The ΔELPD-personality tests were all null (all $p_{\text{FDR}} \geq .394$).

We also computed the per-subject $\Delta$ELPD as an individual-level index of which model architecture better predicted each participant's choices ($\Delta$ELPD = ELPD$_{\text{asymmetric}}$ − ELPD$_{\text{symmetric}}$; positive values indicate the asymmetric model is better supported for that individual, negative values indicate the symmetric model is favored). Nineteen of 61 participants showed positive $\Delta$ELPD (i.e., the asymmetric model better predicted their choices), consistent with the group-level preference for the symmetric architecture (total $\Delta$ELPD = −8.31). $\Delta$ELPD was not reliably associated with any individual-difference scale (all *r*s ≤ .22, all $p_{\text{FDR}} \geq .394$ with FDR correction applied separately over the 9 ΔELPD-personality tests). In the minimal-group context, which model better fits an individual's choices does not meaningfully vary with their personality profile.

### Discussion
Similarity-to-self predicted ingroup classification more strongly than one-to-one trait matching, confirming that self-anchoring is a structured inferential process rather than simple attribute replication. The effect held across both novel and repeated traits, ruling out repetition as an explanation. Model comparison revealed a clear preference for the Symmetric+$\lambda$ architecture over the fully asymmetric model, indicating that in minimal groups, ingroup assimilation and outgroup discrimination are not architecturally dissociable — both are captured by a single projection slope. The model-derived MCR and generalization sensitivity $\lambda$ correlated negatively with dialectical self-views, linking stronger ingroup-favoring discrimination to a more holistic, less differentiated self-concept.

## STUDY 2: SELF-ANCHORING BASED ON RELATIVE STATUS OF UNIVERSITY GROUPS
Study 2 examined how social status modulates self-anchoring in real-world social categories. Study 2 was pre-registered at OSF (https://osf.io/q2vx7). We pre-registered the primary Similarity-to-Self effect and its generalization to novel traits; a directional prediction that lower-status outgroup comparisons would produce stronger ingroup projection relative to negation (this prediction was disconfirmed — the high-status condition produced the strongest projection); that trait segregation would correlate positively with need to belong and dialectical self-views and negatively with self-esteem and independent self-construal; that self-anchoring strength would associate with social identification, perceived prototypicality, and status perceptions; and that generalization to novel traits would not differ from generalization to trained traits. Computational modeling analyses and MCR-based individual differences are exploratory. Minimal groups in Study 1 could not dissociate ingroup projection from outgroup discrimination—a symmetric architecture sufficed. Real social categories introduce meaningful intergroup history, perceived status differentials, and motivated distinctiveness concerns that should activate the two processes differentially. Under conditions of positive regard for the outgroup (e.g., a higher-status rival university), the prior motivation to classify traits as ingroup-characteristic (γ) may attenuate even while the projection mechanism (α) remains intact — or vice versa for derogated outgroups. Study 2 therefore tests both whether the asymmetric architecture is detectable under real intergroup conditions and whether status-modulated motivation manifests as changes in the projection slope or in the baseline ingroup preference.

Beyond the projection slope ($\alpha$), SCT's comparative fit principle suggests that category boundaries should matter most when intergroup differences are psychologically sharpened relative to within-group variation (Turner et al., 1987). $\lambda$ is not itself a direct measure of comparative fit, but if it reflects how narrowly self-knowledge generalizes through semantic space, it could show context-sensitive contraction or broadening under sharper versus weaker intergroup contrasts. We therefore examined condition differences in $\lambda$ as a non-preregistered exploratory analysis rather than as a formal test of comparative fit. Given the exploratory status and the expectation of small effects, these analyses should be interpreted with appropriate caution.

### Methods
From an initial pool of 283 participants, 102 were excluded (final *N* = 181). Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 4), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 47). Participants were native English-speaking university students (68.3% Cisgender Female, 30.4% Cisgender Male, 1.2% Other; *M*<sub>Age</sub> = 19.71, *SD*<sub>Age</sub> = 2.02, Range<sub>Age</sub> = [18, 36]). Ethnic composition included 1.2% White, 23.0% Mixed, 44.1% Asian, 22.4% Hispanic, 0.0% Native-American, 3.1% Black, and 6.2% Middle Eastern. Participants were randomly assigned to one of three outgroup contrast conditions: Negation ("Not Ingroup University"), Higher Status University, or Lower Status University. A *simr* power analysis indicated that our final sample (*N* = 181) meets the 80% power threshold for detecting a cross-level interaction between similarity-to-self and condition at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 181 can detect correlations of *r* ≥ .20 at 80% power (α = .05, two-tailed).

### Results
#### Manipulation Checks
Manipulation checks confirmed perceived status differences. All participants rated the status and warmth of all three universities; pairwise contrasts used linear mixed models with subject random intercepts. Compared to the ingroup university (*M* = 6.24, *SD* = 1.36), the high-status university was rated significantly higher (*M* = 8.63, *SD* = 1.46; *t*(361.3) = 18.15, *p* < .001) and the low-status university significantly lower (*M* = 4.71, *SD* = 1.40; *t*(361.8) = −11.67, *p* < .001). Participants felt most warmly toward the ingroup (*M* = .783, *SD* = .156), followed by the high-status (*M* = .680, *SD* = .226; *t*(318.8) = −4.79, *p* < .001) and low-status university (*M* = .466, *SD* = .227; *t*(336.1) = −14.26, *p* < .001; warmth on 0–1 scale).

#### Trait Desirability and Ingroup Choice
Trait desirability predicted ingroup classification in Study 2 (AME = .047, 95% CI [.034, .061], *z* = 6.92, *p* < .001), whereas the Study 1 effect did not reach significance (AME = .016, *p* = .075). This difference is descriptive — no formal cross-study test was conducted — and should be interpreted cautiously.

#### Self-Evaluations and Ingroup Choice
Direct self-evaluations predicted ingroup classification across all three conditions, replicating the core self-anchoring effect at the level of individual trait ratings (AME = .048, 95% CI [.036, .061], *z* = 7.55, *p* < .001). The effect was consistent across university outgroup contexts, indicating that trait-level self-projection is not disrupted by status-differentiated social categories.

#### Similarity-to-Self and Ingroup Choice
Similarity-to-Self remained the focal predictor. Averaging across all three outgroup conditions, a 1-SD increase in Similarity-to-Self increased P(ingroup choice) by 6.3 pp (AME = .063, 95% CI [.036, .090], *z* = 4.58, *p* < .001); condition-specific AMEs are reported below. Again, Similarity-to-Self was a stronger predictor than self-evaluations, consistent with people leveraging relational similarity to make inferences about their ingroup.

#### Outgroup Condition Differences in Similarity-to-Self Effects
The size of the Similarity-to-Self effect varied across outgroup contexts. The effect was significant in the negation condition (AME = .047, 95% CI [.013, .081], *z* = 2.68, *p* = .007) and strongest in the high-status condition (AME = .100, 95% CI [.047, .153], *z* = 3.68, *p* < .001), but non-significant in the low-status condition (AME = .044, 95% CI [−.006, .094], *z* = 1.74, *p* = .082). Across the Similarity-to-Self gradient in the negation condition, predicted P(ingroup) ranged from 61% at −1 SD to 68% at the mean to 73% at +1 SD; in the high-status condition, the range was considerably wider, from 40% to 51% to 60%.

#### Similarity-to-Self Generalizes to Novel Traits
In an overall model without condition terms, the Similarity-to-Self × Novel interaction was not significant ($b$ = −0.039, 90% CI [−0.09, 0.01], *p* = .165), and a TOST equivalence test supported practical equivalence within $|b| < 0.10$ (*p* = .016). Thus, across Study 2 as a whole, the Similarity-to-Self slope did not differ meaningfully between trained and novel traits. A three-way model (Similarity-to-Self × Novel × Outgroup) nevertheless showed that the size of the underlying Similarity-to-Self effect varied by outgroup context. In the negation condition, effects were significant for both trained (AME = .049, 95% CI [.014, .083], *z* = 2.76, *p* = .006) and novel traits (AME = .043, 95% CI [.008, .077], *z* = 2.43, *p* = .015), suggesting self-anchoring generalizes to novel traits when contrasting against a neutral outgroup. The high-status condition showed the strongest generalization, with large significant effects for trained (AME = .103, 95% CI [.049, .158], *z* = 3.75, *p* < .001) and novel traits (AME = .097, 95% CI [.044, .151], *z* = 3.55, *p* < .001). The low-status condition showed attenuation, with non-significant trained effects (AME = .047, 95% CI [−.003, .098], *z* = 1.85, *p* = .064) and non-significant novel-trait effects (AME = .040, 95% CI [−.012, .091], *z* = 1.50, *p* = .133), suggesting generalization may be selectively suppressed when the outgroup is perceived as lower status. Exploratory Similarity-to-Self moderation models were uniformly null in Study 2: neither self-esteem, social identification, perceived prototypicality, nor independent self-construal moderated the Similarity-to-Self slope in the negation condition, and no condition-specific three-way interactions were significant (all *p*s ≥ .149; Supplementary Materials H).

#### Trait Segregation
Trait segregation (network nominal homophily) varied across conditions; full results are reported in Supplementary Materials K.

#### Computational Model Comparison

Computational modeling methods, reporting conventions, and parameter-recovery analyses follow Study 1 exactly. The same four model architectures were estimated using identical Stan code, priors, and convergence criteria; group-level estimates are reported as grand means of individual posterior medians throughout.

**Table 3. LOO Model Comparison — Study 2 (University Groups, *N* = 181).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −15,898.60 | 63.83 | 0.0 | — |
| Asym+$\lambda$ | −15,910.67 | 63.50 | −12.07 | 3.98 |
| Symmetric | −16,125.40 | 60.61 | −226.80 | 20.16 |
| Bias | −16,301.67 | 59.53 | −403.07 | 25.73 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy.

The self-projection models (Sym+$\lambda$, Asym+$\lambda$) substantially outperformed the Symmetric and Bias architectures across all conditions (see Table 3). As in Study 1, Sym+$\lambda$ was preferred over Asym+$\lambda$, with the advantage clearly exceeding the conventional two-SE threshold (3.0 SEs; $\Delta$ELPD = −12.07, SE = 3.98). Per-condition model comparisons reveal a theoretically interpretable pattern ($\Delta$ELPD = Asym $-$ Sym; positive values favor Asym+$\lambda$): in the Negation condition (abstract outgroup "Not UCR"), Asym+$\lambda$ was numerically preferred ($\Delta$ELPD = +1.15 total, per-subject mean = +0.018, *t*(62) = 0.42, *p* = .678); in the High-Status condition, Sym+$\lambda$ was clearly preferred ($\Delta$ELPD = −10.3 total, per-subject mean = −0.175, *t*(58) = −2.11, *p* = .039); and in the Low-Status condition, the advantage was small and non-significant ($\Delta$ELPD = −2.92 total, per-subject mean = −0.050, *t*(58) = −1.18, *p* = .242). The Sym+$\lambda$ advantage was significantly greater in the High-Status condition than the Negation condition ($|\Delta\Delta\text{ELPD}|$ = 0.193, *t*(88) = 2.06, *p* = .042), suggesting that when the outgroup is concrete and positively-regarded, symmetric processing of in- and outgroup information is more strongly supported.

#### Parameter Differences Across Conditions
The clearest parameter shift across conditions was in ingroup classification bias ($\gamma$), *F*(2, 178) = 27.77, *p* < .001, *R*² = .238. Participants in the High-Status condition showed dramatically reduced ingroup bias ($M$ = 0.39, *SD* = 0.13) relative to both Negation ($M$ = 0.56, *SD* = 0.17; $\beta$ = −0.178, *t*(178) = −6.44, *p* < .001) and Low-Status ($M$ = 0.57, *SD* = 0.15; $\beta$ = +0.005, *t*(178) = 0.17, *p* = .869). Participants may select positive traits as characteristics of a high status outgroup more frequently. By contrast, overall condition differences in projection slope ($\alpha$) were modest, *F*(2, 178) = 3.37, *p* = .036, *R*² = .037, and pairwise contrasts did not resolve reliably (High-Status: $\beta$ = +0.239, *t*(178) = 1.58, *p* = .116; Low-Status: $\beta$ = −0.158, *t*(178) = −1.04, *p* = .299). The Metacontrast Ratio showed no overall condition effect, *F*(2, 178) = 2.36, *p* = .098, although the Low-Status condition was somewhat lower than Negation ($M$ = 1.71 vs. 2.38; $\beta$ = −0.665, *t*(178) = −2.06, *p* = .041); the High-Status contrast was also non-significant ($\beta$ = −0.519, *t*(178) = −1.61, *p* = .110).

As a non-preregistered exploratory analysis, we tested whether $\lambda$ differed across outgroup contrast conditions using a linear model ($\lambda \sim \text{condition}$), *F*(2, 178) = 5.04, *p* = .007, *R*² = .054. Relative to Negation ($M_{\text{Neg}}$ = 3.259, *SE* = 0.022), both the Low-Status condition ($M_{\text{Low}}$ = 3.249, *SE* = 0.013; $\beta$ = −0.010, *t*(178) = −3.08, *p* = .002) and the High-Status condition ($M_{\text{High}}$ = 3.252, *SE* = 0.018; $\beta$ = −0.007, *t*(178) = −2.17, *p* = .032) showed slightly narrower generalization. Because $\lambda$ is only an indirect proxy for comparative fit, we interpret these shifts cautiously as small context-sensitive contractions in semantic generalization sensitivity rather than as a direct test of SCT's comparative-fit mechanism.

#### Parameter Estimates and Individual Differences
As in Study 1, individual-difference analyses are exploratory; FDR correction was applied separately for mechanism-personality tests ($k$ = 36) and ΔELPD-personality tests ($k$ = 9). Individual-level MCR correlated with self-esteem (*r*(179) = .30, *p*<sub>FDR</sub> = .004), self-concept clarity (*r*(179) = .26, *p*<sub>FDR</sub> = .007), and need for cognition (*r*(179) = .21, *p*<sub>FDR</sub> = .049); generalization sensitivity ($\lambda$) independently correlated with social identification (*r*(179) = .23, *p*<sub>FDR</sub> = .024). The ingroup bias parameter $\gamma$ showed no FDR-significant personality associations (all *p*<sub>FDR</sub> > .50). At the individual level, $\lambda$ did not correlate significantly with outgroup warmth in either the High-Status condition (*r*(53) = .193, *p* = .157) or the Low-Status condition (*r*(44) = .066, *p* = .664); the overall correlation was non-significant (*r*(99) = .093, *p* = .353).

If γ operationalizes the positive distinctiveness motive at the individual level, participants who view the higher-status outgroup more warmly should show attenuated ingroup bias. We tested this with Spearman's ρ between individual-level γ and outgroup warmth within each condition. The association was positive and directionally non-significant in the High-Status condition (ρ = .233, *n* = 55, *p* = .088) and null in the Low-Status condition (ρ = .208, *n* = 46, *p* = .166). The condition-level γ attenuation (High-Status *M* = 0.39 vs. Negation *M* = 0.56) is therefore a uniform structural shift, present for everyone in the High-Status condition, rather than a within-condition effect driven by individual variation in outgroup attitudes.

```{r}
#| label: fig-condition-effects-s2
#| fig-cap: "Study 2 parameter distributions by outgroup condition. Left: projection slope (α) varies modestly across conditions, with no reliable pairwise contrasts. Center: ingroup bias (γ) drops dramatically in the High-Status condition (*M* = 0.39) relative to Negation (*M* = 0.56) and Low-Status (*M* = 0.57). Right: generalization sensitivity (λ) is slightly lower in both High-Status and Low-Status conditions than in Negation. Individual participant values shown with jitter; boxplots show median and IQR."
#| fig-width: 12
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_condition_effects_s2.tiff"))
knitr::include_graphics(fig_path("fig_condition_effects_s2.tiff"))
```

```{r}
#| label: fig-condition-effects-s2-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_condition_effects_s2.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-elpd-s2
#| fig-cap: "Per-subject LOO-ELPD by model, Study 2 (University Groups, *N* = 181). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by outgroup contrast condition (Negation, High-Status, Low-Status). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 10
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s2.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s2.tiff"))
```

```{r}
#| label: fig-elpd-s2-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_s2.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 2 — re-run `Figures/make_figures.R` to generate.]*")
```

### Discussion
Study 2 replicates similarity-based generalization in real-world social categories and reveals the locus of contextual modulation: not primarily the projection slope ($\alpha$) but a sharp reduction in ingroup classification bias ($\gamma$) when contrasting against the higher-status outgroup. The projection mechanism remains effectively intact; what changes is the prior disposition to choose the ingroup. The per-condition model comparisons reinforce this: the asymmetric architecture was clearly disfavored in the High-Status condition, consistent with symmetric in/outgroup processing when the outgroup is positively-regarded. At the low-status end, similarity-to-self was attenuated and generalization to novel traits was non-significant — consistent with the meta-contrast principle: when an outgroup is lower in status, categorical boundaries may be rendered salient through status cues alone, reducing the need for self-similarity as a discriminating signal. The small downward shifts in $\lambda$ for both status-manipulated conditions are consistent with modest contraction of semantic generalization sensitivity, but because $\lambda$ is only an indirect proxy for comparative fit, this evidence should be treated as suggestive rather than definitive. Together, these results suggest self-anchoring is most active when the categorization problem is motivationally engaged but not resolved by status cues alone. MCR correlated reliably with self-esteem, self-concept clarity, and need for cognition, confirming that the semantic contrast ratio captures individual differences in self-concept organization.

The pre-registered directional prediction — that low-status outgroup comparisons would produce stronger ingroup projection than negation — was disconfirmed; the high-status condition produced the strongest similarity-to-self effect. The γ–α dissociation also emerged post-hoc: a priori, the projection slope was the theoretically expected lever of status-based modulation. The finding that α showed no significant condition-specific contrasts while γ shifted dramatically illuminates a distinction implicit in social identity theory: the inferential machinery of self-anchoring is effectively stable; the motivational prior that orients it is context-sensitive. This distinction between process stability and motivational variability is made empirically tractable by the present formal architecture. The low-status similarity-to-self effect did not reach significance within Study 2; the pooled behavioral analysis revisits this estimate with greater power across the full sample.

Notably, the magnitude of γ in the High-Status condition is consistent with the interpretation that a positively-regarded, high-status outgroup reduced ingroup preference below the minimal-group baseline, suggesting that the preference generated by arbitrary group membership can be attenuated by a concrete, high-status comparison target.

## STUDY 3: SELF-ANCHORING UNDER MAJORITY AND MINORITY RACIAL GROUP CONTRASTS
Study 2's γ–α dissociation — stable projection machinery, context-sensitive motivational prior — emerged under conditions specific to university status comparisons, where groups have explicit status histories and the outgroup is a concrete institutional rival. Whether this architecture generalizes to racial identities, which carry different forms of intergroup meaning (power asymmetry, shared subordinate status, entrenched categorical boundaries), is an open question that Study 3 addresses.

Study 3 applied the self-anchoring framework to racial identities (Asian and Latino participants), examining how majority or minority outgroup contrasts exert differential effects on generalization. Study 3 was not formally pre-registered. It was designed as a conceptual replication and boundary-condition test, following the same confirmatory predictions as Studies 1 and 2: that Similarity-to-Self predicts ingroup classification and generalizes to novel traits, that intergroup context modulates the parameters of that process, and that MCR correlates with individual differences in group identification. We expected these core features — the basic self-anchoring effect, semantic generalization, and the MCR–personality link — to replicate in the racial context. We did not expect Study 2's specific directional prediction (that low-status contrasts produce stronger projection than negation) to extend to race, as that prediction was disconfirmed even within Study 2, and the status dynamics of racial categories differ structurally from university rank. We made no directional predictions regarding the specific effect of Minority versus Majority outgroup contrast on model parameters: SCT offers competing accounts (shared subordinate status reducing distinctiveness motivation via common fate; vs. majority salience heightening the meta-contrast ratio and elevating γ). Analyses labeled "exploratory" go beyond this confirmatory scope.

### Methods
From an initial pool of 313 participants, 48 were excluded (final *N* = 265). Exclusions were applied for: self-reported low task seriousness (*n* = 2), self-reported unusable data (*n* = 9), and careless responding — defined as > 80% identical self-evaluations, > 95% identical group classifications, or > 40% missing responses in either phase (*n* = 37). Participants were native English-speaking university students (59.14% Cisgender Female, 40.86% Cisgender Male; *M*<sub>Age</sub> = 19.01, *SD*<sub>Age</sub> = 1.71, Range<sub>Age</sub> = [17, 33]), and were 50.97% Hispanic/Latino and 49.03% Asian. Participants were assigned to either a Minority (Asian vs. Latino) or Majority (Ingroup vs. White) comparison condition. Study 3 uses two conditions rather than Study 2's three, requiring a smaller sample for equivalent power; *N* = 265 comfortably exceeds the Study 2 power threshold for detecting a cross-level interaction at a small effect size (log-odds β = .35; Green & MacLeod, 2016). Power was prioritized for multilevel fixed effects; correlational analyses may be underpowered. For completeness, a sensitivity analysis indicates *N* = 265 can detect correlations of *r* ≥ .17 at 80% power (α = .05, two-tailed).

### Results
#### Manipulation Checks
Manipulation checks confirmed that status and warmth perceptions differed across racial groups as expected. All participants rated the status and warmth of White, Asian, and Latino groups; pairwise contrasts used linear mixed models with subject random intercepts. White groups were perceived as significantly higher status (*M* = 8.42, *SD* = 1.63) than Asian (*M* = 6.73, *SD* = 1.51; *t*(518) = −13.29, *p* < .001) or Latino (*M* = 5.02, *SD* = 1.59; *t*(518) = −26.77, *p* < .001) groups; Asian groups were also rated higher in status than Latino groups (*t*(259) = −15.57, *p* < .001). Warmth ratings (0–1 scale) were higher for Latino (*M* = .79, *SD* = .19) and Asian (*M* = .77, *SD* = .19) groups than for White groups (*M* = .54, *SD* = .23; *t*(481) = −14.35, *p* < .001 for both comparisons vs. Latino); Latino and Asian warmth did not significantly differ (*p* = .245).

#### Trait Desirability and Ingroup Choice
Unlike Study 1's minimal groups, where desirability did not reach significance, trait desirability reliably predicted ingroup classification in the racial context (AME = .031, 95% CI [.016, .047], *z* = 4.05, *p* < .001), suggesting that established racial categories carry normative ingroup-positivity expectations that minimal groups lack.

#### Self-Evaluations and Ingroup Choice
Direct self-evaluations also predicted ingroup classification, confirming that the basic self-anchoring effect replicates across racial identities (AME = .039, 95% CI [.028, .050], *z* = 6.84, *p* < .001).

#### Similarity-to-Self and Ingroup Choice
Similarity-to-Self did not predict ingroup classification overall (AME = .012, 95% CI [−.011, .036], *z* = 1.02, *p* = .307). The lack of a significant main effect of Similarity-to-Self was surprising, but may be qualified by condition-dependent effects.

#### Condition Differences in Similarity-to-Self Effects
That null overall effect concealed clear condition-specific variation. The Similarity-to-Self effect was absent in the minority-outgroup condition (AME = −.008, 95% CI [−.042, .026], *z* = −0.45, *p* = .653) but significant in the majority-outgroup condition (AME = .034, 95% CI [.002, .066], *z* = 2.08, *p* = .037). In the majority condition, predicted P(ingroup) ranged from 57% at −1 SD to 61% at the mean to 65% at +1 SD; in the minority condition the gradient was essentially flat (56.7%, 56.5%, 55.9%).

#### Similarity-to-Self Generalizes to Novel Traits
In an overall model without condition terms, the Similarity-to-Self × Novel interaction was not significant ($b$ = −0.016, 90% CI [−0.05, 0.02], *p* = .480), and a TOST equivalence test supported practical equivalence within $|b| < 0.10$ (*p* < .001). Thus, across Study 3 as a whole, the Similarity-to-Self slope did not differ meaningfully between trained and novel traits. A three-way model (Similarity-to-Self × Novel × Condition) nevertheless examined whether the majority-condition effect generalized to novel traits. In the majority condition, the trained-trait effect remained significant (AME = .040, 95% CI [.007, .072], *z* = 2.38, *p* = .017), while the novel-trait effect was positive but non-significant (AME = .026, 95% CI [−.007, .058], *z* = 1.53, *p* = .125). In the minority condition, neither trained (AME = −.009, 95% CI [−.043, .025], *z* = −0.52, *p* = .603) nor novel-trait (AME = −.006, 95% CI [−.041, .028], *z* = −0.35, *p* = .728) effects were significant. These patterns suggest that in the racial context, similarity-based inference is present for familiar traits when contrasting against the majority, but does not reliably propagate to semantically novel traits. Exploratory Similarity-to-Self moderation models were also uniformly null in Study 3: neither self-esteem, social identification, perceived prototypicality, nor independent self-construal moderated the Similarity-to-Self slope overall or specifically in the majority condition (all *p*s ≥ .309; Supplementary Materials H).

#### Trait Segregation
Trait segregation (network nominal homophily) differed by condition; full results are reported in Supplementary Materials K.


#### Computational Model Comparison

Computational modeling methods and reporting conventions follow Study 1 exactly.

**Table 4. LOO Model Comparison — Study 3 (Racial Groups, *N* = 265).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −24,555.67 | 59.79 | 0.0 | — |
| Asym+$\lambda$ | −24,587.24 | 59.32 | −31.56 | 4.92 |
| Symmetric | −24,809.01 | 55.15 | −253.34 | 20.51 |
| Bias | −25,044.37 | 53.57 | −488.70 | 26.66 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy.

As in Studies 1 and 2, the Sym+$\lambda$ model provided the best fit ($\Delta$ELPD = 0; reference). The Asym+$\lambda$ model was clearly distinguishable (ΔELPD = −31.56, SE = 4.92; ratio = 6.4); this separation was larger than in Studies 1 and 2 (3.3 and 3.0 SEs, respectively), reinforcing the pattern that symmetric projection is not merely preferable but robustly adequate across all three intergroup contexts. Models with a generalization sensitivity parameter substantially outperformed architectures without one (Symmetric: ΔELPD = −253.34, SE = 20.51; Bias: ΔELPD = −488.70, SE = 26.66). Per-subject ELPD showed that Sym+$\lambda$ was clearly preferred over Asym+$\lambda$ in both the Minority condition (mean ΔELPD = −0.136, *t*(137) = −3.23, *p* = .002) and the Majority condition (mean ΔELPD = −0.100, *t*(126) = −2.34, *p* = .021), with no differential advantage between conditions (*p* = .549). Symmetric projection was unambiguously sufficient across both racial contrast conditions.

#### Parameter Differences Across Conditions
Group-level parameter means (averages of individual posterior medians) from the winning Sym+$\lambda$ model were: projection slope $\alpha$ = 0.679 (group median = 0.189, 95% CI [0.117, 0.283]), ingroup bias $\gamma$ = 0.504 [0.483, 0.525], and generalization sensitivity $\lambda$ = 2.997 [2.799, 3.248]. Projection slope was similar across conditions, *F*(1, 263) = 0.39, *p* = .532 (Minority *M* = 0.642, Majority *M* = 0.720; $\beta$ = +0.077, *t*(263) = 0.63, *p* = .532). Ingroup bias was higher in the Majority condition than in the Minority condition, *F*(1, 263) = 5.26, *p* = .023, *R*² = .020 (Minority *M* = 0.486, Majority *M* = 0.524; $\beta$ = +0.039, *t*(263) = 2.29, *p* = .023), indicating that contrasting against the racial majority produced stronger ingroup classification bias. Generalization sensitivity was effectively identical across conditions, *F*(1, 263) = 0.39, *p* = .532 (Minority *M* = 2.997, Majority *M* = 2.998; $\beta$ = +0.001, *t*(263) = 0.63, *p* = .532). The semantic contrast ratio also did not differ by condition, *F*(1, 263) < 0.01, *p* = .977 (Minority *M* = 1.713, Majority *M* = 1.707; $\beta$ = −0.006, *t*(263) = −0.03, *p* = .977).

As in Study 2, the condition comparison for $\lambda$ was not preregistered and should be treated as exploratory. Unlike Study 2, where status conditions showed small but significant contractions in $\lambda$, generalization breadth was not modulated by racial outgroup contrast type.

#### Parameter Estimates and Individual Differences
FDR-corrected correlations between model parameters and individual differences revealed no significant associations after correction in Study 3 (all *p*~FDR~ ≥ .090). The strongest nominally significant associations were ingroup bias $\gamma$ with self-esteem (*r*(259) = −.19, *p*~FDR~ = .090), MCR with dialectical self-views (*r*(258) = −.16, *p*~FDR~ = .095), and MCR with self-concept clarity (*r*(258) = .15, *p*~FDR~ = .119). Unlike Studies 1 and 2, where MCR consistently predicted self-concept measures, the MCR–personality structure did not survive FDR correction in the racial context (though point estimates were directionally consistent; the null likely reflects attenuation by the larger FDR family in a context with reduced individual variation in self-referential inference).

At the individual level, $\lambda$ was not associated with ingroup-relative preference in either condition (Overall *r*(232) = .106, *p* = .107; Minority *r*(120) = .073, *p* = .427; Majority *r*(110) = .154, *p* = .105; interaction *p* = .574). The condition × ingroup-over-majority preference interaction for $\gamma$ did not reach significance (Fisher *z* = −1.96, *p* = .050). Descriptively, in the Majority condition, stronger preference for own minority over White was positively associated with ingroup classification bias (*r*(108) = .186, *p* = .051), while in the Minority condition this association was absent (*r*(117) = −.075, *p* = .421).

The condition effect on $\gamma$ was not significantly moderated by participant race (*p* = .133). Asian participants showed directionally similar ingroup bias across conditions (Minority *M* = 0.555, Majority *M* = 0.556), while Latino participants showed somewhat lower bias in the Minority condition (Minority *M* = 0.434, Majority *M* = 0.484), but this cross-over pattern did not reach significance in the final model. Stratifying the MCR–personality correlations by race revealed that MCR was nominally associated with dialectical self-views (*r*(130) = −.235, *p* = .007), self-concept clarity (*r*(129) = .203, *p* = .020), and independent self-construal (*r*(129) = .207, *p* = .018) in Latino participants; no comparable associations emerged in Asian participants. These are uncorrected *p*-values and should be interpreted descriptively given the individual differences null at the pooled level. A full breakdown of condition × race interactions for all parameters is provided in Supplementary Materials C.

```{r}
#| label: fig-elpd-s3
#| fig-cap: "Per-subject LOO-ELPD by model, Study 3 (Racial Groups, *N* = 265). Each line represents one participant's summed LOO-ELPD trajectory across computational architectures, faceted by racial outgroup contrast condition (Racial Minority Outgroup, Racial Majority Outgroup). Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation. Per-subject values are the sum of pointwise log predictive densities for each participant's trials."
#| fig-width: 8.5
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_s3.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_s3.tiff"))
```

```{r}
#| label: fig-elpd-s3-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_s3.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Study 3 — re-run `Figures/make_figures.R` to generate.]*")
```

```{r}
#| label: fig-condition-effects-s3
#| fig-cap: "Study 3 parameter distributions by racial outgroup contrast condition. Left: projection slope (α) is similar in Minority and Majority conditions. Center: ingroup bias (γ) is higher in the Majority condition (*M* = 0.524) than in the Minority condition (*M* = 0.486). Right: generalization sensitivity (λ) is effectively identical across conditions. Individual participant values shown with jitter; boxplots show median and IQR."
#| fig-width: 12
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_condition_effects_s3.tiff"))
knitr::include_graphics(fig_path("fig_condition_effects_s3.tiff"))
```

```{r}
#| label: fig-condition-effects-s3-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_condition_effects_s3.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

### Discussion
Study 3 extends self-anchoring to the racial context. Similarity-to-self predicted ingroup classification in the majority-outgroup condition but not in the minority-outgroup condition. The computational model captured this behavioral asymmetry: $\gamma$ was significantly higher in the Majority condition than the Minority condition, indicating stronger default ingroup classification when contrasting against the racial majority. Neither $\alpha$ nor $\lambda$ differed by condition, and unlike Study 2, $\lambda$ was identical across conditions. Sym+$\lambda$ was the unambiguous winner. FDR-corrected individual differences were null across all parameters, indicating that the MCR–personality structure from Studies 1 and 2 did not replicate in the racial context.

SCT provides two complementary interpretations. The meta-contrast principle predicts that categorization becomes psychologically active when perceived intergroup differences exceed intragroup differences. Contrasting against the dominant majority group instantiates a high-stakes boundary that status perceptions alone cannot resolve, motivating self-anchoring to define and stabilize ingroup identity. When contrasting against a fellow minority group, shared subordinate status may invoke a sense of common fate, blurring the functional distinctiveness of the between-minority boundary. The positive distinctiveness principle offers a related account: differentiation motivation is strongest against a more powerful outgroup and weakest when the comparison makes ingroup status superiority ambiguous.

Formal tests showed that neither trained nor novel-trait effects were significant in the minority condition. In the majority condition, the trained-trait effect was significant but the novel-trait effect was not. Both trained and novel AMEs were numerically larger in the majority condition than in the minority condition, consistent with a gradient of self-anchoring strength rather than a categorical absence.

In Study 2, generalization to novel traits was robust in the negation and high-status conditions. In Study 3, trained-trait effects were significant only in the majority condition and did not extend to novel traits in either condition. Racial categories carry more pre-structured content than university affiliations: participants already hold expectations about which traits "belong" to racial groups, leaving less room for self-referential inference. Van Veelen et al. (2017) proposed that self-anchoring is most active when group content is uncertain; university groups provide thin stereotypic content while racial groups come pre-loaded with cultural stereotypes that compete with self-anchoring. The null individual-difference findings in Study 3 (versus reliable MCR–personality associations in Studies 1 and 2) are consistent with this interpretation: in racial contexts, fixed categorical content may override individual variation in self-concept organization, attenuating the link between self-concept structure and generalization behavior.

## POOLED ANALYSIS

To formally test whether the self-anchoring architecture generalizes across intergroup contexts, we fit the four hierarchical models to the combined sample across Studies 1–3 (*N* = 507) using a three-level hierarchy (Global $\rightarrow$ Study $\rightarrow$ Subject). This architecture estimates global population parameters ($\alpha$, $\gamma$, $\lambda$) shared across all three studies while accommodating study-level deviations, providing a formal test of cross-context generalizability. We also conducted pooled behavioral GLMMs spanning all three studies to formally test whether similarity-based self-anchoring and semantic generalization varied systematically across conditions, using Study 1's minimal groups as the reference category.

### Results

**Table 5. LOO Model Comparison — Pooled Analysis (*N* = 507).**

| Model | ELPD | SE | $\Delta$ELPD | $\Delta$SE |
|:------|-----:|---:|-------------:|----------:|
| Sym+$\lambda$ | −46,113.3 | 92.4 | 0.0 | — |
| Asym+$\lambda$ | −46,160.1 | 91.7 | −46.8 | 6.9 |
| Symmetric | −46,699.3 | 86.1 | −586.0 | 31.6 |
| Bias | −47,188.8 | 83.9 | −1,075.5 | 40.4 |

*Note.* ELPD = expected log predictive density. $\Delta$ELPD relative to best-fitting model (row 1). Models ordered from best to worst fit. $|\Delta\text{ELPD}| > 2 \times \Delta\text{SE}$ is taken as meaningful difference in predictive accuracy. Pooled models use a three-level hierarchical structure (Global → Study → Subject); Sym+$\lambda$: $\hat{R}_{\max}$ = 1.008, <0.1% divergent transitions, 98.3% Pareto $k < 0.7$.

```{r}
#| label: fig-elpd-pooled
#| fig-cap: "Per-subject LOO-ELPD by model, Pooled Analysis (*N* = 507). Each line represents one participant's summed LOO-ELPD trajectory across the four computational architectures. Higher (less negative) values indicate better individual-level predictive accuracy. Boxplots show median and IQR; diamonds indicate group means. *Note.* ELPD = expected log predictive density computed via leave-one-out cross-validation using three-level hierarchical models (Global → Study → Subject)."
#| fig-width: 7
#| fig-height: 5.5
#| eval: !expr file.exists(fig_path("fig_elpd_raincloud_pooled.tiff"))
knitr::include_graphics(fig_path("fig_elpd_raincloud_pooled.tiff"))
```

```{r}
#| label: fig-elpd-pooled-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_elpd_raincloud_pooled.tiff")))
cat("*[Figure pending: Per-subject LOO-ELPD slopegraph for Pooled analysis — re-run `make_figures.R` after `Pooled/run_pooled_analysis.R` completes.]*")
```

At the pooled level, Sym+$\lambda$ clearly outperformed Asym+$\lambda$ ($\Delta$ELPD = −46.8, SE = 6.9; $|\Delta\text{ELPD}|/\Delta\text{SE} = 6.8$), extending the individual-study pattern to the pooled three-level hierarchy: the asymmetric architecture provides no predictive advantage when data are aggregated across all three intergroup contexts. Both generalization-sensitive architectures substantially outperformed the Symmetric model ($\Delta$ELPD = −586.0, SE = 31.6) and the Bias model ($\Delta$ELPD = −1,075.5, SE = 40.4), confirming that the generalization sensitivity parameter ($\lambda$) is a necessary component of the architecture across all intergroup contexts studied.

**Table 6. Pooled Sym+$\lambda$ Parameter Estimates: Global and Study-Specific Means.**

| Parameter | Global Grand Mean | Study 1 (Minimal) | Study 2 (Status) | Study 3 (Racial) |
|:----------|-------:|------------------:|-----------------:|-----------------:|
| $\alpha$ (projection slope) | 0.691 | 0.691 | 0.768 | 0.638 |
| $\gamma$ (ingroup bias) | 0.500 | 0.453 | 0.508 | 0.505 |
| $\lambda$ (generalization) | 3.196 | 3.450 | 3.267 | 3.090 |

*Note.* Values are grand means of individual-level posterior medians; see *Reporting Convention* in Study 1 Methods. Global hyperparameter medians (back-transformed from $\mu_{pr}$): $\alpha = 0.319$ [0.191, 0.590], $\gamma = 0.500$ [0.421, 0.551], $\lambda = 3.196$ [3.010, 3.549].

$\lambda$ showed the highest cross-study consistency. Grand means were 3.45 (minimal groups), 3.27 (status), and 3.09 (racial), with a global grand mean of 3.20 — a 0.36-unit range, or roughly 11% of the grand mean. Minimal-group contexts produced somewhat broader generalization than racial-group contexts.

Ingroup bias ($\gamma$) was lower in Study 1 (minimal groups; grand mean $\gamma$ = 0.453) than in Studies 2 and 3 (0.508 and 0.505, respectively), replicating the individual study pattern and consistent with the view that minimal group boundaries generate weaker ingroup preference than socially meaningful categories. The projection slope ($\alpha$) showed modest cross-study variation intermediate between the relative stability of $\lambda$ and the pronounced contextual sensitivity of $\gamma$: grand means were 0.768 (status groups), 0.691 (minimal groups), and 0.638 (racial groups), a 0.13-unit range. University-status comparisons engaged the self-concept most actively as an inferential resource — likely because university identity is personally relevant but group content is sparse — while racial categories, carrying pre-established cultural content, produced the lowest projection slope. The hierarchical pooling model partially regularizes individual-study estimates toward the global mean, so the apparent between-study spread in $\alpha$ likely represents a lower bound on the true cross-context variability.

**Individual Differences (Pooled CCA).** To assess whether model parameters were systematically associated with personality across all three studies, we conducted a canonical correlation analysis linking the four model parameters ($\alpha$, $\gamma$, $\lambda$, MCR) with nine personality scales in the pooled sample (*N* = 498 with complete personality data; nine Study 3 participants were excluded for missing personality scale responses, yielding *n* = 61, 181, and 256 from Studies 1–3; the full behavioral sample of *N* = 507 was used for all other pooled analyses). Only CV1 reached significance (*r* = .327, *p*$_{\text{perm}}$ < .001; CV2–4 all *p*s > .25). On the model side, MCR dominated CV1 (loading = .864), with smaller contributions from $\gamma$ (−.417), $\lambda$ (.270), and $\alpha$ (.128). On the personality side, self-esteem loaded most strongly (.817), followed by self-concept clarity (.685), dialectical self-views (−.654), need for cognition (.570), and independent self-construal (.536). This pooled CV1 reproduces the pattern from Studies 1 and 2: higher MCR is cross-contextually associated with higher self-esteem, clearer self-concept, and lower dialectical self-views. The dominance of MCR over model parameters in the pooled CCA is consistent with the individual study results and confirms that the metacontrast ratio — the ratio of self-concept similarity signal favoring the ingroup over the outgroup — is the primary computational carrier of personality variation in social generalization across intergroup contexts.

```{r}
#| label: fig-forest-pooled
#| fig-cap: "Sym+λ parameter estimates across all conditions and pooled global. Points show condition-level means of individual posterior medians (±95% CI); point size scales with condition N. Diamond shows the pooled global estimate (90% CI from Φ-transformed global_mu_pr posteriors). Dashed vertical lines mark pooled global means. Conditions are ordered by study (Study 1 top; Pooled bottom)."
#| eval: !expr file.exists(fig_path("fig_forest_plot_pooled.tiff"))
#| echo: false
#| fig-width: 11
#| fig-height: 4.5
knitr::include_graphics(fig_path("fig_forest_plot_pooled.tiff"))
```

```{r}
#| label: fig-combined-alpha-gradient
#| fig-cap: "Ingroup projection slopes (left) and generalization gradients (right) by study and condition, using pooled model individual estimates. Left column: logistic projection curve G_in(E) = plogis(α[E−4]) showing how strongly each self-rating level maps onto ingroup classification probability. Faint lines are individual participant curves; the band-like appearance reflects accumulation of 61–265 individual curves per study. Bold lines show condition means. Right column: S^λ generalization decay curves as a function of trait semantic similarity; faint lines show individuals, shaded band shows ±1 SD around the condition mean, bold line shows the mean. Colors match other figures (Study 1: black; Study 2: orange=Negation, blue=High-Status, green=Low-Status; Study 3: pink=Minority, blue=Majority). Individual estimates from the three-level pooled model (Global → Study → Subject)."
#| fig-width: 12
#| fig-height: 9
#| eval: !expr file.exists(fig_path("fig_combined_alpha_gradient.tiff"))
knitr::include_graphics(fig_path("fig_combined_alpha_gradient.tiff"))
```

```{r}
#| label: fig-combined-alpha-gradient-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_combined_alpha_gradient.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

**Behavioral Analyses**

To formally compare self-anchoring and generalization effects across all three studies in a single model, we fit mixed-effects logistic regression models using `lme4` to the combined dataset (*N* = 507 subjects, 73,771 observations). Each study contributed its own condition levels, with Study 1's minimal-groups condition as the reference category. Predictors were Z-scored within study so that 1 unit reflects a within-study standard deviation. Random effects included study-level intercepts, subject intercepts and slopes nested within study, and trait intercepts nested within study — allowing each intergroup context to carry its own baseline attribution probability for each trait.

Across the full pooled sample, similarity-to-self was a significant predictor of ingroup classification (AME = .039, 95% CI [.022, .055], *z* = 4.58, *p* < .001), as were self-evaluations (AME = .046, CI [.038, .054], *z* = 11.40, *p* < .001) and desirability (AME = .036, CI [.027, .045], *z* = 7.72, *p* < .001). These overall effects confirm that self-anchoring operates reliably as a cross-study phenomenon.

Condition-specific AMEs for similarity-to-self (all relative to the minimal-groups reference) revealed clear contextual modulation. The effect was present and significant in minimal groups (AME = .069, CI [.022, .115], *z* = 2.91, *p* = .004), the negation condition (AME = .048, CI [.016, .081], *z* = 2.92, *p* = .004), the low-status condition (AME = .048, CI [.001, .095], *z* = 1.99, *p* = .046), and the racial majority condition (AME = .039, CI [.006, .071], *z* = 2.31, *p* = .021). The high-status condition showed the strongest similarity-based generalization of any condition (AME = .094, CI [.043, .145], *z* = 3.60, *p* < .001). The racial minority condition was the sole context with a null or directionally reversed effect (AME = −.007, CI [−.042, .027], *z* = −0.43, *p* = .672), confirming the cross-study robustness of this specific boundary condition identified in Study 3.

The predicted P(ingroup) at ±1 SD of similarity-to-self further illustrates the gradient. In the high-status condition, P(ingroup) ranged from .41 at −1 SD to .60 at +1 SD (.190 range), the steepest gradient observed. Minimal groups showed a .150 range (.481 to .631), while the racial minority condition was essentially flat (.568 at −1 SD, .557 at +1 SD).

To test generalization formally, we tested whether the similarity-based inference propagates to semantically novel traits. Pooled across conditions, both trained (AME = .042, CI [.025, .059], *z* = 4.84, *p* < .001) and novel-trait effects (AME = .037, CI [.020, .054], *z* = 4.33, *p* < .001) were significant, confirming robust generalization at the pooled level. The three-way analysis revealed that generalization was condition-specific. In the racial minority condition, neither trained (AME = −.008, *z* = −0.45, *p* = .649) nor novel-trait (AME = −.005, *z* = −0.26, *p* = .793) effects were significant — a complete null. In the racial majority condition, the trained-trait effect was significant (AME = .045, CI [.011, .078], *z* = 2.62, *p* = .009) but the novel-trait effect did not reach significance (AME = .031, CI [−.003, .064], *z* = 1.81, *p* = .071). Among the university conditions and minimal groups, all showed significant trained-trait effects: high-status trained AME = .097 (*z* = 3.66, *p* < .001), novel = .091 (*z* = 3.43, *p* < .001); negation trained = .051 (*z* = 3.01, *p* = .003), novel = .045 (*z* = 2.66, *p* = .008); low-status trained = .051 (*z* = 2.10, *p* = .036), novel = .043 (*z* = 1.72, *p* = .086); minimal groups trained = .067 (*z* = 2.79, *p* = .005), novel = .072 (*z* = 2.97, *p* = .003). Novel-trait generalization was significant in the high-status, negation, and minimal-groups conditions; the low-status and racial majority conditions showed positive but sub-threshold novel-trait effects (*p*s = .086 and .071, respectively).

The low-status condition AME in the pooled model (AME = .048, *p* = .046) reaches significance compared to the Study 2 standalone estimate (AME = .044, *p* = .082). These estimates differ for two reasons. First, in the pooled model the reference category is Study 1's minimal-group baseline rather than Study 2's negation condition, shifting the model intercept; second, estimation in the pooled model draws on the full 507-person sample, increasing precision. The point estimates are directionally consistent and the pooled estimate should be taken as the more stable value.

Taken together, the pooled behavioral analyses converge with individual study findings to identify a clear principle: self-anchoring and semantic generalization are robust across minimal, university status, and racial majority contexts, but are specifically absent when the comparison involves a fellow minority group — a condition in which the shared subordinate social position may undermine the functional distinctiveness of the between-group boundary.

### Discussion

The pooled analysis confirms the main conclusions from the individual studies and adds two findings that individual study estimates cannot establish. First, the symmetric architecture is clearly preferred over the asymmetric architecture at the pooled level. Across 507 participants and 73,771 trials spanning three distinct intergroup contexts, distinguishing ingroup projection from outgroup repulsion provides no reliable improvement in held-out predictive accuracy. The pooled model confirms that the binary forced-choice paradigm does not carry sufficient information to separate these two motives: the single projection slope absorbs both.

Second, the pooled parameter estimates allow formal statements about what is and is not stable across intergroup contexts. The generalization sensitivity parameter ($\lambda$) showed the highest cross-study consistency: grand means of 3.45, 3.27, and 3.09 converged on a global grand mean of 3.20, a range of roughly 11%. That $\lambda$ was replicable across minimal groups, university status contrasts, and racial contrasts supports the interpretation that generalization sensitivity is a stable individual characteristic reflecting self-concept structure rather than context-specific motivation. The ingroup bias prior ($\gamma$) showed the clearest contextual sensitivity: Study 1 minimal groups produced lower bias than the socially structured comparisons of Studies 2 and 3. The projection slope ($\alpha$) occupied an intermediate position — showing modest cross-study variation (0.638–0.768) that exceeded $\lambda$'s relative consistency but fell well short of $\gamma$'s contextual sensitivity. University-status comparisons appear to engage the self-concept most actively as an inferential resource — likely because university identity is construed as personally relevant and group content is sparse, leaving self-anchoring as the primary organizing mechanism. Racial categories, by contrast, carry pre-established cultural content that competes with self-referential inference, consistent with the Van Veelen et al. (2017) account that self-anchoring is strongest when group content is uncertain.

The pooled CCA provides a cross-contextual individual differences summary. Only the first canonical variate was significant, and it was dominated by the metacontrast ratio on the model side, with self-esteem, self-concept clarity, and dialectical self-views leading on the personality side. This replicates the structure identified in Studies 1 and 2 and establishes that the MCR–personality link is not context-specific. Across all three intergroup settings, participants with higher self-esteem, clearer self-concepts, and less dialectical self-views show greater self-anchoring contrast signal, which is the organizational property of the self-concept that drives between-group differentiation.

Taken together, the pooled results support a two-level account of self-anchoring generalization: a stable inferential engine ($\lambda$, and to a lesser extent $\alpha$) that reflects self-concept structure and is consistent across intergroup contexts, and a context-sensitive motivational prior ($\gamma$) that responds to the social meaning and power relations of the specific comparison. The behavioral analyses confirm this partition: the racial minority context, the one condition in which the motivational conditions for self-anchoring were undermined, was the only context in which both self-anchoring and generalization were behaviorally absent.

The two most striking condition-specific patterns — the null racial minority context and the strongest high-status context — converge on a theoretically coherent account. Self-Categorization Theory (Turner et al., 1987) predicts that a categorization becomes psychologically active in proportion to perceived between-group differences relative to within-group similarities, and that its salience is governed by comparative fit — whether the categorization better captures the contrast structure of the social context than available alternatives (Turner et al., 1994). In a comparison between two racial minority groups sharing a common subordinate position within a majority-dominated society, the between-minority boundary carries lower comparative fit than the minority-versus-majority contrast that both groups share. The more psychologically compelling categorization axis subordinates the between-minority boundary, rendering the latter an insufficient basis for self-referential content differentiation. Crucially, the computational parameters in Study 3 provide no parameter-level account for the null: projection slope, ingroup bias, generalization sensitivity, and metacontrast ratio were statistically equivalent between racial minority and majority conditions. The inferential architecture itself was not disrupted; rather, the behavioral null reflects a social-structural condition in which even intact self-projection does not produce between-group differentiated classification.

Conversely, the high-status context produced the strongest similarity-based self-anchoring of any condition studied, and this too follows from first principles. Optimal Distinctiveness Theory (Brewer, 1991) holds that group membership simultaneously satisfies inclusion and differentiation needs. When an outgroup is unambiguously superior in status, positive distinctiveness through social comparison is foreclosed, and the need for distinctive ingroup content intensifies — creating precisely the conditions under which self-concept serves as the primary defining resource. Social Identity Theory's positive distinctiveness motive (Tajfel & Turner, 1986) provides a parallel account: self-anchoring substitutes for, rather than amplifies, status-based favoritism. The computational signature of this substitution is visible in Study 2: ingroup bias ($\gamma$) fell to its lowest value of any condition in the high-status comparison — well below the minimal-groups baseline — while the symmetric architecture was preferred over the asymmetric alternative specifically in that condition (*p* = .039). Against a positively-regarded, higher-status rival, categorical ingroup preference weakens, and self-concept-driven content inference steps into the resulting organizational vacuum.

## GENERAL DISCUSSION
People project their attributes onto ingroup members, but the underlying cognitive mechanisms have remained largely descriptive. Using a semantic dependency network of trait relations, we formalize self-anchoring as a structured inferential process based on similarity-based generalization. Across three studies, individuals treated the self as a semantic prototype, with beliefs propagating to novel group members via relational similarity—a finding robust across minimal, university, and racial categories. The cross-study consistency of λ and the condition-level variation in α and γ are illustrated in @fig-combined-alpha-gradient (individual-level projection slopes and generalization gradients by study and condition). @fig-cross-study-params summarizes the group-level posterior estimates for α, γ, and λ across studies, highlighting both the relative stability of the generalization mechanism and the context-sensitivity of the motivational prior.

```{r}
#| label: fig-cross-study-params
#| fig-cap: "Cross-study parameter estimates (Symmetric+λ model). Posterior medians with 90% credible intervals for projection slope (α), ingroup bias (γ), and generalization sensitivity (λ) across Studies 1–3. Generalization sensitivity is relatively stable across intergroup contexts; ingroup bias and projection slope show the most contextual variation."
#| fig-width: 12
#| fig-height: 3.8
#| eval: !expr file.exists(fig_path("fig_cross_study_params.tiff"))
knitr::include_graphics(fig_path("fig_cross_study_params.tiff"))
```

```{r}
#| label: fig-cross-study-params-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_cross_study_params.tiff")))
cat("*[Figure pending: run `Figures/make_figures.R` to generate.]*")
```

The cross-study consistency of λ — grand means ranging from 3.45 (minimal groups) to 3.09 (racial groups), global grand mean 3.20 — is consistent with generalization sensitivity reflecting self-concept structure rather than intergroup motivation: the same breadth of inferential reach operates whether the comparison group is arbitrary, status-stratified, or racially defined.

### Formalizing Social Identity Theory
This research operationalizes the metacontrast principle as a formal ratio of summed similarities, aligning social identity research with exemplar-based models of category learning and Shepard's (1987) law of generalization. Across all three studies, the asymmetric architecture provided no statistically reliable advantage over the symmetric one, indicating that ingroup love and outgroup repulsion are not architecturally dissociable within the paradigm's binary forced-choice structure; both are absorbed into a single projection slope.
Prior representational claims about similarity-based inference in social categorization have been constrained by the absence of model formalism (Guest & Martin, 2021). We demonstrate that the metacontrast ratio can be precisely measured using relational similarity, yielding testable predictions that verbal accounts cannot generate. Shepard's (1987) law was derived from animal conditioning and perceptual psychophysics: organisms generalize a learned response to novel stimuli in proportion to their similarity to the training exemplar, with that gradient decaying exponentially at a rate governed by a single sensitivity parameter. Nosofsky (1986) showed the same formal structure accounts for human perceptual categorization. That an identical mathematical law appears here—where the prototype is the self, the stimuli are personality traits in a semantic network, and the task is social group classification—is consistent with Shepard's generalization law reflecting a domain-general inference principle: given what I know about one exemplar, how strongly should I predict a property of a novel one? Social identity formation appears to follow the same formal structure — exponential generalization decay governed by a scalar sensitivity parameter — that Shepard identified in animal learning and Nosofsky formalized for perception. Both traditions emerged in parallel with Turner and Tajfel's verbal articulation of the same principles; we connect these traditions and provide an empirically tractable foundation for the representational claims Self-Categorization Theory has long advanced. A notable result is the empirical identification of $\lambda$—Shepard's generalization sensitivity—as a recoverable parameter in human social categorization data. In principle, $\lambda$ and $\alpha$ are mathematically entangled, and their joint identifiability requires the graded semantic structure of a trait network combined with a training-to-generalization paradigm. Demonstrating that $\lambda$ is estimable from social categorization data provides a quantitative index of self-concept breadth that cannot be reduced to projection strength, enabling researchers to formally distinguish how far the self-concept's inferential reach extends ($\lambda$) from how strongly self-beliefs are weighted in that inference ($\alpha$)—a distinction verbal theories of self-anchoring have never been able to draw.

Turner et al. (1987) defined the metacontrast ratio verbally as the ratio of perceived intergroup difference to intragroup similarity, with categorization becoming psychologically active when this ratio is maximized. The model-derived MCR — $\text{simW}_{in} / \text{simW}_{out}$ — is the direct computational implementation of that definition, not an analogy. $\text{simW}_{in}$ and $\text{simW}_{out}$ are generalization-weighted sums of self-beliefs projected onto ingroup- versus outgroup-predictive training traits, calibrated to each participant's posterior parameter estimates. MCR correlations with self-concept organization — dialectical self-views in Study 1 and self-esteem and self-concept clarity in Study 2 — validate this operationalization as capturing what Turner's verbal construct intended. These associations did not survive correction in Study 3; fixed racial category content may have attenuated individual variation in self-referential inference. The self functions here as a social prototype in the sense Rosch (1978) formalized for natural categories: the reference point relative to which group category membership is inferred.

In this context, the structure of the self-concept and not the subjective sense of group representativeness drives intergroup differentiation. Perceived prototypicality did not predict the projection slope $\alpha$ in any study, indicating that self-to-group mapping operates independently of whether participants regard themselves as typical ingroup exemplars. In Study 2, however, self-esteem, self-concept clarity, and need for cognition each correlated reliably with the model-derived MCR — the ratio of self-concept similarity signal favoring the ingroup over the outgroup. This dissociation reveals that the self-as-prototype assumption holds at the level of the self-concept's *semantic contrast structure* (how much its organization discriminates ingroup from outgroup) rather than how steeply self-beliefs slope into ingroup classification.

### Contextual Modulation and Social Identification
Context modulates self-anchoring through distinct parameters across studies. In Study 2, the projection slope (α) showed no significant difference across conditions; what changed was the prior ingroup preference (γ), which fell below the minimal-group baseline when the outgroup was a positively-regarded rival university. When the outgroup is desirable, participants' baseline disposition to attribute traits to the ingroup weakens — even while the similarity-weighted inference machinery operates unchanged. This pattern — α stable, γ sharply attenuated — was not the anticipated locus of contextual modulation; it emerged as a post-hoc observation illuminating a distinction social identity theory has typically left implicit: the inferential process of self-anchoring and the motivational prior that activates it are separable, and only the latter appears to be contextually modulated. Behaviorally, the High-Status condition produced the strongest similarity-to-self effect of any condition, while the Low-Status condition showed attenuation that did not reach significance. These patterns are not contradictory: γ is the intercept of ingroup preference, while the AME reflects the slope of similarity-based inference; a lower γ and steeper slope can co-occur when participants rely more heavily on self-information in the absence of a strong default ingroup prior — consistent with Optimal Distinctiveness Theory's prediction that reduced group-based distinctiveness heightens reliance on self-concept content to define group identity (Brewer, 1991; Leonardelli et al., 2010). In Study 3, self-anchoring was absent under minority–minority contrasts, with similarity-to-self predicting ingroup classification only in the majority-outgroup condition. Computationally, this behavioral asymmetry corresponded to a difference in $\gamma$: ingroup classification bias was higher when contrasting against the racial majority than against a fellow minority. The meta-contrast principle provides a unifying account: self-anchoring and the motivational ingroup prior are most active when the intergroup boundary is motivationally engaged but not structurally resolved by status cues alone. When contrasting against a fellow minority, shared subordinate position may invoke a sense of common fate that reduces the comparative fit of the between-minority categorization relative to the more salient minority–majority contrast both groups share (Turner et al., 1994), lowering both the motivational pressure for self-referential inference and the baseline disposition to attribute traits to the ingroup.

As an aside, we developed and validated a network-based trait segregation index (network nominal homophily) to quantify the degree to which participants' ingroup versus outgroup classifications clustered along the semantic similarity structure. Results across all three studies are reported in Supplementary Materials K; the index showed condition-specific variation consistent with the behavioral and computational findings but is not a central focus of the present paper.

Within this framework, γ operationalizes SIT's positive distinctiveness motive — the baseline prior for ingroup attribution, independent of the projection mechanism. Crucially, the social-contextual content of that motive varies across comparison types, and we argue this variation is itself theoretically informative rather than a limitation of the parameter's interpretability. γ does not have a single fixed social meaning; instead, it captures whatever motivational structure the intergroup context imposes on the baseline tendency to attribute traits to the ingroup. The High-Status condition in Study 2 provides the clearest empirical signature: γ, reduced from the Negation baseline. A prestigious outgroup erodes the ingroup preference that even arbitrary group assignment produces; under SIT, this follows because positive distinctiveness motivation is highest when ingroup status superiority is uncertain. In Study 3, γ showed the opposite directional pattern: elevated when contrasting against the racial majority and lower when contrasting against a fellow minority. A prestigious rival university is an *aspirational* outgroup: the boundary is permeable, the outgroup is positively regarded, and no entrenched power asymmetry structures the comparison. A dominant racial majority is a different kind of comparison: the boundary is impermeable, the power asymmetry is entrenched, and minority identity is organized in part around protection against that asymmetry. Facing the racial majority activates a defensive ingroup prior, elevating γ relative to the within-minority comparison. Contrasting against a fellow minority suppresses it, consistent with common-fate identification reducing functional ingroup distinctiveness. That γ shifts in opposite directions across these two contexts is not a contradiction — it reflects the parameter's sensitivity to the specific motivational demands of each social comparison, and it is precisely this context-sensitivity that gives γ theoretical value as a formal index of the positive distinctiveness motive.

The generalization sensitivity parameter λ operationalizes the decay of self-anchoring across the semantic network as a person-specific index of inferential reach. High λ produces faster decay, restricting inference to semantically proximal traits; low λ allows broader propagation to more distal attributes. λ was broadly stable across intergroup contexts — global grand mean 3.20, grand mean range 3.09–3.45 — though Study 2 showed small but significant condition-level differences in generalization sensitivity, suggesting categorical boundary salience may produce modest compression of the generalization sensitivity curve. Higher social identification correlated with higher λ in Study 2, indicating that stronger group identification sharpens the inferential boundary — anchoring primarily on diagnostically proximal attributes — rather than broadening it.

### Limitations
The binary forced-choice paradigm imposes a structural limit on dissociating $\alpha_{in}$ from $\alpha_{out}$: each trial yields a single ingroup-or-outgroup response, so ingroup attractiveness and outgroup repulsion cannot vary independently within a trial. Paradigms that solicit independent ingroup and outgroup typicality ratings would provide richer behavioral signatures for estimating these parameters separately. The consistent symmetric-architecture preference may therefore partly reflect task constraints rather than genuine cognitive indistinguishability of ingroup love and outgroup hate. The trait pool consisted entirely of positively valenced traits, constraining interpretation of $\gamma$. Because all traits are desirable, $\gamma$ above 0.5 reflects preferential attribution of valued characteristics to the ingroup — but the model cannot separately estimate ingroup attribution versus outgroup withholding of positive traits, and outgroup derogation via negative trait assignment is outside the paradigm's scope entirely. Future work incorporating both positive and negative traits would allow $\gamma$ to capture the full valence structure of ingroup favoritism and outgroup derogation. Of SCT's four fit criteria, neither normative fit nor perceiver readiness is directly assessed. Normative fit — whether trait content matches expectations for a group label — is not measured. Perceiver readiness is imposed by the task structure: the model describes how self-anchoring operates once a category is engaged, not who spontaneously activates social categorization in naturalistic settings. Comparative fit was explored via $\lambda$ variation across Study 2 conditions, but effects were small ($R^2$ = .054) and these analyses should be treated as exploratory rather than formal tests of comparative fit. Finally, the cross-study consistency of $\lambda$ ≈ 3.1–3.5 is partly constrained by the fixed semantic similarity matrix shared across all analyses; fully independent replication with a distinct similarity instrument would be required before treating this range as a domain-general constant.

### Conclusion
Group beliefs are not stored as fixed templates but constructed by propagating self-knowledge through relational semantic structure — the same formal architecture identified in perceptual categorization research. What is most consistent across intergroup contexts is the generalization architecture (λ showed the highest cross-study consistency, ranging 3.09–3.45); the motivational parameters were context-sensitive: the baseline ingroup prior (γ) responded to the desirability, status, and power relations of the comparison group, and the projection slope (α) varied across contexts (0.638–0.768), highest in university status comparisons and lowest in racial ones. Formalizing these distinctions within a single computational architecture provides a testable account of social identity that verbal theories have approximated but not achieved.

### Supplementary Materials A: Posterior Predictive Checks
We conducted posterior predictive checks (PPCs) to verify model fit to observed data, evaluating both the training and generalization phases across all three studies. Observed and predicted data were well-aligned, confirming adequate fit.

### Supplementary Materials B: Parameter Recovery Analyses
We assessed parameter identifiability by simulating behavior from known true parameters, then fitting the model to the simulated data and comparing recovered posteriors to ground truth. The simulation used the Study 1 trial structure (*N* = 61), real trait similarity matrices, and two design choices described below.

**Parameter generation.** True parameters for each simulated participant were drawn from distributions calibrated to the Study 1 NoW posterior rather than from the prior. Group-level means ($\mu_{pr}$) and individual-level standard deviations ($\sigma$) on the probit scale were taken directly from the Study 1 NoW posterior summaries (Sym+$\lambda$: $\sigma_\alpha = 0.732$, $\sigma_\gamma = 0.343$, $\sigma_\lambda = 0.076$; Asym+$\lambda$: $\sigma_{\alpha_{in}} = 0.732$, $\sigma_{\alpha_{out}} = 0.732$, $\sigma_\gamma = 0.343$, $\sigma_\lambda = 0.076$). This ensures simulated individual differences match the range actually observed in the data rather than an arbitrary prior specification. Because the posterior $\sigma_\lambda = 0.076$ concentrates 95% of participants within $\lambda \in [3.45, 3.94]$ — a span of less than 0.5 units — we additionally ran a capacity test with $\sigma_\lambda = 0.30$ (spanning approximately $\lambda \in [2.4, 4.8]$) to assess whether the model can identify $\lambda$ when genuine individual variation is present.

**Self-rating generation.** Each simulated participant received synthetic self-ratings drawn from a Gaussian Markov Random Field (GMRF) defined on the trait network. Prior shrinkage for $\lambda$. An initial recovery analysis revealed a structural $\lambda$–$\alpha$ identifiability tradeoff: because both parameters scale the ingroup-over-outgroup evidence ratio ($\text{simW}_{in}/\text{simW}_{out}$), the likelihood surface is approximately flat along the ($\alpha$, $\lambda$) ridge, and the parameters partially trade off against one another in estimation. Removing the lapse parameter ($w$) substantially improved recovery of both $\alpha$ and $\lambda$ relative to the full model, consistent with $w$ suppressing the mechanistic signal by down-weighting all trial-level projection evidence. However, residual $\alpha$–$\lambda$ competition remained. Assigning a tighter hierarchical prior to the individual-level $\lambda$ dispersion ($\sigma_\lambda \sim \text{Half-Normal}(0, 0.1)$) — while retaining the standard dispersion prior for $\alpha$ ($\sigma_\alpha \sim \text{Half-Normal}(0, 0.3)$) — yielded marked improvements in $\alpha$ recovery and acceptable $\lambda$ recovery, validating this prior specification for the final models. We computed the precision matrix $\mathbf{P} = \alpha\mathbf{L} + \varepsilon\mathbf{I}_{148}$, where $\mathbf{L} = \mathbf{D} - \mathbf{A}$ is the combinatorial graph Laplacian of the trait network, $\alpha = 1.0$ controls network smoothness, and $\varepsilon = 0.01$ regularizes the singular Laplacian. Each participant received an independent draw $\mathbf{x} \sim \mathcal{N}(\mathbf{0},\, \mathbf{P}^{-1})$, standardized to the observed within-person SD (1.13), centered at 4, and rounded to integers 1–7. Intuitively, the graph Laplacian encodes which traits are structurally proximate in the network; inverting the regularized Laplacian produces a covariance matrix in which connected traits covary — a participant who rates *Warm* highly will tend to rate *Friendly* similarly, exactly the structure the projection model assumes. Centering ratings at the scale midpoint (4) ensures that self-ratings span both the self-descriptive and non-self-descriptive range, which is required for $\alpha$ to be identifiable from the data.

Recovery varied by parameter and architecture (Figure B1). Both models converged well (max Rhat < 1.01, zero divergent transitions). For the Symmetric+$\lambda$ model, ingroup bias showed excellent recovery ($\gamma$: *r* = .944, RMSE = 0.039), and projection slope showed good individual-level recovery ($\alpha$: *r* = .763, RMSE = 0.616, bias = −0.192), with the modest downward bias reflecting appropriate shrinkage of extreme estimates toward the group mean. Generalization sensitivity showed moderate individual-level recovery in the capacity test ($\lambda$: *r* = .342, RMSE = 0.532, bias = +0.258); the upward bias reflects the regularizing prior pulling individual estimates toward the group mean, as the model is designed to treat $\lambda$ as primarily a group-level parameter. Group-level $\mu_\lambda$ is well-identified through the hierarchical structure. For the Asymmetric+$\lambda$ model, bias recovered well ($\gamma$: *r* = .956). Both projection slopes showed substantially reduced recovery ($\alpha_{in}$: *r* = .400, RMSE = 1.195; $\alpha_{out}$: *r* = .389, RMSE = 1.049), consistent with the theoretical prediction that a binary forced-choice task provides insufficient leverage to dissociate ingroup and outgroup projection slopes at the individual level. These results reinforce the symmetric architecture as the more parsimonious and better-identified model. Figure B2 shows the parameter confusion matrix: each cell gives the Pearson *r* between true parameter *i* and recovered parameter *j*, with diagonal cells (outlined) reflecting self-recovery and off-diagonal cells reflecting cross-parameter confusability.

**Empirical recovery.** The random-parameter simulation above uses parameter values drawn from calibrated distributions, which may not match the specific range observed in the data. We therefore ran a complementary empirical recovery: true parameters were set to each Study 1 participant's actual posterior medians from the fitted models, and simulation used each participant's actual self-ratings rather than GMRF draws. This tests whether the parameter values driving the paper's results are themselves recoverable.

Results differed from random-parameter recovery in two ways. First, projection-slope recovery improved markedly for both models. Sym+$\lambda$ $\alpha$ recovered at *r* = .918 (RMSE = 0.355, bias = −0.056), compared to *r* = .763 under random recovery. Asym+$\lambda$ $\alpha_{in}$ and $\alpha_{out}$ recovered at *r* = .880 (RMSE = 0.166) and *r* = .865 (RMSE = 0.497), compared to *r* ≈ .40 under random recovery. The improvement reflects the higher $\alpha$ values observed empirically — actual participant medians extend well above those drawn from the calibrated simulation distribution — placing parameters in a more discriminable regime where the self-rating gradient spans a wider range. Second, $\lambda$ recovery showed lower *r* under empirical parameters (Sym+$\lambda$: *r* = .204, RMSE = 0.125; Asym+$\lambda$: *r* = .432, RMSE = 0.343). The lower *r* reflects range restriction: empirical $\lambda$ values cluster tightly across participants, leaving little between-person variance for the correlation to capture. The small RMSE confirms that absolute recovery error is minimal; the model estimates each individual's $\lambda$ near its true value. For the Asym+$\lambda$ model, the derived metacontrast ratio recovered well (*r* = .942, RMSE = 0.979, bias = −0.338), validating MCR as a recoverable individual-difference index when parameters reflect actual participant values.

```{r}
#| label: fig-param-recovery
#| fig-cap: "Parameter recovery for the Symmetric+λ (top row) and Asymmetric+λ (bottom row) models. Each panel shows the 2D density of true (x-axis) vs. posterior-median recovered (y-axis) parameter values across simulated participants (*N* = 61, Study 1 structure). The dashed red diagonal indicates perfect recovery. Pearson *r* values are shown per parameter."
#| fig-width: 11
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig_param_recovery.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery.tiff"))
```

```{r}
#| label: fig-param-recovery-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery.tiff")))
cat("*[Figure B1 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

```{r}
#| label: fig-param-recovery-heatmap
#| fig-cap: "Parameter recovery confusion matrix for the Symmetric+λ (left) and Asymmetric+λ (right) models. Each cell shows the Pearson *r* between the true value of parameter *i* (rows) and the posterior-median recovered value of parameter *j* (columns). Diagonal cells (black outline) give self-recovery correlations; off-diagonal cells reflect cross-parameter confusability. Higher off-diagonal values indicate that two parameters' behavioral signatures are difficult to disentangle."
#| fig-width: 9
#| fig-height: 5
#| eval: !expr file.exists(fig_path("fig_param_recovery_heatmap.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery_heatmap.tiff"))
```

```{r}
#| label: fig-param-recovery-heatmap-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery_heatmap.tiff")))
cat("*[Figure B2 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

```{r}
#| label: fig-param-recovery-empirical-heatmap
#| fig-cap: "Empirical parameter recovery confusion matrix for the Symmetric+λ (left) and Asymmetric+λ (right) models. True parameters were set to each Study 1 participant's actual posterior medians; re-simulation used each participant's actual self-ratings. Each cell shows the Pearson *r* between the true value of parameter *i* (rows) and the posterior-median recovered value of parameter *j* (columns). Diagonal cells (black outline) give self-recovery correlations under empirical conditions. Higher *r* values on the diagonal relative to Figure B2 indicate improved recovery for projection slope when parameters lie in the empirically observed range."
#| fig-width: 9
#| fig-height: 5
#| eval: !expr file.exists(fig_path("fig_param_recovery_empirical_heatmap.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery_empirical_heatmap.tiff"))
```

```{r}
#| label: fig-param-recovery-empirical-heatmap-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery_empirical_heatmap.tiff")))
cat("*[Figure B3 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

```{r}
#| label: fig-param-recovery-bias-rmse
#| fig-cap: "Parameter recovery RMSE (top) and bias (bottom) for the Symmetric+λ and Asymmetric+λ models under simulated (teal circles) and empirical (orange triangles) conditions. RMSE reflects absolute recovery error; bias reflects mean signed error (recovered − true). The dashed red line marks zero bias. λ shows low RMSE under empirical conditions despite low *r* (Figure B2), reflecting range restriction rather than large absolute errors. α recovery improves substantially under empirical conditions, where parameter values lie in a more discriminable regime."
#| fig-width: 10
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig_param_recovery_bias_rmse.tiff"))
knitr::include_graphics(fig_path("fig_param_recovery_bias_rmse.tiff"))
```

```{r}
#| label: fig-param-recovery-bias-rmse-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_param_recovery_bias_rmse.tiff")))
cat("*[Figure B4 pending: run `Figures/make_param_recovery_fig.R` to generate.]*")
```

```{r}
#| label: fig-05-lambda-identifiability
#| fig-cap: "Supplementary Figure B5. Parameter identifiability via Shepard's Law (λ). As λ increases, the generalization sensitivity curve steepens, restricting the influence of self-evaluations to only local semantic neighbors. This differential weighting of near versus distant novel traits provides the mathematical leverage necessary to distinguish the structural reach of the self-concept (λ) from the extremity of social projection (α)."
#| fig-width: 8
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig05_lambda_identifiability.tiff"))
knitr::include_graphics(fig_path("fig05_lambda_identifiability.tiff"))
```

```{r}
#| label: fig-05-lambda-identifiability-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig05_lambda_identifiability.tiff")))
cat("*[Figure B5 pending: run `Figures/make_figures.R` to generate.]*")
```

### Supplementary Materials C: Race Moderation Analyses (Study 3)

Study 3 pools Asian and Latino participants within each contrast condition, an assumption that warrants direct examination. We tested whether participant race (Asian vs. Latino) moderated the condition effects reported in the main text by adding a condition × race interaction term to each parameter model.

**Parameter estimates by condition × race.** Cell means for key parameters are shown in Table C1.

| Condition | Race | $\gamma$ | $\lambda$ | MCR |
|:---|:---|---:|---:|---:|
| Minority | Asian | 0.555 | 2.997 | 1.670 |
| Minority | Latino | 0.434 | 2.997 | 1.745 |
| Majority | Asian | 0.556 | 2.997 | 1.408 |
| Majority | Latino | 0.484 | 2.998 | 2.088 |

*Note.* N(Asian) = 130, N(Latino) = 135; Minority: Asian N=59, Latino N=79; Majority: Asian N=71, Latino N=56. Parameters are individual-level posterior medians averaged within each cell.

**Condition × race interaction.** The condition × race interaction for $\gamma$ was not significant, *F*(1, 261) = 2.28, *p* = .133. Descriptively, Asian participants showed similar ingroup bias across conditions (Minority $M$ = 0.555, Majority $M$ = 0.556), while Latino participants showed somewhat lower bias in the Minority condition (Minority $M$ = 0.434, Majority $M$ = 0.484; Latino main effect of race: $\beta$ = −0.121, *t*(261) = −5.47, *p* < .001; condition × race interaction: $\beta$ = +0.048, *t*(261) = 1.51, *p* = .133). Within the Minority (Asian-vs-Latino) contrast, Asians and Latinos occupy opposite ingroup/outgroup roles; the apparent lower bias for Latinos in the Minority condition may reflect this structural asymmetry. No condition × race interactions were significant for $\alpha$ (*F*(1, 261) < 0.01, *p* = .885), $\lambda$ (*F*(1, 261) < 0.01, *p* = .929), MCR (*F*(1, 261) = 2.22, *p* = .138), or $\Delta$ELPD (*F*(1, 261) = 1.04, *p* = .310).

**MCR–personality correlations by race.** Within Latino participants, MCR showed nominal (uncorrected) associations with dialectical self-views (*r*(130) = −.235, *p* = .007), independent self-construal (*r*(129) = .207, *p* = .018), and self-concept clarity (*r*(129) = .203, *p* = .020). No comparable associations emerged in Asian participants (all *p*s ≥ .073). These are uncorrected *p*-values; individual differences did not survive FDR correction at the pooled level. These race-stratified patterns should be interpreted cautiously given sample sizes within each race × condition cell (N = 56–79).

**Warmth moderation by race.** The race × ingroup-over-minority preference interaction for MCR was not significant (*p* = .099). No warmth × race interactions reached significance for any parameter. All race moderation results are exploratory, were not pre-registered, and should be replicated before interpretation.

### Supplementary Materials D: Self-Concept Entropy (*H_g*) and Ingroup Classification

We computed a *local self-concept clarity* index (*H_g*) as a similarity-weighted Shannon entropy over the self-evaluation distribution in each test trait's semantic neighborhood:

$$H_g = -\sum_{e=1}^{7} p_e \log_2 p_e, \quad p_e = \frac{\sum_{t:\, E_t = e} S_{tg}}{\sum_{t=1}^{T} S_{tg}}$$

where $p_e$ is the similarity-weighted proportion of training traits rated at level $e$ on the 7-point scale. Low $H_g$ indicates coherent, concentrated self-ratings near the test trait; high $H_g$ indicates mixed, diffuse self-ratings. This operationalizes Campbell et al.'s (1996) self-concept clarity at the local semantic level. Each study used a separate mixed-effects logistic regression with desirability controlled and a by-subject random slope for $H_g$.

$H_g$ was non-significant in Study 1 (AME = −.058, 95% CI [−.152, .036], *z* = −1.21, *p* = .225), consistent with low statistical power under minimal-group conditions. $H_g$ significantly predicted lower ingroup classification in Study 2 (AME = −.058, 95% CI [−.099, −.017], *z* = −2.78, *p* = .005) and Study 3 (AME = −.051, 95% CI [−.096, −.006], *z* = −2.21, *p* = .027). These results are consistent with a signal-precision account: when group content is real and self-anchoring is the primary inferential channel, a diffuse local self-concept degrades classification. The null in Study 1 is consistent with reduced behavioral leverage for detecting entropy effects when groups carry no prior content.

### Supplementary Materials E: Canonical Correlation Analysis

**Study 1 CCA (Minimal Groups, *N* = 61).** To examine the multivariate personality structure of model-derived indices, we conducted an exploratory CCA of model parameters (X: $\alpha$, $\lambda$, $\gamma$, MCR, trait segregation; $k = 5$) against personality scales (Y: Dialectical Self-Views, Ingroup Prototypicality, Self-Concept Clarity, Social Identification, Self-Esteem, Need to Belong, Need for Cognition, Independent Self-Construal, Interdependent Self-Construal; $k = 9$). Statistical significance was assessed via permutation test (*B* = 5,000). *N* = 61 falls below recommended guidelines for CCA with 14 variables; results should be regarded as preliminary and interpreted with caution. The first canonical variate was significant (*r* = .720, *p*~perm~ = .013). On the model side, CV1 was defined primarily by MCR (loading = .53), ingroup bias $\gamma$ (loading = .45), and trait segregation (loading = .39); $\alpha$ and $\lambda$ loaded negligibly. On the personality side, interdependent self-construal dominated (loading = .87), followed by social identification (loading = .53) and need to belong (loading = .48). A second variate was also significant (*r* = .623, *p*~perm~ = .005) but is not interpreted given the sample size. The pooled CCA below provides better-powered replication.

**Pooled CCA (*N* = 498).** To provide a better-powered test of the multivariate personality structure, we conducted a pooled CCA combining all three studies (*N* = 498 complete cases: *n* = 61, *n* = 181, *n* = 256; nine Study 3 participants excluded for missing personality data). Model parameters (X: $\alpha$, $\lambda$, $\gamma$, MCR; $k = 4$) and personality scales (Y: Dialectical Self-Views, Ingroup Prototypicality, Self-Concept Clarity, Social Identification, Self-Esteem, Need to Belong, Need for Cognition, Independent Self-Construal, Interdependent Self-Construal; $k = 9$) were Z-scored within each study before pooling to remove study-level mean differences. Statistical significance was assessed via permutation test (*B* = 5,000).

The first canonical variate was significant (*r* = .327, *p*~perm~ < .001); CV2–CV4 were all non-significant (*p*s > .25). On the model side, CV1 was dominated by MCR (loading = .864); $\gamma$ ($-.417$), $\lambda$ (.270), and $\alpha$ (.128) loaded more weakly. On the personality side, self-esteem dominated (loading = .817), followed by self-concept clarity (.685), dialectical self-views (−.654), need for cognition (.570), independent self-construal (.536), social identification (.357), and ingroup prototypicality (.360); need to belong showed a negative loading (−.237) and interdependent self-construal was negligible (.014). This pattern — MCR as the primary model driver aligned with an RSE/SCC/DS cluster — replicates the individual-study structure and confirms that the metacontrast ratio captures a coherent individual-difference dimension that generalizes across intergroup contexts: participants with higher self-esteem, clearer self-concepts, and fewer dialectical self-views show stronger self-anchoring signal regardless of group type. Table I1 reports the corresponding pooled bivariate correlations using the same within-study standardization strategy.

### Supplementary Materials F: Semantic Trait Network

The semantic dependency network used in all three studies comprised 148 personality traits. Figure F1 displays a force-directed layout of the 80 most-connected traits (Fruchterman–Reingold algorithm). Node size and color reflect degree centrality. Traits with high connectivity occupy the network's densely interconnected core and have broad semantic influence during the similarity-weighted inference process; low-degree traits at the periphery exert narrower inferential reach and primarily receive rather than propagate generalization weight.

```{r}
#| label: fig-f1-trait-network
#| fig-cap: "Semantic trait network (top 80 traits by connectivity). Nodes represent personality traits; edges represent adjacency in the semantic dependency network. Node size and color indicate degree centrality (number of connections). Force-directed layout (Fruchterman–Reingold). Trait labels omitted for clarity; the full adjacency matrix is available in the Open Materials."
#| fig-width: 8
#| fig-height: 7
#| eval: !expr file.exists(fig_path("fig01_trait_network.tiff"))
knitr::include_graphics(fig_path("fig01_trait_network.tiff"))
```

```{r}
#| label: fig-f1-trait-network-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig01_trait_network.tiff")))
cat("*[Figure F1 pending: run `Figures/make_figures.R` to generate.]*")
```

### Supplementary Materials G: Projection Rate (α) by Study and Condition

Figure G1 shows the distribution of individual-level projection slope (α) posterior medians from the pooled model, broken down by study and condition. In Study 2, α varied only modestly across conditions and no individual condition contrast reached significance after correction. In Study 3, α was similar in the Minority and Majority conditions (*p* = .532). This figure supplements the forest plot (@fig-forest-pooled) with individual-level distributions.

```{r}
#| label: fig-alpha-by-condition
#| fig-cap: "Projection rate (α) posterior medians from the pooled model by study and condition. Jitter shows individual participants; boxplot shows median and IQR. Colors match the color scheme used throughout (Study 1: blue; Study 2: orange=Negation, blue=High-Status, green=Low-Status; Study 3: pink=Minority, blue=Majority). Estimates from the three-level pooled model (Global → Study → Subject)."
#| fig-width: 12
#| fig-height: 4.5
#| eval: !expr file.exists(fig_path("fig_alpha_by_condition.tiff"))
knitr::include_graphics(fig_path("fig_alpha_by_condition.tiff"))
```

```{r}
#| label: fig-alpha-by-condition-placeholder
#| results: asis
#| echo: false
#| eval: !expr isFALSE(file.exists(fig_path("fig_alpha_by_condition.tiff")))
cat("*[Figure G1 pending: run `Figures/make_figures.R` to generate.]*")
```

### Supplementary Materials H: Regression Coefficients for Behavioral Models

For interpretability, the main text emphasizes estimated marginal means and average marginal effects. The tables below report the corresponding fixed-effect coefficients for the reported behavioral models and the coefficient tables for the reported condition-level parameter comparisons.

```{r}
#| results: asis
#| echo: false
s1_coef_path <- here("Results", "study_1_behavioral_model_coefficients.csv")
if (file.exists(s1_coef_path)) {
  x <- read.csv(s1_coef_path)
  x$estimate <- round(x$estimate, 3)
  x$std_error <- round(x$std_error, 3)
  x$statistic <- round(x$statistic, 2)
  x$p_value <- ifelse(x$p_value < .001, "< .001", sprintf("%.3f", x$p_value))
  knitr::kable(
    x,
    col.names = c("Study", "Model", "Model Label", "Term", "b", "SE", "z", "p"),
    caption = "Table H1. Study 1 Fixed-Effect Coefficients for Behavioral Models."
  )
} else {
  cat("*[Table H1 pending: run `Rscript Scripts/export_behavioral_coefficients.R` to generate.]*")
}
```

```{r}
#| results: asis
#| echo: false
s2_coef_path <- here("Results", "study_2_behavioral_model_coefficients.csv")
if (file.exists(s2_coef_path)) {
  x <- read.csv(s2_coef_path)
  x$estimate <- round(x$estimate, 3)
  x$std_error <- round(x$std_error, 3)
  x$statistic <- round(x$statistic, 2)
  x$p_value <- ifelse(x$p_value < .001, "< .001", sprintf("%.3f", x$p_value))
  knitr::kable(
    x,
    col.names = c("Study", "Model", "Model Label", "Term", "b", "SE", "z", "p"),
    caption = "Table H2. Study 2 Fixed-Effect Coefficients for Behavioral Models."
  )
} else {
  cat("*[Table H2 pending: run `Rscript Scripts/export_behavioral_coefficients.R` to generate.]*")
}
```

```{r}
#| results: asis
#| echo: false
s3_coef_path <- here("Results", "study_3_behavioral_model_coefficients.csv")
if (file.exists(s3_coef_path)) {
  x <- read.csv(s3_coef_path)
  x$estimate <- round(x$estimate, 3)
  x$std_error <- round(x$std_error, 3)
  x$statistic <- round(x$statistic, 2)
  x$p_value <- ifelse(x$p_value < .001, "< .001", sprintf("%.3f", x$p_value))
  knitr::kable(
    x,
    col.names = c("Study", "Model", "Model Label", "Term", "b", "SE", "z", "p"),
    caption = "Table H3. Study 3 Fixed-Effect Coefficients for Behavioral Models."
  )
} else {
  cat("*[Table H3 pending: run `Rscript Scripts/export_behavioral_coefficients.R` to generate.]*")
}
```

```{r}
#| results: asis
#| echo: false
ss_mod_path <- here("Results", "ss_moderation_results.csv")
if (file.exists(ss_mod_path)) {
  x <- read.csv(ss_mod_path)
  names(x) <- c("Study", "Moderator", "Effect", "b", "SE", "z", "p")
  x$b <- round(x$b, 3)
  x$SE <- round(x$SE, 3)
  x$z <- round(x$z, 2)
  x$p <- ifelse(x$p < .001, "< .001", sprintf("%.3f", x$p))
  knitr::kable(
    x,
    caption = "Table H4. Exploratory Moderators of the Similarity-to-Self Effect on Ingroup Choice."
  )
} else {
  cat("*[Table H4 pending: required file `Results/ss_moderation_results.csv` not found.]*")
}
```

```{r}
#| results: asis
#| echo: false
s2_param_path <- here("Results", "param_by_condition_s2_lm.csv")
if (file.exists(s2_param_path)) {
  x <- read.csv(s2_param_path)
  x <- x[, c("param", "term", "Estimate", "Std..Error", "t.value", "Pr...t..", "F_stat", "p_F", "R2")]
  names(x) <- c("Parameter", "Term", "b", "SE", "t", "p", "F", "Model p", "R2")
  x$Parameter <- gsub("^m$", "Projection Rate", x$Parameter)
  x$Parameter <- gsub("^lambda$", "Generalization Sensitivity", x$Parameter)
  x$Parameter <- gsub("^bias$", "Ingroup Bias", x$Parameter)
  x$Parameter <- gsub("^subject_mcr$", "Metacontrast Ratio", x$Parameter)
  x$Parameter <- gsub("^delta_elpd$", "Per-Subject Delta ELPD", x$Parameter)
  x$Term <- gsub("^\\(Intercept\\)$", "Intercept", x$Term)
  x$Term <- gsub("^conditionHigh-Status$", "High-Status Outgroup (vs. negation)", x$Term)
  x$Term <- gsub("^conditionLow-Status$", "Low-Status Outgroup (vs. negation)", x$Term)
  x[, 3:9] <- lapply(x[, 3:9], function(v) round(v, 3))
  knitr::kable(
    x,
    caption = "Table H5. Study 2 Coefficients for Condition Differences in Model-Derived Parameters."
  )
} else {
  cat("*[Table H5 pending: required file `Results/param_by_condition_s2_lm.csv` not found.]*")
}
```

```{r}
#| results: asis
#| echo: false
s3_param_path <- here("Results", "param_by_condition_s3_lm.csv")
if (file.exists(s3_param_path)) {
  x <- read.csv(s3_param_path)
  x <- x[, c("param", "term", "Estimate", "Std..Error", "t.value", "Pr...t..", "F_stat", "p_F", "R2")]
  names(x) <- c("Parameter", "Term", "b", "SE", "t", "p", "F", "Model p", "R2")
  x$Parameter <- gsub("^m$", "Projection Rate", x$Parameter)
  x$Parameter <- gsub("^lambda$", "Generalization Sensitivity", x$Parameter)
  x$Parameter <- gsub("^bias$", "Ingroup Bias", x$Parameter)
  x$Parameter <- gsub("^subject_mcr$", "Metacontrast Ratio", x$Parameter)
  x$Parameter <- gsub("^delta_elpd$", "Per-Subject Delta ELPD", x$Parameter)
  x$Term <- gsub("^\\(Intercept\\)$", "Intercept", x$Term)
  x$Term <- gsub("^conditionMajority$", "Majority Outgroup Condition (vs. minority)", x$Term)
  x[, 3:9] <- lapply(x[, 3:9], function(v) round(v, 3))
  knitr::kable(
    x,
    caption = "Table H6. Study 3 Coefficients for Condition Differences in Model-Derived Parameters."
  )
} else {
  cat("*[Table H6 pending: required file `Results/param_by_condition_s3_lm.csv` not found.]*")
}
```

### Supplementary Materials I: Pooled Parameter and Individual-Difference Correlations

To clarify the pooled CCA, Table I1 reports pooled bivariate correlations between model-derived parameters and individual-difference measures after Z-scoring both sets of variables within study before pooling. This preserves the pooled analysis logic by isolating within-study individual differences rather than study-level mean shifts. Mechanism-personality correlations and model-preference correlations were false-discovery-rate corrected within their respective families.

```{r}
#| results: asis
#| echo: false
pooled_corr_path <- here("Results", "correlations_pooled_standardized.csv")
if (file.exists(pooled_corr_path)) {
  x <- read.csv(pooled_corr_path)
  x <- subset(x, family == "mechanism")
  x$Parameter <- x$param
  x$Parameter <- gsub("^m$", "Projection Rate", x$Parameter)
  x$Parameter <- gsub("^bias$", "Ingroup Bias", x$Parameter)
  x$Parameter <- gsub("^lambda$", "Generalization Sensitivity", x$Parameter)
  x$Parameter <- gsub("^subject_mcr$", "Metacontrast Ratio", x$Parameter)
  x$Scale <- x$scale
  x$Scale <- gsub("^DS$", "Dialectical Self-Views", x$Scale)
  x$Scale <- gsub("^Proto$", "Perceived Prototypicality", x$Scale)
  x$Scale <- gsub("^SCC$", "Self-Concept Clarity", x$Scale)
  x$Scale <- gsub("^SI$", "Social Identification", x$Scale)
  x$Scale <- gsub("^RSE$", "Self-Esteem", x$Scale)
  x$Scale <- gsub("^NTB$", "Need to Belong", x$Scale)
  x$Scale <- gsub("^NFC$", "Need for Cognition", x$Scale)
  x$Scale <- gsub("^SING\\.Ind$", "Independent Self-Construal", x$Scale)
  x$Scale <- gsub("^SING\\.Inter$", "Interdependent Self-Construal", x$Scale)
  x$p_raw <- ifelse(x$p_raw < .001, "< .001", sprintf("%.3f", x$p_raw))
  x$p_fdr <- ifelse(x$p_fdr < .001, "< .001", sprintf("%.3f", x$p_fdr))
  x <- x[, c("Parameter", "Scale", "r", "p_raw", "p_fdr", "n")]
  knitr::kable(
    x,
    col.names = c("Parameter", "Scale", "r", "p", "FDR p", "N"),
    caption = "Table I1. Pooled Within-Study-Standardized Correlations Between Model-Derived Parameters and Individual Differences."
  )
} else {
  cat("*[Table I1 pending: run `Rscript Pooled/pooled_param_indiff_correlations.R` to generate.]*")
}
```

### Supplementary Materials J: Schematic of the Model-Derived Metacontrast Ratio

Figure J1 illustrates how the model-derived MCR is constructed. Self-ratings are first transformed into projected ingroup and outgroup evidence through the projection-rate parameter, then weighted by semantic similarity through the generalization parameter. The trial-level metacontrast ratio is the ratio of accumulated ingroup to outgroup evidence, and the subject-level MCR is the average of that ratio across trials.

```{r}
#| label: fig-mcr-schematic
#| fig-cap: "Schematic of the model-derived Metacontrast Ratio (MCR). Self-ratings are transformed into projected ingroup and outgroup evidence, weighted by semantic similarity, converted to a trial-level metacontrast ratio, and then averaged across trials to yield the subject-level MCR."
#| fig-width: 10
#| fig-height: 3.8
library(ggplot2)

schem <- data.frame(
  xmin = c(0.0, 2.1, 4.2, 6.3, 8.4),
  xmax = c(1.6, 3.7, 5.8, 7.9, 10.0),
  ymin = c(0.2, 0.2, 0.2, 0.2, 0.2),
  ymax = c(0.8, 0.8, 0.8, 0.8, 0.8),
  lab = c(
    "Self-ratings\nE_t",
    "Projection\nG_t = logit^-1(alpha[E_t - 4])",
    "Similarity weighting\nS_tg^lambda",
    "Trial-level ratio\nMCR_t = simW_in / simW_out",
    "Subject-level MCR\nmean_t(MCR_t)"
  )
)

arrows <- data.frame(
  x = c(1.6, 3.7, 5.8, 7.9),
  xend = c(2.1, 4.2, 6.3, 8.4),
  y = c(0.5, 0.5, 0.5, 0.5),
  yend = c(0.5, 0.5, 0.5, 0.5)
)

ggplot() +
  geom_rect(
    data = schem,
    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
    fill = c("#DCEAF4", "#E5F0E8", "#F7ECD7", "#F8E0D6", "#E8E0F3"),
    color = "black",
    linewidth = 0.4
  ) +
  geom_segment(
    data = arrows,
    aes(x = x, xend = xend, y = y, yend = yend),
    arrow = grid::arrow(length = grid::unit(0.18, "cm"), type = "closed"),
    linewidth = 0.5
  ) +
  geom_text(
    data = schem,
    aes(x = (xmin + xmax) / 2, y = 0.5, label = lab),
    size = 3.2,
    lineheight = 0.95
  ) +
  annotate("text", x = 5.0, y = 0.05,
           label = "simW_in = sum(S_tg^lambda * G_t);   simW_out = sum(S_tg^lambda * [1 - G_t])",
           size = 3.1) +
  coord_cartesian(xlim = c(-0.1, 10.2), ylim = c(0, 1), clip = "off") +
  theme_void()
```

### Supplementary Materials K: Trait Segregation Analyses

We developed a network-based measure of trait segregation — network nominal homophily — to quantify whether participants' ingroup versus outgroup classifications cluster along the semantic similarity structure. Formally, this is the correlation between trait similarity and same-group assignment: high segregation indicates that semantically proximal traits received the same group label, producing spatially coherent ingroup and outgroup neighborhoods; low segregation indicates that group labels were distributed without regard for semantic structure.

**Study 1.** Trait segregation across the full Study 1 sample was *M* = .09 (*SD* = .08; range [−.04, .26]).

**Study 2.** Trait segregation differed across outgroup conditions, *F*(2, 176) = 14.75, *p* < .001. High-status contrast participants showed higher segregation (*M* = .11, *SD* = .08) than both negation (*M* = .04, *SD* = .05; *t*(176) = 4.92, *p* < .001) and low-status (*M* = .05, *SD* = .07; *t*(176) = 0.37, *p* = .710) participants. Notably, the high-status condition also produced the strongest behavioral self-anchoring effect (AME = .100), indicating that higher trait segregation co-occurs here with stronger — not weaker — similarity-based projection. This dissociation suggests that a positively-regarded, high-status outgroup simultaneously sharpens semantic boundary formation and heightens reliance on self-knowledge for classification, perhaps because participants more carefully organize the trait space when the outgroup is clearly differentiated in status.

**Study 3.** Minority contrast participants showed higher segregation (*M* = .12, *SD* = .08) than majority contrast participants (*M* = .08, *SD* = .07; *t*(249) = −4.32, *p* < .001). Unlike Study 2 where high segregation accompanied high self-projection, here high segregation in the minority condition co-occurs with absent similarity-to-self effects (AME ≈ 0). This difference across studies cautions against a simple "high segregation = disrupted self-anchoring" interpretation: segregation captures whether classifications are semantically structured, but the motivational basis for that structure differs by context. In Study 2, the high-status context sharpens both boundary formation and self-referential inference; in Study 3, the minority-contrast context produces rigid categorical partitioning in the absence of self-anchoring, consistent with the shared subordinate status account.

### Supplementary Materials L: Reporting Convention and the Grand Mean Approach

We report group-level parameter estimates as the arithmetic mean of individual-level posterior medians (grand means) unless otherwise specified. While it is common in Bayesian hierarchical modeling to report back-transformed hyperparameters ($\Phi(\mu_{pr})$), these represent the *median* of the group distribution. For non-linearly transformed parameters with large between-subject variance — most notably the projection slope $\alpha$ — the group median is systematically lower than the sample average due to the right-skew of the probit-transformed distribution (a manifestation of Jensen's inequality). We prioritize grand means throughout the manuscript to ensure descriptive consistency between group-level tables and condition-level visualizations, as the latter necessarily reflect the distribution of actual participant estimates.

## OPEN MATERIALS

Analysis scripts, Stan model code, and de-identified data are available at https://github.com/JacobElder/SelfAnchoring. An interactive web supplement demonstrating the Symmetric + λ and Asymmetric + λ model architectures is available at https://jacobelder.shinyapps.io/SelfAnchoring/. The supplement allows readers to manipulate model parameters and resample training-trait configurations in real time. Setting γ = 0.50 isolates the core self-anchoring mechanism — no baseline ingroup preference — so that the classification curve reflects only the similarity-weighted self-concept signal. The pooled global posterior medians (α = 0.32, γ = 0.49, λ = 3.3) are loaded by default.

## REFERENCES

Adler, N. E., Boyce, T., Chesney, M. A., Cohen, S., Folkman, S., Kahn, R. L., & Syme,
S. L. (1994). Socioeconomic status and health: The challenge of the gradient.
*American Psychologist*, *49*, 15–24. https://doi.org/10.1037/0003-066X.49.1.15

Ahn, W.-Y., Haines, N., & Zhang, L. (2017). Revealing neurocomputational
mechanisms of reinforcement learning and decision-making with the
hBayesDM package. *Computational Psychiatry*, *1*, 24–57.
https://doi.org/10.1162/CPSY_a_00002

Ahn, W.-Y., Krawitz, A., Kim, W., Busmeyer, J. R., & Brown, J. W. (2011). A model-based fMRI analysis with hierarchical Bayesian parameter estimation. *Journal of Neuroscience, Psychology, and Economics*, *4*(2), 95–110.
https://doi.org/10.1037/a0020684

Ames, D. R. (2004). Inside the mind reader's tool kit: Projection and stereotyping in
mental state inference. *Journal of Personality and Social Psychology*, *87*(3), 340–353. https://doi.org/10.1037/0022-3514.87.3.340

Arel-Bundock, V. (2026). *marginaleffects: Predictions, comparisons, slopes, marginal means, and hypothesis tests* (R package version 0.32.0). https://marginaleffects.com/

Baayen, R. H., Davidson, D. J., & Bates, D. M. (2008). Mixed-effects modeling with
crossed random effects for subjects and items. *Journal of Memory and Language*,
*59*(4), 390–412. https://doi.org/10.1016/j.jml.2007.12.005

Bafumi, J., & Gelman, A. (2007). *Fitting multilevel models when predictors and group
effects correlate* (SSRN Scholarly Paper No. 1010095).
https://doi.org/10.2139/ssrn.1010095

Balliet, D., Wu, J., & De Dreu, C. K. W. (2014). Ingroup favoritism in cooperation: A
meta-analysis. *Psychological Bulletin*, *140*, 1556–1581.
https://doi.org/10.1037/a0037737

Barr, D. J., Levy, R., Scheepers, C., & Tily, H. J. (2013). Random effects structure for
confirmatory hypothesis testing: Keep it maximal. *Journal of Memory and
Language*, *68*(3). https://doi.org/10.1016/j.jml.2012.11.001

Baumeister, R. F., & Leary, M. R. (1995). The need to belong: Desire for interpersonal
attachments as a fundamental human motivation. *Psychological Bulletin*, *117*,
497–529. https://doi.org/10.1037/0033-2909.117.3.497

Bianchi, M., Machunsky, M., Steffens, M. C., & Mummendey, A. (2009). Like me or
like us: Is ingroup projection just social projection? *Experimental Psychology*, *56*,
198–205. https://doi.org/10.1027/1618-3169.56.3.198

Blake, K. R., & Gangestad, S. (2020). On attenuated interactions, measurement error, and
statistical power: Guidelines for social and personality psychologists. *Personality
and Social Psychology Bulletin*, *46*, 1702–1711.
https://doi.org/10.1177/0146167220913363

Bowman, C. R., Iwashita, T., & Zeithamova, D. (2020). Tracking prototype and exemplar
representations in the brain across learning. *ELife*, *9*, e59360.
https://doi.org/10.7554/eLife.59360

Brewer, M. B. (1991). The social self: On being the same and different at the same time.
*Personality and Social Psychology Bulletin*, *17*(5), 475–482.

Brewer, M. B. (1993). Social identity, distinctiveness, and in-group homogeneity. *Social
Cognition*, *11*, 150–164. https://doi.org/10.1521/soco.1993.11.1.150

Brewer, M. B. (1999). The psychology of prejudice: Ingroup love and outgroup hate?
*Journal of Social Issues*, *55*(3), 429–444. https://doi.org/10.1111/0022-4537.00126

Brown, R. (2000). Social identity theory: Past achievements, current problems and future
challenges. *European Journal of Social Psychology*, *30*(6), 745–778.
https://doi.org/10.1002/1099-0992(200011/12)30:6<745::AID-EJSP24>3.0.CO;2-O

Brown, R. J. (1984). The role of similarity in intergroup relations. In H. Tajfel (Ed.), *The
social dimension: European developments in social psychology* (Vol. 2, pp.
603–623). Cambridge University Press.
https://doi.org/10.1017/CBO9780511759154.012

Cacioppo, J. T., & Petty, R. E. (1982). The need for cognition. *Journal of Personality and
Social Psychology*, *42*(1), 116–131.

Cadinu, M., Carnaghi, A., & Guizzo, F. (2020). Group meaningfulness and the causal
direction of influence between the ingroup and the self or another individual:
Evidence from the induction-deduction paradigm. *PLoS ONE*, *15*(3), e0229321.
https://doi.org/10.1371/journal.pone.0229321

Cadinu, M., & De Amicis, L. (1999). The relationship between the self and the ingroup:
When having a common conception helps. *Swiss Journal of Psychology*, *58*,
226–232. https://doi.org/10.1024/1421-0185.58.4.226

Cadinu, M., Latrofa, M., & Carnaghi, A. (2013). Comparing self-stereotyping with
ingroup-stereotyping and out-group-stereotyping in unequal-status groups: The
case of gender. *Self and Identity*, *12*(6), 582–596.
https://doi.org/10.1080/15298868.2012.712753

Cadinu, M., & Rothbart, M. (1996). Self-anchoring and differentiation processes in the
minimal group setting. *Journal of Personality and Social Psychology*, *70*, 661–677. https://doi.org/10.1037/0022-3514.70.4.661

Campbell, D. T. (1958). Common fate, similarity, and other indices of the status of
aggregates of persons as social entities. *Behavioral Science*, *3*(1), 14–25.
https://doi.org/10.1002/bs.3830030103

Campbell, J. D., Trapnell, P. D., Heine, S. J., Katz, I. M., Lavallee, L. F., & Lehman, D.
R. (1996). Self-concept clarity: Measurement, personality correlates, and cultural
boundaries. *Journal of Personality and Social Psychology*, *70*(1), 141–156.
https://doi.org/10.1037/0022-3514.70.1.141

Clement, R. W., & Krueger, J. (2000). The primacy of self-referent information in
perceptions of social consensus. *British Journal of Social Psychology*, *39*, 279–299. https://doi.org/10.1348/014466600164471

Clement, R. W., & Krueger, J. (2002). Social categorization moderates social
projection. *Journal of Experimental Social Psychology*, *38*(3), 219–231.
https://doi.org/10.1006/jesp.2001.1503

Coats, S., Smith, E. R., Claypool, H. M., & Banner, M. J. (2000). Overlapping mental
representations of self and in-group: Reaction time evidence and its relationship
with explicit measures of group identification. *Journal of Experimental Social
Psychology*, *36*, 304–315. https://doi.org/10.1006/jesp.1999.1416

Davis, T., & Goldwater, M. (2021). Using model-based neuroimaging to adjudicate
structured and continuous representational accounts in same-different
categorization and beyond. *Current Opinion in Behavioral Sciences*, *37*, 103–108.
https://doi.org/10.1016/j.cobeha.2020.11.011

Davis, T., & Love, B. C. (2010). Memory for category information is idealized through
contrast with competing options. *Psychological Science*, *21*(2), 234–242.
https://doi.org/10.1177/0956797609357712

Davis, T., Love, B. C., & Preston, A. R. (2012a). Striatal and hippocampal entropy and
recognition signals in category learning: Simultaneous processes revealed by
model-based fMRI. *Journal of Experimental Psychology: Learning, Memory, and
Cognition*, *38*(4), 821–839. https://doi.org/10.1037/a0027865

Davis, T., Love, B. C., & Preston, A. R. (2012b). Learning the exception to the rule:
Model-based fMRI reveals specialized representations for surprising category
members. *Cerebral Cortex*, *22*(2), 260–273.
https://doi.org/10.1093/cercor/bhr036

Daw, N. D. (2011). Trial-by-trial data analysis using computational models. In
*Decision making, affect, and learning: Attention and performance XXIII* (Vol. 23).
Oxford University Press.

Dawes, R. M. (1989). Statistical criteria for establishing a truly false consensus effect. *Journal of Experimental Social Psychology*, *25*(1), 1–17.
https://doi.org/10.1016/0022-1031(89)90036-0

de la Haye, A.-M. (2000). A methodological note about the measurement of the false-consensus effect. *European Journal of Social Psychology*, *30*(4), 569–581.
https://doi.org/10.1002/1099-0992(200007/08)30:4<569::AID-EJSP8>3.0.CO;2-V

DiDonato, T. E., Ullrich, J., & Krueger, J. I. (2011). Social perception as induction and
inference: An integrative model of intergroup differentiation, ingroup favoritism,
and differential accuracy. *Journal of Personality and Social Psychology*, *100*, 66–83. https://doi.org/10.1037/a0021051

Don, H. J., Otto, A. R., Cornwall, A. C., Davis, T., & Worthy, D. A. (2019). Learning
reward frequency over reward probability: A tale of two learning rules. *Cognition*,
*193*, 104042. https://doi.org/10.1016/j.cognition.2019.104042

Don, H. J., & Worthy, D. A. (2022). Frequency effects in action versus value learning.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *48*,
1311–1327. https://doi.org/10.1037/xlm0000896

Doosje, B., Ellemers, N., & Spears, R. (1995). Perceived intragroup variability as a
function of group status and identification. *Journal of Experimental Social
Psychology*, *31*(5), 410–436. https://doi.org/10.1006/jesp.1995.1018

Eager, C., & Roy, J. (2017). *Mixed effects models are sometimes terrible*
(arXiv:1701.04858). arXiv. https://doi.org/10.48550/arXiv.1701.04858

Elder, J., Cheung, B., Davis, T., & Hughes, B. (2023). Mapping the self: A network
approach for understanding psychological and neural representations of self-concept structure. *Journal of Personality and Social Psychology*, *124*(2), 237–263. https://doi.org/10.1037/pspa0000315

Elder, J., Davis, T. H., & Hughes, B. L. (2023). A fluid self-concept: How the brain
maintains coherence and positivity across an interconnected self-concept while
incorporating social feedback. *Journal of Neuroscience*.
https://doi.org/10.1523/JNEUROSCI.1951-22.2023

Elder, J., Davis, T., & Hughes, B. (2022a). Self-concept certainty and stability are
associated with semantic relations between self-beliefs. *PsyArXiv*.
https://doi.org/10.31234/osf.io/8y2vr

Elder, J., Davis, T., & Hughes, B. (2022b). Self-derogating to align with group norms:
Similarity-based learning drives assimilation of the group to the self. *PsyArXiv*.
https://doi.org/10.31234/osf.io/38bf7

Elder, J., Davis, T., & Hughes, B. L. (2022c). Learning about the self: Motives for
coherence and positivity constrain learning from self-relevant social feedback.
*Psychological Science*, *33*(4), 629–647.
https://doi.org/10.1177/09567976211045934

Ellemers, N., Spears, R., & Doosje, B. (2001). Self and social identity. *Annual Review of Psychology*, *53*, 161–186.

Estes, W. K. (1976). The cognitive side of probability learning. *Psychological Review*,
*83*, 37–64. https://doi.org/10.1037/0033-295X.83.1.37

FeldmanHall, O., & Shenhav, A. (2019). Resolving uncertainty in a social world. *Nature
Human Behaviour*, *3*(5), 426–435. https://doi.org/10.1038/s41562-019-0590-x

Fielding, K. S., & Hogg, M. A. (1997). Social identity, self-categorization, and
leadership: A field study of small interactive groups. *Group Dynamics: Theory,
Research, and Practice*, *1*(1), 39–51. https://doi.org/10.1037/1089-2699.1.1.39

Fiske, S. T., Dupree, C. H., Nicolas, G., & Swencionis, J. K. (2016). Status, power, and
intergroup relations: The personal is the societal. *Current Opinion in Psychology*,
*11*, 44–48. https://doi.org/10.1016/j.copsyc.2016.05.012

Gaertner, S. L., Dovidio, J. F., Guerra, R., Hehman, E., & Saguy, T. (2016). A common
ingroup identity: Categorization, identity, and intergroup relations. In *Handbook of prejudice, stereotyping, and discrimination* (2nd ed., pp. 433–454). Psychology
Press. https://doi.org/10.4324/9781841697772

Goldstone, R. L., Medin, D. L., & Gentner, D. (1991). Relational similarity and the
nonindependence of features in similarity judgments. *Cognitive Psychology*,
*23*(2), 222–262. https://doi.org/10.1016/0010-0285(91)90010-L

Gramzow, R. H., & Gaertner, L. (2005). Self-esteem and favoritism toward novel in-groups: The self as an evaluative base. *Journal of Personality and Social
Psychology*, *88*(5), 801–815. https://doi.org/10.1037/0022-3514.88.5.801

Gramzow, R. H., Gaertner, L., & Sedikides, C. (2001). Memory for in-group and out-group information in a minimal group context: The self as an informational base.
*Journal of Personality and Social Psychology*, *80*(2), 188–205.
https://doi.org/10.1037/0022-3514.80.2.188

Green, P., & MacLeod, C. J. (2016). SIMR: An R package for power analysis of
generalized linear mixed models by simulation. *Methods in Ecology and
Evolution*, *7*(4), 493–498. https://doi.org/10.1111/2041-210X.12504

Griffiths, T. L., Steyvers, M., & Tenenbaum, J. B. (2007). Topics in semantic
representation. *Psychological Review*, *114*, 211–244.
https://doi.org/10.1037/0033-295X.114.2.211

Guest, O., & Martin, A. E. (2021). How computational modeling can force theory
building in psychological science. *Perspectives on Psychological Science*, *16*(4),
789–802. https://doi.org/10.1177/1745691620970585

Guillaume, J. H. A., Jakeman, J. D., Marsili-Libelli, S., Asher, M., Brunner, P., Croke,
B., Hill, M. C., Jakeman, A. J., Keesman, K. J., Razavi, S., & Stigter, J. D.
(2019). Introductory overview of identifiability analysis: A guide to evaluating
whether you have the right type of data for your modeling purpose.
*Environmental Modelling & Software*, *119*, 418–432.
https://doi.org/10.1016/j.envsoft.2019.07.007

Haslam, S. A., Oakes, P. J., Turner, J. C., & McGarty, C. (1995). Social categorization
and group homogeneity: Changes in the perceived applicability of stereotype
content as a function of comparative context and trait favourableness. *British
Journal of Social Psychology*, *34*(2), 139–160. https://doi.org/10.1111/j.2044-8309.1995.tb01054.x

Heit, E., & Rubinstein, J. (1994). Similarity and property effects in inductive reasoning.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *20*(2),
411–422. https://doi.org/10.1037/0278-7393.20.2.411

Hewstone, M., Rubin, M., & Willis, H. (2002). Intergroup bias. *Annual Review of
Psychology*, *53*, 575–604.
https://doi.org/10.1146/annurev.psych.53.100901.135109

Hirsh, J. B., Mar, R. A., & Peterson, J. B. (2012). Psychological entropy: A framework
for understanding uncertainty-related anxiety. *Psychological Review*, *119*(2),
304–320. https://doi.org/10.1037/a0026767

Hogg, M. A. (2007). Uncertainty-identity theory. In *Advances in experimental social
psychology* (Vol. 39, pp. 69–126). Elsevier Academic Press.
https://doi.org/10.1016/S0065-2601(06)39002-8

Hogg, M. A. (2014). From uncertainty to extremism: Social categorization and identity
processes. *Current Directions in Psychological Science*, *23*(5), 338–342.
https://doi.org/10.1177/0963721414540168

Hogg, M. A., & Abrams, D. (1988). *Social identifications: A social psychology of
intergroup relations and group processes*. Routledge.

Hogg, M. A., Abrams, D., Otten, S., & Hinkle, S. (2004). The social identity
perspective: Intergroup relations, self-conception, and small groups. *Small Group
Research*, *35*(3), 246–276. https://doi.org/10.1177/1046496404263424

Hogg, M. A., & Hains, S. C. (1996). Intergroup relations and group solidarity: Effects of
group identification and social beliefs on depersonalized attraction. *Journal of
Personality and Social Psychology*, *70*(2), 295–309. https://doi.org/10.1037/0022-3514.70.2.295

Hogg, M. A., Hardie, E. A., & Reynolds, K. J. (1995). Prototypical similarity, self-categorization, and depersonalized attraction: A perspective on group
cohesiveness. *European Journal of Social Psychology*, *25*(2), 159–177.
https://doi.org/10.1002/ejsp.2420250204

Hong, Y., & Ratner, K. G. (2021). Minimal but not meaningless: Seemingly arbitrary
category labels can imply more than group membership. *Journal of Personality
and Social Psychology*, *120*(3), 576–600. https://doi.org/10.1037/pspa0000255

Hornsey, M. J., & Hogg, M. A. (1999). Subgroup differentiation as a response to an
overly-inclusive group: A test of optimal distinctiveness theory. *European
Journal of Social Psychology*, *29*, 543–550.

Hornsey, M. J., & Hogg, M. A. (2000). Assimilation and diversity: An integrative model
of subgroup relations. *Personality and Social Psychology Review*, *4*, 143–156.
https://doi.org/10.1207/S15327957PSPR0402_03

Huys, Q. J. M., Cools, R., Gölzer, M., Friedel, E., Heinz, A., Dolan, R. J., & Dayan, P.
(2011). Disentangling the roles of approach, activation and valence in
instrumental and Pavlovian responding. *PLOS Computational Biology*, *7*(4),
e1002028. https://doi.org/10.1371/journal.pcbi.1002028

Iyengar, S., Lelkes, Y., Levendusky, M., Malhotra, N., & Westwood, S. J. (2019). The
origins and consequences of affective polarization in the United States. *Annual
Review of Political Science*, *22*(1), 129–146. https://doi.org/10.1146/annurev-polisci-051117-073034

James, W. (1890). *The principles of psychology* (Vol. 1). Henry Holt and Co.
https://doi.org/10.1037/10538-000

Jost, J. T., & Banaji, M. R. (1994). The role of stereotyping in system-justification and
the production of false consciousness. *British Journal of Social Psychology*,
*33*(1), 1–27. https://doi.org/10.1111/j.2044-8309.1994.tb01008.x

Judd, C. M., Westfall, J., & Kenny, D. A. (2012). Treating stimuli as a random factor in
social psychology: A new and comprehensive solution to a pervasive but largely
ignored problem. *Journal of Personality and Social Psychology*, *103*(1), 54–69.
https://doi.org/10.1037/a0028347

Krueger, J. (2007). From social projection to social behaviour. *European Review of
Social Psychology*, *18*(1), 1–35. https://doi.org/10.1080/10463280701284645

Krueger, J., & Clement, R. W. (1994). The truly false consensus effect: An ineradicable
and egocentric bias in social perception. *Journal of Personality and Social
Psychology*, *67*, 596–610. https://doi.org/10.1037/0022-3514.67.4.596

Krueger, J., & Clement, R. W. (1996). Inferring category characteristics from sample
characteristics: Inductive reasoning and social projection. *Journal of
Experimental Psychology: General*, *125*(1), 52–68.

Kubinec, R. (2022). Ordered beta regression: A parsimonious, well-fitting model for
continuous data with lower and upper bounds. *Political Analysis*, *31*, 519–536. https://doi.org/10.1017/pan.2022.20

Lakens, D., Scheel, A. M., & Isager, P. M. (2018). Equivalence testing for psychological
research: A tutorial. *Advances in Methods and Practices in Psychological
Science*, *1*(2), 259–269. https://doi.org/10.1177/2515245918770963

Latrofa, M., Vaes, J., & Cadinu, M. (2012). Self-stereotyping: The central role of an
ingroup threatening identity. *The Journal of Social Psychology*, *152*(1), 92–111.
https://doi.org/10.1080/00224545.2011.565382

Latrofa, M., Vaes, J., Pastore, M., & Cadinu, M. (2009). "United we stand, divided we
fall"! The protective function of self-stereotyping for stigmatised members'
psychological well-being. *Applied Psychology: An International Review*, *58*(1),
84–104. https://doi.org/10.1111/j.1464-0597.2008.00383.x

Leach, C. W., van Zomeren, M., Zebel, S., Vliek, M. L. W., Pennekamp, S. F., Doosje,
B., Ouwerkerk, J. W., & Spears, R. (2008). Group-level self-definition and self-investment: A hierarchical (multicomponent) model of in-group identification.
*Journal of Personality and Social Psychology*, *95*(1), 144–165.
https://doi.org/10.1037/0022-3514.95.1.144

Leary, M. R., Kelly, K. M., Cottrell, C. A., & Schreindorfer, L. S. (2013). Construct
validity of the need to belong scale: Mapping the nomological network.
*Journal of Personality Assessment*, *95*(6), 610–624.
https://doi.org/10.1080/00223891.2013.819511

Lelkes, Y., & Westwood, S. J. (2017). The limits of partisan prejudice. *The Journal of
Politics*, *79*(2), 485–501. https://doi.org/10.1086/688223

Lenth, R. V. (2026). *emmeans: Estimated marginal means, aka least-squares means* (R package version 2.0.0). https://cran.r-project.org/package=emmeans

Leonardelli, G. J., Pickett, C. L., & Brewer, M. B. (2010). Optimal distinctiveness theory:
A framework for social identity, social cognition, and intergroup relations. In
*Advances in experimental social psychology* (Vol. 43, pp. 63–113). Elsevier.

Lüdecke, D., Ben-Shachar, M. S., Patil, I., Waggoner, P., & Makowski, D. (2021).
performance: An R package for assessment, comparison and testing of
statistical models. *Journal of Open Source Software*, *6*(60), 3139.
https://doi.org/10.21105/joss.03139

Luhtanen, R., & Crocker, J. (1992). A collective self-esteem scale: Self-evaluation of
one's social identity. *Personality and Social Psychology Bulletin*, *18*(3), 302–318. https://doi.org/10.1177/0146167292183006

Maddox, W. T., & Ashby, F. G. (1993). Comparing decision bound and exemplar models
of categorization. *Perception & Psychophysics*, *53*(1), 49–70.
https://doi.org/10.3758/BF03211715

Makowski, D., Ben-Shachar, M. S., Chen, S. H. A., & Lüdecke, D. (2019). Indices of
effect existence and significance in the Bayesian framework. *Frontiers in
Psychology*, *10*, 2767. https://doi.org/10.3389/fpsyg.2019.02767

Markus, H., & Wurf, E. (1987). The dynamic self-concept: A social psychological
perspective. *Annual Review of Psychology*, *38*, 299–337.
https://doi.org/10.1146/annurev.ps.38.020187.001503

Mullen, B. (1991). Group composition, salience, and cognitive representations: The
phenomenology of being in a group. *Journal of Experimental Social Psychology*,
*27*, 297–323. https://doi.org/10.1016/0022-1031(91)90028-5

Murayama, K., Usami, S., & Sakaki, M. (2022). Summary-statistics-based power
analysis: A new and practical method to determine sample size for mixed-effects
modeling. *Psychological Methods*. https://doi.org/10.1037/met0000330

Nelson, L. J., & Miller, D. T. (1995). The distinctiveness effect in social categorization:
You are what makes you unusual. *Psychological Science*, *6*, 246–249.
https://doi.org/10.1111/j.1467-9280.1995.tb00600.x

Nicenboim, B., & Vasishth, S. (2016). Statistical methods for linguistic research:
Foundational ideas—Part II. *Language and Linguistics Compass*, *10*(11), 591–613. https://doi.org/10.1111/lnc3.12207

Nosofsky, R. M. (1984). Choice, similarity, and the context theory of classification.
*Journal of Experimental Psychology: Learning, Memory, and Cognition*, *10*, 104–114. https://doi.org/10.1037/0278-7393.10.1.104

Nosofsky, R. M. (1986). Attention, similarity, and the identification–categorization
relationship. *Journal of Experimental Psychology: General*, *115*(1), 39–57.
https://doi.org/10.1037/0096-3445.115.1.39

Nosofsky, R. M. (1988). Similarity, frequency, and category representations. *Journal of
Experimental Psychology: Learning, Memory, and Cognition*, *14*(1), 54–65.
https://doi.org/10.1037/0278-7393.14.1.54

Nosofsky, R. M. (1991). Typicality in logically defined categories: Exemplar-similarity
versus rule instantiation. *Memory & Cognition*, *19*(2), 131–150.
https://doi.org/10.3758/BF03197110

Nosofsky, R. M. (2011). The generalized context model: An exemplar model of
classification. In A. J. Wills & E. M. Pothos (Eds.), *Formal approaches in
categorization* (pp. 18–39). Cambridge University Press.
https://doi.org/10.1017/CBO9780511921322.002

Obst, P., White, K., Mavor, K., & Baker, R. (2011). Social identification dimensions as
mediators of the effect of prototypicality on intergroup behaviours. *Psychology*,
*2*, 265–269. https://doi.org/10.4236/psych.2011.25066

Otten, S. (2003). "Me and us" or "us and them"? The self as a heuristic for defining
minimal ingroups. *European Review of Social Psychology*, *13*(1), 1–33.
https://doi.org/10.1080/10463280240000028

Otten, S. (2004). Self-anchoring as predictor of in-group favoritism: Is it applicable to
real group contexts? *Current Psychology of Cognition*, *22*(4/5), 427–444.

Otten, S., & Epstude, K. (2006). Overlapping mental representations of self, ingroup, and
outgroup: Unraveling self-stereotyping and self-anchoring. *Personality & Social
Psychology Bulletin*, *32*(7), 957–969. https://doi.org/10.1177/0146167206287254

Otten, S., & Wentura, D. (2001). Self-anchoring and in-group favoritism: An individual
profiles analysis. *Journal of Experimental Social Psychology*, *37*(6), 525–532.
https://doi.org/10.1006/jesp.2001.1479

Postmes, T., Haslam, S. A., & Jans, L. (2013). A single-item measure of social
identification: Reliability, validity, and utility. *British Journal of Social
Psychology*, *52*(4), 597–617. https://doi.org/10.1111/bjso.12006

Rabinovich, A., & Morton, T. A. (2011). Subgroup identities as a key to cooperation
within large social groups. *British Journal of Social Psychology*, *50*(1), 36–51.
https://doi.org/10.1348/014466610X486356

Riketta, M., & Sacramento, C. A. (2008). "They cooperate with us, so they are like me":
Perceived intergroup relationship moderates projection from self to outgroups.
*Group Processes & Intergroup Relations*, *11*(1), 115–131.
https://doi.org/10.1177/1368430207084849

Robinaugh, D. J., Haslbeck, J. M. B., Ryan, O., Fried, E. I., & Waldorp, L. J. (2021).
Invisible hands and fine calipers: A call to use formal theory as a toolkit for
theory construction. *Perspectives on Psychological Science*, *16*(4), 725–743.
https://doi.org/10.1177/1745691620974697

Rosch, E., & Lloyd, B. B. (1978). *Principles of categorization*. Lawrence Erlbaum Associates.

Rosenberg, M. (1965). *Society and the adolescent self-image*. Princeton University Press.

Roth, J., Steffens, M. C., & Vignoles, V. L. (2018). Group membership, group change,
and intergroup attitudes: A recategorization model based on cognitive
consistency principles. *Frontiers in Psychology*, *9*, 479.
https://doi.org/10.3389/fpsyg.2018.00479

Schneider, M. J., Rubin-McGregor, J., Elder, J., Hughes, B., & Tamir, D. (2022).
Simulation requires activation of self-knowledge to change self-concept.
*PsyArXiv*. https://doi.org/10.31234/osf.io/92mru

Schubert, T. W., & Otten, S. (2002). Overlap of self, ingroup, and outgroup: Pictorial
measures of self-categorization. *Self and Identity*, *1*, 353–376.
https://doi.org/10.1080/152988602760328012

Shannon, C. E. (1948). A mathematical theory of communication. *Bell System
Technical Journal*, *27*(3), 379–423. https://doi.org/10.1002/j.1538-7305.1948.tb01338.x

Shepard, R. N. (1987). Toward a universal law of generalization for psychological
science. *Science*, *237*(4820), 1317–1323. https://doi.org/10.1126/science.3629243

Sherman, D. K., & Kim, H. S. (2005). Is there an "I" in "team"? The role of the self in
group-serving judgments. *Journal of Personality and Social Psychology*, *88*,
108–120. https://doi.org/10.1037/0022-3514.88.1.108

Simon, B., & Brown, R. (1987). Perceived intragroup homogeneity in minority-majority
contexts. *Journal of Personality and Social Psychology*, *53*, 703–711.
https://doi.org/10.1037/0022-3514.53.4.703

Smith, E. R., & Henry, S. (1996). An in-group becomes part of the self: Response time
evidence. *Personality and Social Psychology Bulletin*, *22*, 635–642.
https://doi.org/10.1177/0146167296226008

Sorensen, T., Hohenstein, S., & Vasishth, S. (2016). Bayesian linear mixed models using
Stan: A tutorial for psychologists, linguists, and cognitive scientists. *The
Quantitative Methods for Psychology*, *12*(3), 175–200.
https://doi.org/10.20982/tqmp.12.3.p175

Spears, R., Doosje, B., & Ellemers, N. (1997). Self-stereotyping in the face of threats to
group status and distinctiveness: The role of group identification. *Personality
and Social Psychology Bulletin*, *23*(5), 538–553.
https://doi.org/10.1177/0146167297235009

Spencer-Rodgers, J., Srivastava, S., Boucher, H. C., English, T., Paletz, S. B., & Peng, K.
(2015). *The dialectical self scale*. Unpublished manuscript.
https://doi.org/10.13140/RG.2.1.3695.5928

Tajfel, H. (1974). Social identity and intergroup behaviour. *Social Science Information*,
*13*(2), 65–93. https://doi.org/10.1177/053901847401300204

Tajfel, H. (1978). *Differentiation between social groups: Studies in the social psychology
of intergroup relations*. Academic Press.

Tajfel, H., & Billig, M. (1974). Familiarity and categorization in intergroup behavior.
*Journal of Experimental Social Psychology*, *10*, 159–170.
https://doi.org/10.1016/0022-1031(74)90064-X

Tajfel, H., Sheikh, A. A., & Gardner, R. C. (1964). Content of stereotypes and the
inference of similarity between members of stereotyped groups. *Acta
Psychologica*, *22*, 191–201.

Tropp, L. R., & Wright, S. C. (2001). Ingroup identification as the inclusion of ingroup in
the self. *Personality and Social Psychology Bulletin*, *27*, 585–600.
https://doi.org/10.1177/0146167201275007

Turner, J. C., Hogg, M. A., Oakes, P. J., Reicher, S. D., & Wetherell, M. S. (1987).
*Rediscovering the social group: A self-categorization theory*. Basil Blackwell.

Turner, J. C., Oakes, P. J., Haslam, S. A., & McGarty, C. (1994). Self and collective:
Cognition and social context. *Personality and Social Psychology Bulletin*, *20*(5),
454–463.

Tversky, A. (1977). Features of similarity. *Psychological Review*, *84*(4), 327–352.
https://doi.org/10.1037/0033-295X.84.4.327

Tyler, L. K., & Moss, H. E. (2001). Towards a distributed account of conceptual
knowledge. *Trends in Cognitive Sciences*, *5*, 244–252.
https://doi.org/10.1016/S1364-6613(00)01651-X

Unkelbach, C. (2007). Reversing the truth effect: Learning the interpretation of
processing fluency in judgments of truth. *Journal of Experimental Psychology:
Learning, Memory, and Cognition*, *33*(1), 219–230. https://doi.org/10.1037/0278-7393.33.1.219

Unkelbach, C., Koch, A., Silva, R. R., & Garcia-Marques, T. (2019). Truth by repetition:
Explanations and implications. *Current Directions in Psychological Science*,
*28*(3), 247–253. https://doi.org/10.1177/0963721419827854

Unkelbach, C., & Rom, S. C. (2017). A referential theory of the repetition-induced truth
effect. *Cognition*, *160*, 110–126. https://doi.org/10.1016/j.cognition.2016.12.016

van Veelen, R., Eisenbeiss, K. K., & Otten, S. (2016). Newcomers to social categories:
Longitudinal predictors and consequences of ingroup identification. *Personality
and Social Psychology Bulletin*, *42*(6), 811–825.
https://doi.org/10.1177/0146167216643937

van Veelen, R., Otten, S., Cadinu, M., & Hansen, N. (2016). An integrative model of
social identification: Self-stereotyping and self-anchoring as two cognitive
pathways. *Personality and Social Psychology Review*, *20*(1), 3–26.
https://doi.org/10.1177/1088868315576642

van Veelen, R., Otten, S., & Hansen, N. (2011). Linking self and ingroup: Self-anchoring
as distinctive cognitive route to social identification. *European Journal of Social
Psychology*, *41*(5), 628–637. https://doi.org/10.1002/ejsp.792

van Veelen, R., Otten, S., & Hansen, N. (2013a). Social identification when an in-group
identity is unclear: The role of self-anchoring and self-stereotyping. *British
Journal of Social Psychology*, *52*(3), 543–562. https://doi.org/10.1111/j.2044-8309.2012.02110.x

van Veelen, R., Otten, S., & Hansen, N. (2013b). A personal touch to diversity: Self-anchoring increases minority members' identification in a diverse group. *Group
Processes & Intergroup Relations*, *16*(6), 671–683.
https://doi.org/10.1177/1368430212473167

Vehtari, A., Gelman, A., & Gabry, J. (2017). Practical Bayesian model evaluation using
leave-one-out cross-validation and WAIC. *Statistics and Computing*, *27*(5), 1413–1432. https://doi.org/10.1007/s11222-016-9696-4

Vehtari, A., Gelman, A., Simpson, D., Carpenter, B., & Bürkner, P.-C. (2021). Rank-normalization, folding, and localization: An improved R-hat for assessing
convergence of MCMC (with discussion). *Bayesian Analysis*, *16*(2), 667–718.
https://doi.org/10.1214/20-BA1221

Vogel, T., Carr, E. W., Davis, T., & Winkielman, P. (2018). Category structure
determines the relative attractiveness of global versus local averages. *Journal of
Experimental Psychology: Learning, Memory, and Cognition*, *44*, 250–267.
https://doi.org/10.1037/xlm0000446

Yarkoni, T. (2022). The generalizability crisis. *Behavioral and Brain Sciences*, *45*, e1.
https://doi.org/10.1017/S0140525X20001685

Zeithamova, D., Maddox, W. T., & Schnyer, D. M. (2008). Dissociable prototype
learning systems: Evidence from brain imaging and behavior. *Journal of
Neuroscience*, *28*(49), 13194–13201. https://doi.org/10.1523/JNEUROSCI.2915-08.2008
