---
title: "R Notebook"
output: html_notebook
---

```{r}
library(lmerTest)
library(ggeffects)
library(dplyr)
library(report)
library(r2glmm)
library(performance)
library(corrr)
library(broom.mixed)
```

```{r}
library(devtools)
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/corToOne.R")
source_url("https://raw.githubusercontent.com/JacobElder/MiscellaneousR/master/plotCommAxes.R")
```


```{r}
fullTest <- read.csv("../Cleaning/output/fullTest.csv")
fullTrain <- read.csv("../Cleaning/output/fullTrain.csv")

traitsFreqs <- read.csv("../Cleaning/output/traitFreqOverUnder.csv")


uSubs <- unique(fullTest$subID)

indDiffs <- fullTest[!duplicated(fullTest$subID),]
```

```{r}
fullTest$ingChoiceN <- as.factor(fullTest$ingChoiceN)
fullTest$novel <- as.factor(fullTest$novel)
fullTest$selfResp.Z <- scale(fullTest$selfResp)
fullTest$SE.Z <- scale(fullTest$SE)
fullTest$iSE.Z <- scale(fullTest$iSE)
fullTest$oSE.Z <- scale(fullTest$oSE)
fullTest$predicted.Z <- scale(fullTest$predicted)
fullTest$slope.Z <- scale(fullTest$slope)
fullTest$entropy.Z <- scale(fullTest$entropy)
fullTest$WSR.Z <- scale(fullTest$WSR)
fullTest$neighAveOutSE.Z <- scale(fullTest$neighAveOutSE)
fullTest$neighAveAllSE.Z <- scale(fullTest$neighAveAllSE)
fullTest$neighAveInSE.Z <- scale(fullTest$neighAveInSE)
fullTest$evalLOO.Z <- scale(fullTest$evalLOO)
fullTest$propCorrLOO.Z <- scale(fullTest$propCorrLOO)
fullTest$propCorr <- scale(fullTest$propCorr)
```


```{r}
fullTest$novel <- as.factor(fullTest$novel)
levels(fullTest$novel) <- list("Trained"  = "0", "Held Out" = "1")
```

```{r}
PCA<- prcomp(na.omit(fullTest[c("predicted","neighAveOutSE")]),
                center = TRUE,
                scale. = TRUE)
fullTest$PCA[!is.na(fullTest$predicted) & !is.na(fullTest$neighAveOutSE)] <- PCA$x[,1]
```


```{r}
propMatrix <- matrix(nrow=148,ncol=7)
for(i in 1:148){
    traitDf <- subset(fullTest, Idx==i)
    test <- t.test(as.numeric(traitDf$ingChoiceN)-1, mu=.50)
    propMatrix[i, ] <- c(i, test$statistic, test$p.value, test$conf.int, test$estimate, test$parameter)
}
colnames(propMatrix) <- c("Idx", "stat", "p", "LCI", "UCI", "est", "param")
propMatrix <- as.data.frame(propMatrix)
propMatrix$trait <- traitsFreqs$trait
propMatrix <- propMatrix[order(propMatrix$p),]

propMatrix
```

```{r}
indDiffs %>% select(groupHomoph, seHomoph, DS:SING.Inter) %>% corToOne(., "groupHomoph")
indDiffs %>% select(groupHomoph, seHomoph, DS:SING.Inter) %>% plotCorToOne(., "groupHomoph")
```

# (Attempt to) replicate prior work: Ingroup favoritism exhibited by ascribing more positive traits to ingroup

```{r}
m <- glmer( ingChoiceN ~ desirability + propCorrLOO.Z +  ( desirability + propCorrLOO.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```


# Replication of prior self-anchoring findings: Self-evaluations predicting ingroup evaluations

## No covariates

```{r}
m <- glmer( ingChoiceN ~ selfResp.Z +  ( selfResp.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```


## Covariates

```{r}
m <- glmer( ingChoiceN ~ selfResp.Z + propCorr + desirability + ( selfResp.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("selfResp.Z")) %>% plot(show.title=F) + xlab("Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/SelfProjection.tiff",dpi=600)
```

# Replication of prior self-anchoring findings: Is it merely just average self-descriptiveness of the trait?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ evalLOO.Z +  ( evalLOO.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```


## Covariates

```{r}
m <- glmer( ingChoiceN ~ evalLOO.Z + propCorrLOO.Z + desirability + ( evalLOO.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("evalLOO.Z")) %>% plot(show.title=F) + xlab("Leave-One-Out Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
```

# Does similarity-weighted self-evaluation average predict ingroup choices?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ WSR.Z + ( WSR.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```


## Covariates

```{r}
m <- glmer( ingChoiceN ~ WSR.Z + propCorrLOO.Z + desirability + ( WSR.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
```

# Does self-evaluation weighted similarity predict ingroup choices?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ SE.Z + ( SE.Z | subID) , data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ SE.Z + propCorr + desirability + ( SE.Z | subID) , data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
```

# Do cross-validated similarity*self-evaluation predictions predict ingroup choices? 

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z + ( predicted.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

# Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z + propCorrLOO.Z + desirability + ( predicted.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("predicted.Z")) %>% plot(show.title=F) + xlab("Cross-Validated Self-Descriptiveness Predictions") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/CVprediction.tiff",dpi=600)
```
# Do people self-anchor more for higher indegree traits?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * inDegree + ( predicted.Z + inDegree | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * inDegree + propCorr + desirability +  ( predicted.Z + inDegree | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "inDegree")) %>% plot(show.title=F) + xlab("Cross-Validated Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
```


# Do people self-anchor more for higher outdegree traits?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * outDegree + ( predicted.Z + outDegree | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * outDegree + propCorr + desirability +  ( predicted.Z + outDegree | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "outDegree")) %>% plot(show.title=F) + xlab("Cross-Validated Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
```

# Do cross-validated similarity * self-evaluation predictions predict ingroup choices, regardless of whether it was seen prior or not?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel + ( predicted.Z + novel | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel + propCorrLOO.Z + desirability + ( predicted.Z + novel | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("predicted.Z", "novel")) %>% plot(show.title=F)+ xlab("Cross-Validated Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()  + scale_color_discrete(labels = c("Trained","Held-Out"))
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/CVpredictionGeneralize.tiff",dpi=600)
```

# Does generalization depend on outdegree?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel * outDegree  + ( predicted.Z + novel | subID) , data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel * outDegree  + propCorrLOO.Z + desirability + ( predicted.Z + novel | subID) , data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("predicted.Z", "outDegree" ,"novel")) %>% plot(show.title=F)+ xlab("Cross-Validated Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/CVpredictionGeneralize.tiff",dpi=600)
```
# Does generalization depend on indegree?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel * inDegree + ( predicted.Z + novel | subID) , data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ predicted.Z * novel * inDegree + propCorrLOO.Z + desirability +  ( predicted.Z + novel | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("predicted.Z", "inDegree" ,"novel")) %>% plot(show.title=F)+ xlab("Cross-Validated Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
```

# Neighboring Dependencies Predicting Choices

## No covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveOutSE.Z  + ( neighAveOutSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveOutSE.Z  + propCorrLOO.Z + desirability + ( neighAveOutSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("neighAveOutSE.Z")) %>% plot(show.title=F)+ xlab("Outwards Neighboring Self-Evaluations") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/outdegreeNeighbors.tiff",dpi=600)
```

# Neighboring Indegree Dependencies Predicting Choices

## No covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveInSE.Z  + ( neighAveInSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveInSE.Z  + propCorrLOO.Z + desirability + ( neighAveInSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("neighAveInSE.Z")) %>% plot(show.title=F)+ xlab("Inwards Neighboring Self-Evaluations") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/IndegreeNeighbors.tiff",dpi=600)
```

# Neighboring Both Degree Dependencies Predicting Choices

## No covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveAllSE.Z  + ( neighAveAllSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveAllSE.Z  + propCorrLOO.Z + desirability + ( neighAveAllSE.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("neighAveAllSE.Z")) %>% plot(show.title=F)+ xlab("Inwards Neighboring Self-Evaluations") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/IndegreeNeighbors.tiff",dpi=600)
```

# Generalization of Outdegree Neighboring Self-Evaluations

## No covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveOutSE.Z * novel + ( neighAveOutSE.Z + novel | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ neighAveOutSE.Z * novel + propCorr + desirability + ( neighAveOutSE.Z + novel | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("neighAveOutSE.Z","novel")) %>% plot(show.title=F)+ xlab("Outwards Neighboring Self-Evaluations") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/outdegreeNeighborsGeneralization.tiff",dpi=600)
```

# Does entropy (i.e., uncertainty) predict likelihood of ingroup choices?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ entropy.Z  + ( entropy.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ entropy.Z  + propCorr + desirability + ( entropy.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
r2beta(m)
ggpredict(m, c("entropy.Z")) %>% plot(show.title=F) + xlab("Uncertainty") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/Uncertainty.tiff",dpi=600)
```

# Does a linear trend of similarity-based probabilities predict ingroup choices?

## No covariates

```{r}
m <- glmer( ingChoiceN ~ slope.Z  + ( slope.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
```

## Covariates

```{r}
m <- glmer( ingChoiceN ~ slope.Z  + propCorrLOO.Z + desirability + ( slope.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
ggpredict(m, c("slope.Z")) %>% plot(show.title=F) + xlab("Linear Trend of Greater Self-Descriptiveness") + ylab("Likelihood of Ingroup Choice") + jtools::theme_apa()
ggsave("~/Documents/UC Riverside/Studies/Self-Anchoring/Figures/Slope.tiff",dpi=600)
```

# Does a linear trend of similarity-based probabilities predict ingroup choices, controlling for self-descriptiveness?

```{r}
m <- glmer( ingChoiceN ~ scale(slope) + selfResp.Z  + ( scale(slope) + selfResp.Z | subID) + (1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
tidy(m,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
```

# Backwards solution: Can you predict self-evaluations from similarity to ingroup and outgroup choices?

```{r}
m <- lmer( scale(selfResp) ~ scale(inGsim) + scale(outGsim) + (  scale(inGsim) + scale(outGsim) | subID) + (1 | trait), data = fullTrain)
summary(m)
tidy(m,conf.int=TRUE,effects="fixed")
ggpredict(m, c("inGsim")) %>% plot(show.title=F) + xlab("Similarity to Ingroup Choices") + ylab("Self-Evaluation") + jtools::theme_apa()
```

## Moderated by Group Homophily

People who mentally segregrate the groups also self-evaluate more similar to their later group choices.

```{r}
m <- lmer( scale(selfResp) ~ scale(inGsim) * scale(groupHomoph) + scale(outGsim) + (  scale(inGsim) + scale(outGsim) | subID) + (1 | trait), data = fullTrain)
summary(m)
tidy(m,conf.int=TRUE,effects="fixed")
ggpredict(m, c("inGsim","groupHomoph")) %>% plot(show.title=F) + xlab("Similarity to Ingroup Choices") + ylab("Self-Evaluation") + jtools::theme_apa()
```

# Individual Differences and Cross-Validated Predictions


```{r}
m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(groupHomoph) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "groupHomoph")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(RSE) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "RSE")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(SCC) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "SCC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(DS) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "DS")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(NFC) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "NFC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(SING.Ind) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "SING.Ind")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(SING.Inter) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "SING.Inter")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(Proto) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "Proto")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(SI) + ( predicted.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "SI")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ predicted.Z*scale(NTB) + ( predicted.Z | subID) + ( predicted.Z | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("predicted.Z", "NTB")) %>% plot()
```


# Individual Differences and Linear Trend

```{r}
m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(RSE) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "RSE")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(SCC) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "SCC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(DS) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "DS")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(NFC) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "NFC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(SING.Ind) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "SING.Ind")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(SING.Inter) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "SING.Inter")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(Proto) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "Proto")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(SI) + ( slope.Z | subID) + ( 1 | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "SI")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ slope.Z*scale(NTB) + ( slope.Z | subID) + ( slope.Z | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("slope.Z", "NTB")) %>% plot()
```

# Individual Differences and Desirability in Predicting Ingroup Choice

```{r}
m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(RSE) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "RSE")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(SCC) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "SCC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(DS) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "DS")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(NFC) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "NFC")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(SING.Ind) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "SING.Ind")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(SING.Inter) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "SING.Inter")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(Proto) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "Proto")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(SI) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "SI")) %>% plot()

m <- glmer( as.factor(ingChoiceN) ~ scale(desirability)*scale(NTB) + ( scale(desirability) | subID) + ( scale(desirability) | trait), data = fullTest, family = binomial, control = glmerControl(optimizer = "bobyqa",
                                    optCtrl = list(maxfun = 100000)),
    nAGQ = 1)
summary(m)
ggpredict(m, c("desirability", "NTB")) %>% plot()
```


